---
title: "Analysis"
format: html
editor: visual
---

# Sex differences in the Dark Triad and trait aggression: A variance-weighted interpretation of the bifactor model

## Notes on replication package

1.  The analysis script assumes that the R project environment is set to the folder containing the script and replication objects. File paths are therefore written relative to the project root. The required replication objects are: `replicationData.rds`, `interceptsBPAQ.rds`, `interceptsSD3.rds`, `baselineBoot.rds`, `moderatedBoot.rds`, `saturatedBoot.rds`, `parsimoniousBoot.rds`, `correlatedFactorsBoot.rds`, `psychopathyReferenceBoot.rds`, `narcissismReferenceBoot.rds`. If the script is run from another working directory, file-loading commands may need to be adjusted accordingly.

2.  Bootstrap and Multiple Imputation (MI) procedures can be run either in parallel or sequentially. The replication script exposes several tuning parameters for these parts of the analysis: `runBootstraps`, `parallelSupported`, `availableCores`, the number of bootstrap iterations `B`, the number of MI plausible value draws for the full sample `M`, and the number of MI plausible value draws within bootstrap samples `MB`, respectively. If `restartBootstraps` is set to `TRUE`, the script regenerates the bootstrap matrices. If `parallelSupported` is set to `TRUE`, the bootstrap is run in parallel using `pbmcapply()` from the `pbmcapply` package, with the number of cores determined by `availableCores`. If `parallelSupported` is set to `FALSE`, the script uses `lapply()` instead.

3.  Attempting to replicate the bootstrap analyses without parallel computation is not adviced, as multi-stage CFA and SEM model fitting (full pipeline) can be computationally expensive. To facilitate reproduction of the reported estimates and avoid requiring users to rerun the full bootstrap procedures, the bootstrap result matrices used in the manuscript are included in the replication package as `.rds` files. The script defaults to using these files for the final bootstrap-based p-value calculations.

### Tuning parameters

```{r}

RNGkind("L'Ecuyer-CMRG")
masterSeed <- 779

runBootstraps      <- FALSE
parallelSupported  <- TRUE
availableCores     <- 15    # Number of parallel workers
B                  <- 9999  # Bootstrap resamples
M                  <- 500   # Multiple imputation draws
MB                 <- 20    # Multiple imputations draws inside each bootstrap resample
restartBootstraps  <- FALSE # Delete stored results and regenerate bootstrap matrices
runRegularization  <- FALSE # Run regularized CFA instead of using stored results
export             <- TRUE  # Export tables and figures
```

## **Load libraries and data**

```{r}

#| echo: false

requiredPackages <- c(
  "tidyverse",
  "lavaan",
  "semTools",
  "lessSEM",
  "pbmcapply",
  "see",
  "gt",
  "kableExtra",
  "knitr",
  "webshot2"
)

missingPackages <- requiredPackages[
  !vapply(
    requiredPackages,
    requireNamespace,
    logical(1),
    quietly = TRUE
  )
]

if (length(missingPackages) > 0L) {
  install.packages(
    missingPackages,
    repos = "https://cloud.r-project.org"
  )
}

library(tidyverse)
library(lavaan)       # SEM
library(semTools)     # Reliability and plausible values
library(lessSEM)      # Regularized multigroup CFA
library(pbmcapply)    # Parallel computation
library(see)          # Half violin plots
library(gt)           # Print HTML tables
library(kableExtra)   # Export LaTeX tables

replicationData <- readRDS("../Data/replicationData.rds") %>%
  mutate(
    Age = as.numeric(scale(Age))
  )
```

## **Helpers**

```{r}

stretchLatexTable <- function(x) {
  x <- paste(as.character(x), collapse = "\n")
  
  pattern <- "\\\\begin\\{tabular\\}(\\[[^]]*\\])?\\{([^\\r\\n]*)\\}"
  
  if (!grepl(pattern, x, perl = TRUE)) {
    stop("No standard tabular environment found.")
  }
  
  x <- sub(
    pattern,
    "\\\\begin{autotabular}\\1{\\2}",
    x,
    perl = TRUE
  )
  
  sub(
    "\\end{tabular}",
    "\\end{autotabular}",
    x,
    fixed = TRUE
  )
}
```

### **Item mapping**

```{r}

physicalItems <- c("BPAQ1_response", "BPAQ5_response", "BPAQ9_response", "BPAQ13_response", "BPAQ17_response", "BPAQ21_response", "BPAQ24_response", "BPAQ27_response", "BPAQ29_response")

verbalItems <- c("BPAQ14_response", "BPAQ2_response", "BPAQ6_response", "BPAQ10_response", "BPAQ18_response")

hostilityItems <- c("BPAQ16_response", "BPAQ4_response", "BPAQ8_response", "BPAQ12_response", "BPAQ20_response", "BPAQ23_response", "BPAQ26_response", "BPAQ28_response")

angerItems <- c("BPAQ25_response", "BPAQ3_response", "BPAQ7_response", "BPAQ11_response", "BPAQ15_response", "BPAQ19_response", "BPAQ22_response")

machiavellianismItems <- c("DT1_response",  "DT2_response",  "DT3_response", "DT4_response",  "DT5_response",  "DT6_response", "DT7_response",  "DT8_response",  "DT9_response")

psychopathyItems <- c("DT19_response", "DT20_response", "DT21_response", "DT22_response", "DT23_response", "DT24_response", "DT25_response", "DT26_response", "DT27_response")

narcissismItems <- c("DT10_response", "DT11_response", "DT12_response", "DT13_response", "DT14_response", "DT15_response", "DT16_response", "DT17_response", "DT18_response")

coreItems <- c(machiavellianismItems, psychopathyItems, narcissismItems)
```

Generate sum scores

```{r}

replicationData$PhysicalSumScore <- rowSums(replicationData[, physicalItems])

replicationData$VerbalSumScore <- rowSums(replicationData[, verbalItems])

replicationData$HostilitySumScore <- rowSums(replicationData[, hostilityItems])

replicationData$AngerSumScore <- rowSums(replicationData[, angerItems])

replicationData$MachiavellianismSumScore <- rowSums(replicationData[, machiavellianismItems])

replicationData$PsychopathySumScore <- rowSums(replicationData[, psychopathyItems])

replicationData$NarcissismSumScore <- rowSums(replicationData[, narcissismItems])
```

## Descriptives

```{r}

physicalMean <- rowMeans(replicationData[, physicalItems])

verbalMean <- rowMeans(replicationData[, verbalItems])

hostilityMean <- rowMeans(replicationData[, hostilityItems])

angerMean <- rowMeans(replicationData[, angerItems])

machiavellianismMean <- rowMeans(replicationData[, machiavellianismItems])

psychopathyMean <- rowMeans(replicationData[, psychopathyItems])

narcissismMean <- rowMeans(replicationData[, narcissismItems])

descriptivesTable <- data.frame(
  Sex = ifelse(replicationData$Male == 1, "Male", "Female"),
  Physical = physicalMean,
  Verbal = verbalMean,
  Hostility = hostilityMean,
  Anger = angerMean,
  Machiavellianism = machiavellianismMean,
  Psychopathy = psychopathyMean,
  Narcissism = narcissismMean
) %>%
  group_by(Sex) %>%
  summarise(
    across(
      everything(),
      list(
        Mean = ~ mean(.x, na.rm = TRUE),
        SD = ~ sd(.x, na.rm = TRUE)
      ),
      .names = "{.col}_{.fn}"
    ),
    .groups = "drop"
  )

# --------------------------- PREPARE TABLE ---------------------------

variableOrder <- unique(
  sub(
    "_(Mean|SD)$",
    "",
    setdiff(names(descriptivesTable), "Sex")
  )
)

descriptivesTable <- descriptivesTable %>%
  tidyr::pivot_longer(
    cols = -Sex,
    names_to = c("Variable", ".value"),
    names_pattern = "^(.*)_(Mean|SD)$"
  ) %>%
  tidyr::pivot_wider(
    id_cols = Variable,
    names_from = Sex,
    values_from = c(Mean, SD),
    names_glue = "{Sex}_{.value}"
  ) %>%
  mutate(
    Variable = factor(Variable, levels = variableOrder)
  ) %>%
  arrange(Variable) %>%
  mutate(
    Variable = as.character(Variable)
  ) %>%
  select(
    Variable,
    Female_Mean,
    Female_SD,
    Male_Mean,
    Male_SD
  ) %>%
  mutate(
    across(
      -Variable,
      ~ ifelse(is.na(.x), "—", sprintf("%.2f", .x))
    )
  )


# ------------------------------- GT ----------------------------------

descriptivesGT <- descriptivesTable %>%
  gt::gt(
    rowname_col = "Variable"
  ) %>%
  gt::tab_stubhead(
    label = "Variable"
  ) %>%
  gt::cols_label(
    Female_Mean = gt::html("<i>M</i>"),
    Female_SD = gt::html("<i>SD</i>"),
    Male_Mean = gt::html("<i>M</i>"),
    Male_SD = gt::html("<i>SD</i>")
  ) %>%
  gt::tab_spanner(
    label = "Female",
    columns = c(Female_Mean, Female_SD)
  ) %>%
  gt::tab_spanner(
    label = "Male",
    columns = c(Male_Mean, Male_SD)
  ) %>%
  gt::cols_align(
    align = "center",
    columns = -Variable
  ) %>%
  gt::tab_options(
    table.font.names = c("Verdana", "Arial", "sans-serif"),
    table.font.size = gt::px(11),
    column_labels.font.weight = "bold",
    column_labels.border.top.width = gt::px(0),
    column_labels.border.bottom.width = gt::px(1),
    table_body.hlines.width = gt::px(0)
  )

descriptivesGT
  
if (export) {
  
  descriptivesGT_png <- descriptivesGT %>%
    gt::tab_options(
      table.width = gt::px(624)
    )
    
  gt::gtsave(
    descriptivesGT_png,
    filename = "../Tables/descriptivesTable.png",
    zoom = 3.125,
    expand = 0
  )


# ------------------------------ LATEX --------------------------------
  
  # Convert one HTML-formatted result cell to LaTeX
  toLatexCell <- function(x) {
    if (is.na(x)) {
      return("\\textemdash{}")
    }
    
    x <- gsub("&lt;", "$<$", x, fixed = TRUE)
    
    # Replace each complete star sequence exactly once
    x <- gsub(
      "(\\*{1,3})",
      "{\\\\tiny \\1}",
      x,
      perl = TRUE
    )
    
    lines <- strsplit(x, "<br>", fixed = TRUE)[[1]]
    
    paste0(
      "\\makecell{",
      paste(lines, collapse = " \\\\ "),
      "}"
    )
  }
  
  descriptivesTableLatex <- descriptivesTableLatex %>%
    mutate(
      across(
        -1,
        \(x) vapply(as.character(x), toLatexCell, character(1))
      )
    )

  descriptivesKable <- descriptivesTableLatex %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      col.names = c("Variable", "$M$", "$SD$", "$M$", "$SD$"),
      align = c("l", rep("c", 4))
    ) %>%
    kableExtra::add_header_above(
      header = c(" " = 1, "Female" = 2, "Male" = 2),
      bold = TRUE
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(descriptivesTableLatex) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(descriptivesKable),
    "../Tables/descriptivesTable.tex"
  )

}
```

### Distributions

```{r}

variableOrder <- c(
  "Physical",
  "Verbal",
  "Hostility",
  "Anger",
  "Machiavellianism",
  "Psychopathy",
  "Narcissism"
)

distributionData <- replicationData %>%
  dplyr::select(Male, PhysicalSumScore, VerbalSumScore, HostilitySumScore, AngerSumScore, MachiavellianismSumScore, PsychopathySumScore, NarcissismSumScore) %>%
  mutate(
    PhysicalSumScore = PhysicalSumScore / length(physicalItems),
    VerbalSumScore = VerbalSumScore / length(verbalItems),
    HostilitySumScore = HostilitySumScore / length(hostilityItems),
    AngerSumScore = AngerSumScore / length(angerItems),
    MachiavellianismSumScore = MachiavellianismSumScore / length(machiavellianismItems),
    PsychopathySumScore = PsychopathySumScore / length(psychopathyItems),
    NarcissismSumScore = NarcissismSumScore / length(narcissismItems),
  ) %>%
  pivot_longer(
    cols=c(PhysicalSumScore, VerbalSumScore, HostilitySumScore, AngerSumScore, MachiavellianismSumScore, PsychopathySumScore, NarcissismSumScore),
    names_to = "Variable",
    values_to = "Response"
  ) %>%
  mutate(
    Male = ifelse(Male==1, "Male", "Female"),
    Variable = sub("SumScore$", "", Variable),
    Variable = factor(Variable, levels = variableOrder)
  ) %>%
  rename(Sex = Male)

ggplot(distributionData, aes(x=Response, fill=Sex)) +
  geom_histogram(binwidth = 0.2, alpha=0.75) +
  scale_fill_manual(
    values  = c("Female" = "steelblue", "Male" = "lightcoral"),
  )+
  facet_wrap(
    ~ Variable,
    nrow = 2,
    scales = "fixed"
  ) +
  labs(x="Response", y="Count") +
  theme_minimal() +
  theme(
    legend.position = "top",
    legend.title = element_blank()
  )

ggplot(distributionData, aes(x = Variable, y = Response, fill = Sex)) +
  see::geom_violinhalf(
    data = \(x) dplyr::filter(x, Sex == "Female"),
    aes(group = Variable),
    alpha = 0.5,
    flip = TRUE,
    trim = FALSE,
    show.legend = FALSE
  ) +
  see::geom_violinhalf(
    data = \(x) dplyr::filter(x, Sex == "Male"),
    aes(group = Variable),
    alpha = 0.5,
    flip = FALSE,
    trim = FALSE,
    show.legend = FALSE
  ) +
  geom_boxplot(
    width = 0.35,
    outlier.shape = NA,
    whisker.colour = NA,
    staple.colour = NA,
    alpha = 1,
    position = position_dodge(width = 0.35),
    show.legend = TRUE
  ) +
  scale_fill_manual(
    values = c(
      Female = "steelblue",
      Male   = "lightcoral"
    )
  ) +
  scale_y_continuous(
    breaks = 0:4,
    expand = expansion(mult = c(0, 0))
  ) +
  coord_cartesian(
    ylim = c(0, 4)
  ) +
  labs(x = NULL, y = "Response") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top",
    legend.title = element_blank()
  )

rm(distributionData)
```

## CFA

### Fix measurement functions

```{r}

fixedSingleFun <- function(i, parameterTable, digits=10) {
  
  par <- round(parameterTable[i,"est"], digits = digits)
  lhs <- parameterTable[i, "lhs"]
  rhs <- parameterTable[i, "rhs"]
  op  <- parameterTable[i, "op"]
  
  if (parameterTable[i,"op"] == "~1") {
    string <- paste(lhs, "~", par, "*", 1)
    return(string)
  } else {
    string <- paste(lhs, op, par, "*", rhs)
    return(string)
  }
}

fixedMultiFun <- function(i, parameterTable, digits=10) {
  
  par1 <- round(parameterTable[i, "est1"], digits = digits)
  par2 <- round(parameterTable[i, "est2"], digits = digits)
  lhs <- parameterTable[i, "lhs"]
  rhs <- parameterTable[i, "rhs"]
  op  <- parameterTable[i, "op"]
  
  if (op == "~1") {
    return(paste0(lhs, " ~ c(", par1, ", ", par2, ")*1"))
  } else {
    return(paste0(lhs, " ", op, " c(", par1, ", ", par2, ")*", rhs))
  }
}

extraMeasurementFun <- function(lvNames, covariates, group, data) {
  
  extraMeasurement <- paste(
    c(
      paste0(
        lvNames, " ~~ ",
        paste(covariates, collapse = " + "),
        " \n "
      ),
      if (length(covariates) > 1L) {
        paste0(
          covariates[-length(covariates)], " ~~ ",
          sapply(
            seq_len(length(covariates) - 1L),
            function(i) {
              paste(
                covariates[(i + 1L):length(covariates)],
                collapse = " + "
              )
            }
          ),
          " \n "
        )
      }
    ),
    collapse = ""
  )
  
  if(is.null(group)){
    # Fix mean of binary variable for convergence, cannot estimate both mean and var
    binaryString <- paste("Male", "~", mean(data$Male), "*", 1)
  } else {
    binaryString <- NULL
  }
  
  return(paste(extraMeasurement, binaryString, sep=" \n "))
}

congenialFun <- function(measurementFit, covariates=NULL, group=NULL, groupLabels=NULL, data) {
  
  if (inherits(measurementFit, "lavaan")) {
    measurementFit <- list(measurementFit)
  }

  parameterTable <- dplyr::bind_rows(
    lapply(measurementFit, parameterEstimates)
  )
  
  lvNames <- unique(unlist(
    lapply(measurementFit, lavNames, type = "lv")
  ))
  
  if(is.null(group)) {
    fixedMeasurementBlock <- sapply(
      X = 1:nrow(parameterTable),
      FUN = fixedSingleFun,
      parameterTable = parameterTable,
      digits=10
    ) %>%
      paste(collapse = " \n ")  
  } else {
    parameterTable <- parameterTable %>%
      dplyr::select(lhs, op, rhs, group, est) %>%
      pivot_wider(
        id_cols = c(lhs, op, rhs),
        names_from = group,
        values_from = est,
        names_prefix = "est"
      )
    fixedMeasurementBlock <- sapply(
      X = 1:nrow(parameterTable),
      FUN = fixedMultiFun,
      parameterTable = parameterTable,
      digits=10
    ) %>%
      paste(collapse = " \n ")  
  }
  
  expandedModel <- fixedMeasurementBlock
  
  if (length(covariates) > 0L) {
    expandedModel <- paste(
      expandedModel,
      extraMeasurementFun(lvNames, covariates, group, data),
      sep = "\n"
    )
  }
  
  congenialFit <- cfa(
    expandedModel,  
    estimator = "ML",
    se = "none",
    test = "none",
    meanstructure = TRUE,
    std.lv = FALSE,
    group = group,
    group.label = groupLabels,
    data = data
  )

}
```

### Response

```{r}

set.seed(masterSeed)

responseMeasurement <- paste(
  'Physical =~ ', paste(physicalItems, collapse = " + "), ' \n ',
  'Verbal =~ ', paste(verbalItems, collapse = " + "), ' \n ',
  'Hostility =~ ', paste(hostilityItems, collapse = " + "), ' \n ',
  'Anger =~ ', paste(angerItems, collapse = " + "), ' \n '
)

responseFit <- cfa(
  responseMeasurement,
  estimator = "MLR",
  std.lv = TRUE,
  meanstructure = TRUE,
  data = replicationData
)

responseAlphaReliability <- compRelSEM(
  responseFit,
  obs.var = TRUE,
  tau.eq = TRUE
)

responseOmegaReliability <- compRelSEM(
  responseFit,
  obs.var = TRUE,
  tau.eq = FALSE
)

unlist(responseAlphaReliability)
unlist(responseOmegaReliability)

summary(responseFit, fit.measures = TRUE, standardized = TRUE)

# -------------------------- RELIABILITY ADJUSTMENT -------------------------------
# Makes effects defined with respect to the true score variance of the response

replicationData$PhysicalSumScore <- as.numeric(scale(replicationData$PhysicalSumScore)) / sqrt(responseOmegaReliability$Physical[[1]])
replicationData$VerbalSumScore <- as.numeric(scale(replicationData$VerbalSumScore)) / sqrt(responseOmegaReliability$Verbal[[1]])
replicationData$HostilitySumScore <- as.numeric(scale(replicationData$HostilitySumScore)) / sqrt(responseOmegaReliability$Hostility[[1]])
replicationData$AngerSumScore <- as.numeric(scale(replicationData$AngerSumScore)) / sqrt(responseOmegaReliability$Anger[[1]])
```

### Predictors

#### First order

```{r}

set.seed(masterSeed)

firstOrderMeasurement <- paste(
  'Machiavellianism =~ ', paste(machiavellianismItems, collapse = " + "), ' \n ',
  'Psychopathy =~ ', paste(psychopathyItems, collapse = " + "), ' \n ',
  'Narcissism =~ ', paste(narcissismItems, collapse = " + "), ' \n '
)

firstOrderFit <- cfa(
  firstOrderMeasurement,  
  data = replicationData,
  estimator = "MLR",
  meanstructure = TRUE,
  std.lv = TRUE
)

predictorAlphaReliability <- compRelSEM(
  firstOrderFit,
  obs.var = TRUE,
  tau.eq = TRUE
)

predictorOmegaReliability <- compRelSEM(
  firstOrderFit,
  obs.var = TRUE,
  tau.eq = FALSE
)

cat('\n\n Alpha reliability: \n\n')

unlist(predictorAlphaReliability)

cat('\n\n Omega reliability: \n\n')

unlist(predictorOmegaReliability)

# -------------------------- RELIABILITY ADJUSTMENT -------------------------------

replicationData$MachiavellianismSumScore <- as.numeric(scale(replicationData$MachiavellianismSumScore)) / sqrt(predictorOmegaReliability$Machiavellianism[[1]])
replicationData$PsychopathySumScore <- as.numeric(scale(replicationData$PsychopathySumScore)) / sqrt(predictorOmegaReliability$Psychopathy[[1]])
replicationData$NarcissismSumScore <- as.numeric(scale(replicationData$NarcissismSumScore)) / sqrt(predictorOmegaReliability$Narcissism[[1]])
```

#### Bifactor (S-1)

- Eid, M., Geiser, C., Koch, T., & Heene, M. (2017). Anomalous results in *G*-factor models: Explanations and alternatives. *Psychological Methods, 22*(3), 541–562. [https://doi.org/10.1037/met0000083](https://psycnet.apa.org/doi/10.1037/met0000083)

```{r}

set.seed(masterSeed)

bifactorMeasurement <- paste(
  'Reference =~ ', paste(coreItems, collapse = " + "), ' \n ',
  'Psychopathy =~ ', paste(psychopathyItems, collapse = " + "), ' \n ',
  'Narcissism =~ ', paste(narcissismItems, collapse = " + "), ' \n ',
  'Psychopathy ~~ 0*Reference \n ',
  'Narcissism ~~ 0*Reference \n '
)

bifactorFit <- cfa(
  bifactorMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  std.lv = TRUE,
  data = replicationData
)

reliability <- compRelSEM(
  bifactorFit,
  obs.var = TRUE,
  tau.eq = FALSE
)

unlist(reliability)

summary(bifactorFit, fit.measures = TRUE, standardized = TRUE)
```

### Diagnostics

#### Invariance

##### Regularized BPAQ

```{r}

if(runRegularization) {
  
  set.seed(masterSeed)
  
  itemsBPAQ <- c(physicalItems, verbalItems, hostilityItems, angerItems)
  
  interceptsFemale <- paste0(
    itemsBPAQ, "_SEP_Int_SEP_none_SEP_Female"
  )
  
  interceptsMale <- gsub(
    "Female", "Male", interceptsFemale, fixed = TRUE
  )
  
  interceptsDelta <- gsub(
    "Female", "Delta", interceptsFemale, fixed = TRUE
  )
  
  residualsFemale <- paste0(
    itemsBPAQ, "_SEP_Var_SEP_", itemsBPAQ, "_SEP_Female"
  )
  
  lvNames <- lavNames(responseFit, "lv")
  
  latentCovFemale <- paste0(
    unlist(
      lapply(
        seq_along(lvNames),
        function(i) {
          rhs <- lvNames[i:length(lvNames)]
          
          paste0(
            lvNames[[i]], " ~~ ",
            lvNames[[i]], "_SEP_Var_SEP_", rhs, "_SEP_Female*",
            rhs, "\n"
          )
        }
      )
    ),
    collapse = ""
  )
  
  responseMeasurementFemale <- paste(
    "Physical =~",
    paste0(
      "Physical_SEP_Lam_SEP_", physicalItems, "_SEP_Both*",
      physicalItems,
      collapse = " + "
    ),
    "\n Verbal =~",
    paste0(
      "Verbal_SEP_Lam_SEP_", verbalItems, "_SEP_Both*",
      verbalItems,
      collapse = " + "
    ),
    "\n Hostility =~",
    paste0(
      "Hostility_SEP_Lam_SEP_", hostilityItems, "_SEP_Both*",
      hostilityItems,
      collapse = " + "
    ),
    "\n Anger =~",
    paste0(
      "Anger_SEP_Lam_SEP_", angerItems, "_SEP_Both*",
      angerItems,
      collapse = " + "
    ),
    "\n",
    paste0(
      itemsBPAQ, " ~ ", interceptsFemale, "*1",
      collapse = "\n"
    ),
    "\n",
    paste0(
      itemsBPAQ, " ~~ ", residualsFemale, "*", itemsBPAQ,
      collapse = "\n"
    ),
    "\n",
    latentCovFemale
  )
  
  meansMale <- paste0(
    lvNames, "_SEP_Int_SEP_none_SEP_Male"
  )
  
  latentMeansMale <- paste0(
    lvNames, " ~ ", meansMale, "*1",
    collapse = "\n"
  )
  
  responseMeasurementMale <- gsub(
    "Female",
    "Male",
    responseMeasurementFemale,
    fixed = TRUE
  )
  
  responseMeasurementMale <- paste0(
    responseMeasurementMale, "\n",
    latentMeansMale
  )
  
  # Female reference: latent variances = 1, latent means = 0
  singleGroupFemaleBPAQ <- cfa(
    responseMeasurementFemale,
    estimator = "MLR",
    meanstructure = TRUE,
    std.lv = TRUE,
    data = replicationData[replicationData$Male == 0, ]
  )
  
  # Male: free latent variances, means, and all loadings
  singleGroupMaleBPAQ <- cfa(
    responseMeasurementMale,
    estimator = "MLR",
    meanstructure = TRUE,
    std.lv = FALSE,
    auto.fix.first = FALSE,
    do.fit = FALSE,
    data = replicationData[replicationData$Male == 1, ]
  )
  
  transformation <- paste0(
    "parameters: ",
    paste(
      c(interceptsMale, interceptsFemale, interceptsDelta),
      collapse = ", "
    ),
    "\n",
    paste0(
      interceptsMale, " = ",
      interceptsFemale, " + ",
      interceptsDelta, ";",
      collapse = "\n"
    )
  )
  
  tauDif <- 0.20
  nObs <- nobs(singleGroupFemaleBPAQ) + nobs(singleGroupMaleBPAQ)
  
  lambda <- 1 / (nObs * tauDif^2)
  
  lassoFitBPAQ <- lessSEM::lasso(
    lavaanModel = c(singleGroupFemaleBPAQ, singleGroupMaleBPAQ),
    regularized = interceptsDelta,
    lambdas = lambda,
    modifyModel = lessSEM::modifyModel(
      transformations = transformation
    )
  )
  
  lassoTableBPAQ <- dplyr::bind_rows(
    lassoFitBPAQ@parameters %>%
      dplyr::select(-lambda, -alpha),
    
    lassoFitBPAQ@transformations %>%
      dplyr::select(-lambda, -alpha)
  ) %>%
    tidyr::pivot_longer(
      everything(),
      names_to = "Parameter",
      values_to = "est",
      values_drop_na = TRUE
    ) %>%
    tidyr::separate_wider_delim(
      Parameter,
      delim = "_SEP_",
      names = c("lhs", "op", "rhs", "group")
    ) %>%
    dplyr::filter(group != "Delta") %>%
    dplyr::mutate(
      op = dplyr::recode(
        op,
        Lam = "=~",
        Var = "~~",
        Int = "~1"
      ),
      rhs = dplyr::if_else(rhs == "none", "", rhs),
      group = dplyr::if_else(
        group == "Both",
        "Female,Male",
        group
      )
    ) %>%
    tidyr::separate_longer_delim(group, delim = ",") %>%
    dplyr::mutate(
      group = dplyr::recode(group, Female = 1L, Male = 2L)
    ) %>%
    dplyr::bind_rows(
      parTable(singleGroupFemaleBPAQ) %>%
        dplyr::filter(
          free == 0,
          lhs %in% lvNames,
          (op == "~~" & lhs == rhs) | op == "~1"
        ) %>%
        dplyr::transmute(
          lhs,
          op,
          rhs,
          group = 1L,
          est = ustart
        )
    ) %>%
    dplyr::arrange(
      group,
      match(op, c("=~", "~1", "~~")),
      lhs,
      rhs
    )
  
  interceptsBPAQ <- lassoTableBPAQ %>%
    filter(
      op == "~1" & lhs %in% lavNames(singleGroupFemaleBPAQ, "ov.ind")
    ) %>%
    pivot_wider(
      id_cols = c(lhs, op),
      names_from = group,
      values_from = est,
      names_prefix = "est"
    ) %>%
    mutate(
      dif = abs(est2 - est1),
      factor = case_when(
        lhs %in% physicalItems ~ "Physical",
        lhs %in% verbalItems ~ "Verbal",
        lhs %in% hostilityItems ~ "Hostility",
        lhs %in% angerItems ~ "Anger"
      )
    ) %>%
    arrange(desc(dif))
  
  saveRDS(interceptsBPAQ, file = "../Data/interceptsBPAQ.rds")
}
```

##### Regularized SD3

```{r}

if(runRegularization) {

  set.seed(masterSeed)
  
  interceptsFemale <- paste0(
    coreItems, "_SEP_Int_SEP_none_SEP_Female"
  )
  
  interceptsMale <- gsub(
    "Female", "Male", interceptsFemale, fixed = TRUE
  )
  
  interceptsDelta <- gsub(
    "Female", "Delta", interceptsFemale, fixed = TRUE
  )
  
  residualsFemale <- paste0(
    coreItems, "_SEP_Var_SEP_", coreItems, "_SEP_Female"
  )
  
  lvNames <- lavNames(bifactorFit, "lv")
  
  latentCovFemale <- paste(
    "Reference ~~ Reference_SEP_Var_SEP_Reference_SEP_Female*Reference", " \n ",
    "Reference ~~ 0*Psychopathy", " \n ",
    "Reference ~~ 0*Narcissism", " \n ", 
    "Psychopathy ~~ Psychopathy_SEP_Var_SEP_Psychopathy_SEP_Female*Psychopathy", " \n ",
    "Psychopathy ~~ Psychopathy_SEP_Var_SEP_Narcissism_SEP_Female*Narcissism", " \n ",
    "Narcissism ~~ Narcissism_SEP_Var_SEP_Narcissism_SEP_Female*Narcissism", " \n "
  )
  
  bifactorMeasurementFemale <- paste(
    "Reference =~",
    paste0(
      "Reference_SEP_Lam_SEP_", coreItems, "_SEP_Both*",
      coreItems,
      collapse = " + "
    ),
    "\n Psychopathy =~",
    paste0(
      "Psychopathy_SEP_Lam_SEP_", psychopathyItems, "_SEP_Both*",
      psychopathyItems,
      collapse = " + "
    ),
    "\n Narcissism =~",
    paste0(
      "Narcissism_SEP_Lam_SEP_", narcissismItems, "_SEP_Both*",
      narcissismItems,
      collapse = " + "
    ),
    "\n",
    paste0(
      coreItems, " ~ ", interceptsFemale, "*1",
      collapse = "\n"
    ),
    "\n",
    paste0(
      coreItems, " ~~ ", residualsFemale, "*", coreItems,
      collapse = "\n"
    ),
    "\n",
    latentCovFemale
  )
  
  meansMale <- paste0(
    lvNames, "_SEP_Int_SEP_none_SEP_Male"
  )
  
  latentMeansMale <- paste0(
    lvNames, " ~ ", meansMale, "*1",
    collapse = "\n"
  )
  
  bifactorMeasurementMale <- gsub(
    "Female",
    "Male",
    bifactorMeasurementFemale,
    fixed = TRUE
  )
  
  bifactorMeasurementMale <- paste0(
    bifactorMeasurementMale, "\n",
    latentMeansMale
  )
  
  # Female reference: latent variances = 1, latent means = 0
  singleGroupFemaleSD3 <- cfa(
    bifactorMeasurementFemale,
    estimator = "MLR",
    meanstructure = TRUE,
    std.lv = TRUE,
    data = replicationData[replicationData$Male == 0, ]
  )
  
  # Male: free latent variances, means, and all loadings
  singleGroupMaleSD3 <- cfa(
    bifactorMeasurementMale,
    estimator = "MLR",
    meanstructure = TRUE,
    std.lv = FALSE,
    auto.fix.first = FALSE,
    do.fit = FALSE,
    data = replicationData[replicationData$Male == 1, ]
  )
  
  transformation <- paste0(
    "parameters: ",
    paste(
      c(interceptsMale, interceptsFemale, interceptsDelta),
      collapse = ", "
    ),
    "\n",
    paste0(
      interceptsMale, " = ",
      interceptsFemale, " + ",
      interceptsDelta, ";",
      collapse = "\n"
    )
  )
  
  tauDif <- 0.20
  nObs <- nobs(singleGroupFemaleSD3) + nobs(singleGroupMaleSD3)
  
  lambda <- 1 / (nObs * tauDif^2)
  
  lassoFitSD3 <- lessSEM::lasso(
    lavaanModel = c(singleGroupFemaleSD3, singleGroupMaleSD3),
    regularized = interceptsDelta,
    lambdas = lambda,
    modifyModel = lessSEM::modifyModel(
      transformations = transformation
    )
  )
  
  lassoTableSD3 <- dplyr::bind_rows(
    lassoFitSD3@parameters %>%
      dplyr::select(-lambda, -alpha),
    
    lassoFitSD3@transformations %>%
      dplyr::select(-lambda, -alpha)
  ) %>%
    tidyr::pivot_longer(
      everything(),
      names_to = "Parameter",
      values_to = "est",
      values_drop_na = TRUE
    ) %>%
    tidyr::separate_wider_delim(
      Parameter,
      delim = "_SEP_",
      names = c("lhs", "op", "rhs", "group")
    ) %>%
    dplyr::filter(group != "Delta") %>%
    dplyr::mutate(
      op = dplyr::recode(
        op,
        Lam = "=~",
        Var = "~~",
        Int = "~1"
      ),
      rhs = dplyr::if_else(rhs == "none", "", rhs),
      group = dplyr::if_else(
        group == "Both",
        "Female,Male",
        group
      )
    ) %>%
    tidyr::separate_longer_delim(group, delim = ",") %>%
    dplyr::mutate(
      group = dplyr::recode(group, Female = 1L, Male = 2L)
    ) %>%
    dplyr::bind_rows(
      parTable(singleGroupFemaleSD3) %>%
        dplyr::filter(
          free == 0,
          lhs %in% lvNames,
          (op == "~~" & lhs == rhs) | op == "~1"
        ) %>%
        dplyr::transmute(
          lhs,
          op,
          rhs,
          group = 1L,
          est = ustart
        )
    ) %>%
    dplyr::arrange(
      group,
      match(op, c("=~", "~1", "~~")),
      lhs,
      rhs
    )
  
  
  interceptsSD3 <- lassoTableSD3 %>%
    filter(
      op == "~1" & lhs %in% lavNames(singleGroupFemaleSD3, "ov.ind")
    ) %>%
    pivot_wider(
      id_cols = c(lhs, op),
      names_from = group,
      values_from = est,
      names_prefix = "est"
    ) %>%
    mutate(
      dif = abs(est2 - est1),
      factor = case_when(
        lhs %in% machiavellianismItems ~ "Machiavellianism",
        lhs %in% psychopathyItems ~ "Psychopathy",
        lhs %in% narcissismItems ~ "Narcissism"
      )
    ) %>%
    arrange(desc(dif))
  
  saveRDS(interceptsSD3, file = "../Data/interceptsSD3.rds")
}
```

##### Invariance statistics

```{r}

set.seed(masterSeed)

interceptsSD3 <- readRDS(file = "../Data/interceptsSD3.rds")
interceptsBPAQ <- readRDS(file = "../Data/interceptsBPAQ.rds")

nFreeBPAQ <- 9
nFreeSD3 <- 6

# ---------------------------------- SD3 -------------------------------------

cat("----------------------- SD3 Invariance Metrics ---------------------------", "\n\n")

nullMeasurement <- paste(coreItems, "~ 1", collapse = "\n")

nullFitSD3 <- cfa(
  nullMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  group = "Male",   
  group.label = c("0", "1"),
  group.equal = c("intercepts", "residuals"),
  auto.cov.y = FALSE,
  auto.var = TRUE,
  data = replicationData
)

configuralInvarianceFitSD3 <- cfa(
  bifactorMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  group = "Male",
  group.label = c("0", "1"),
  std.lv = TRUE,
  data = replicationData
)

fitMeasures(
  configuralInvarianceFitSD3, 
  fit.measures = c("cfi", "cfi.robust", "rmsea", "rmsea.robust","srmr", "mfi"),
  baseline.model = nullFitSD3
)

metricInvarianceFitSD3 <- cfa(
  bifactorMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  group = "Male",
  group.label = c("0", "1"),
  group.equal = c("loadings"),
  std.lv = TRUE,
  data = replicationData
)

fitMeasures(
  metricInvarianceFitSD3, 
  fit.measures = c("cfi", "cfi.robust", "rmsea", "rmsea.robust", "srmr", "mfi"),
  baseline.model = nullFitSD3
)

scalarInvarianceFitSD3 <- cfa(
  bifactorMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  group = "Male",
  group.label = c("0", "1"),
  group.equal = c("loadings", "intercepts"),
  std.lv = TRUE,
  data = replicationData
)

fitMeasures(
  scalarInvarianceFitSD3, 
  fit.measures = c("cfi", "cfi.robust", "rmsea", "rmsea.robust", "srmr", "mfi"),
  baseline.model = nullFitSD3
)

freeSD3 <- interceptsSD3$lhs[1:nFreeSD3]

partialInvarianceFitSD3 <- cfa(
  bifactorMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  group = "Male",
  group.label = c("0", "1"),
  group.equal = c("loadings", "intercepts"),
  group.partial = paste0(freeSD3, "~ 1"),
  std.lv = TRUE,
  data = replicationData
)

fitMeasures(
  partialInvarianceFitSD3, 
  fit.measures = c("cfi", "cfi.robust", "rmsea", "rmsea.robust", "srmr", "mfi"),
  baseline.model = nullFitSD3
)

cat("\n\n","SD3: ", nFreeSD3, " out of ", nrow(interceptsSD3)," item intercepts freed. Items correspond to: ", "\n")

table(interceptsSD3$factor[1:nFreeSD3])

cat("\n", "Total items per dimension: ", "\n")

table(interceptsSD3$factor)

partialFirstOrderFit <- cfa(
  firstOrderMeasurement,  
  estimator = "ML",
  se = "none",
  test = "none",
  baseline = FALSE,
  meanstructure = TRUE,
  std.lv = TRUE,
  group = "Male",
  group.label = c("0", "1"),
  group.equal = c("loadings", "intercepts"),
  group.partial = paste0(freeSD3, "~ 1"),
  data = replicationData
)

# ---------------------------------- BPAQ -------------------------------------

cat("\n\n", "----------------------- BPAQ Invariance Metrics ---------------------------", "\n\n")

nullMeasurement <- paste(
  c(physicalItems, verbalItems, hostilityItems, angerItems),
  "~ 1", 
  collapse = "\n"
)

nullFitBPAQ <- cfa(
  nullMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  group = "Male",
  group.label = c("0", "1"),
  group.equal = c("intercepts", "residuals"),
  auto.cov.y = FALSE,
  auto.var = TRUE,
  data = replicationData
)

configuralInvarianceFitBPAQ <- cfa(
  responseMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  group = "Male",
  group.label = c("0", "1"),
  std.lv = TRUE,
  data = replicationData
)

fitMeasures(
  configuralInvarianceFitBPAQ, 
  fit.measures = c("cfi", "cfi.robust", "rmsea", "rmsea.robust","srmr", "mfi"),
  baseline.model = nullFitBPAQ
)

metricInvarianceFitBPAQ <- cfa(
  responseMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  group = "Male",
  group.label = c("0", "1"),
  group.equal = c("loadings"),
  std.lv = TRUE,
  data = replicationData
)

fitMeasures(
  metricInvarianceFitBPAQ, 
  fit.measures = c("cfi", "cfi.robust", "rmsea", "rmsea.robust", "srmr", "mfi"),
  baseline.model = nullFitBPAQ
)

scalarInvarianceFitBPAQ <- cfa(
  responseMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  group = "Male",
  group.label = c("0", "1"),
  group.equal = c("loadings", "intercepts"),
  std.lv = TRUE,
  data = replicationData
)

fitMeasures(
  scalarInvarianceFitBPAQ, 
  fit.measures = c("cfi", "cfi.robust", "rmsea", "rmsea.robust", "srmr", "mfi"),
  baseline.model = nullFitBPAQ
)


freeBPAQ <- interceptsBPAQ$lhs[1:nFreeBPAQ]

partialInvarianceFitBPAQ <- cfa(
  responseMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  group = "Male",
  group.label = c("0", "1"),
  group.equal = c("loadings", "intercepts"),
  group.partial = paste0(freeBPAQ, "~ 1"),
  std.lv = TRUE,
  data = replicationData
)

fitMeasures(
  partialInvarianceFitBPAQ, 
  fit.measures = c("cfi", "cfi.robust", "rmsea", "rmsea.robust", "srmr", "mfi"),
  baseline.model = nullFitBPAQ
)

cat("\n\n","BPAQ: ", nFreeBPAQ, " out of ", nrow(interceptsBPAQ)," item intercepts freed. Items correspond to: ", "\n")

table(interceptsBPAQ$factor[1:nFreeBPAQ])

cat("\n", "Total items per dimension: ", "\n")

table(interceptsBPAQ$factor)
```

##### Congenial models

```{r}

congenialMetricFit <- congenialFun(
  measurementFit=list(metricInvarianceFitBPAQ, metricInvarianceFitSD3), 
  covariates=c(
    "Age"
  ),
  group="Male",
  groupLabels = c("0", "1"),
  data=replicationData
)

congenialScalarFit <- congenialFun(
  measurementFit=list(scalarInvarianceFitBPAQ, scalarInvarianceFitSD3), 
  covariates=c(
    "Age"
  ),
  group="Male",
  groupLabels = c("0", "1"),
  data=replicationData
)

congenialPartialFit <- congenialFun(
  measurementFit=list(partialInvarianceFitBPAQ, partialInvarianceFitSD3), 
  covariates=c(
    "Age"
  ),
  group="Male",
  groupLabels = c("0", "1"),
  data=replicationData
)

congenialFirstOrderFit <- congenialFun(
  measurementFit=list(partialInvarianceFitBPAQ, partialFirstOrderFit), 
  covariates=c(
    "Age"
  ),
  group="Male",
  groupLabels = c("0", "1"),
  data=replicationData
)

congenialSingleGroup <- congenialFun(
  measurementFit=list(responseFit, firstOrderFit), 
  covariates=c(
    "Male",
    "Age"
  ),
  data=replicationData
)
```

##### HTML

```{r}

invarianceFitsSD3 <- list(
  Configural = configuralInvarianceFitSD3,
  Metric = metricInvarianceFitSD3,
  Scalar = scalarInvarianceFitSD3,
  Partial = partialInvarianceFitSD3
)

invarianceTableSD3 <- purrr::imap_dfr(
  invarianceFitsSD3,
  function(fit, modelName) {
    
    indices <- fitMeasures(
      fit,
      fit.measures = c(
        "cfi.robust",
        "rmsea.robust",
        "srmr"
      ),
      baseline.model = nullFitSD3
    )
    
    tibble::as_tibble_row(
      c(list(Model = modelName), as.list(indices))
    )
  }
) %>%
  mutate(
    across(
      c(cfi.robust, rmsea.robust, srmr),
      ~ .x - .x[c(NA_integer_, 1L, 2L, 2L)],
      .names = "delta_{.col}"
    ),
    across(
      where(is.numeric),
      ~ ifelse(
        is.na(.x),
        NA_character_,
        sub("^(-?)0\\.", "\\1.", sprintf("%.4f", .x))
      )
    ),
    Panel = "SD3"
  )

invarianceFitsBPAQ <- list(
  Configural = configuralInvarianceFitBPAQ,
  Metric = metricInvarianceFitBPAQ,
  Scalar = scalarInvarianceFitBPAQ,
  Partial = partialInvarianceFitBPAQ
)

invarianceTableBPAQ <- purrr::imap_dfr(
  invarianceFitsBPAQ,
  function(fit, modelName) {
    
    indices <- fitMeasures(
      fit,
      fit.measures = c(
        "cfi.robust",
        "rmsea.robust",
        "srmr"
      ),
      baseline.model = nullFitBPAQ
    )
    
    tibble::as_tibble_row(
      c(list(Model = modelName), as.list(indices))
    )
  }
) %>%
  mutate(
    across(
      c(cfi.robust, rmsea.robust, srmr),
      ~ .x - .x[c(NA_integer_, 1L, 2L, 2L)],
      .names = "delta_{.col}"
    ),
    across(
      where(is.numeric),
      ~ ifelse(
        is.na(.x),
        NA_character_,
        sub("^(-?)0\\.", "\\1.", sprintf("%.4f", .x))
      )
    ),
    Panel = "BPAQ"
  )

invarianceTable <- dplyr::bind_rows(invarianceTableBPAQ, invarianceTableSD3)

invarianceGT <- invarianceTable %>%
  dplyr::select(
    Model,
    Panel,
    cfi.robust, delta_cfi.robust,
    rmsea.robust, delta_rmsea.robust,
    srmr, delta_srmr
  ) %>%
  gt::gt(
    rowname_col = "Model",
    groupname_col = "Panel"
  ) %>%
  gt::cols_label(
    cfi.robust = "CFI",
    rmsea.robust = "RMSEA",
    srmr = "SRMR",
    delta_cfi.robust = "ΔCFI",
    delta_rmsea.robust = "ΔRMSEA",
    delta_srmr = "ΔSRMR"
  ) %>%
  gt::tab_stubhead(label = "") %>%
  gt::fmt_markdown(
    columns = -Model
  ) %>%
  gt::cols_align(
    align = "center",
    columns = -Model
  ) %>%
  gt::sub_missing(
    columns = -Model,
    missing_text = "—"
  ) %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(
      groups = everything()
    )
  ) %>%
  gt::tab_options(
    table.font.names = c("Verdana", "Arial", "sans-serif"),
    table.font.size = gt::px(11),
    column_labels.font.weight = "bold",
    column_labels.border.top.width = gt::px(0),
    column_labels.border.bottom.width = gt::px(1),
    table_body.hlines.width = gt::px(0)
  )

invarianceGT

if (export) {
  
  invarianceGT_png <- invarianceGT %>%
    gt::tab_options(
      table.width = gt::px(624)
    )
    
  gt::gtsave(
    invarianceGT_png,
    filename = "../Tables/invarianceTable.png",
    zoom = 3.125,
    expand = 0
  )
  
}
```

##### LaTeX

```{r}

if (export) {
  
  # Convert one HTML-formatted result cell to LaTeX
  toLatexCell <- function(x) {
    if (is.na(x)) {
      return("\\textemdash{}")
    }
    
    x <- gsub("&lt;", "$<$", x, fixed = TRUE)
    
    # Replace each complete star sequence exactly once
    x <- gsub(
      "(\\*{1,3})",
      "{\\\\tiny \\1}",
      x,
      perl = TRUE
    )
    
    lines <- strsplit(x, "<br>", fixed = TRUE)[[1]]
    
    paste0(
      "\\makecell{",
      paste(lines, collapse = " \\\\ "),
      "}"
    )
  }
  
  invarianceTableLatex <- invarianceTable %>%
    mutate(
      across(
        -c(Model, Panel),
        \(x) vapply(x, toLatexCell, character(1))
      )
    )
  
  panelSizes <- table(invarianceTable$Panel)
  
  nBPAQ <- unname(panelSizes["BPAQ"])
  nSD3  <- unname(panelSizes["SD3"])
  
  invarianceKable <- invarianceTableLatex %>%
    dplyr::select(
      Model,
      cfi.robust, delta_cfi.robust,
      rmsea.robust, delta_rmsea.robust,
      srmr, delta_srmr
    ) %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", rep("c", 6)),
      col.names = c(
        "BPAQ",
        "CFI", "\\Delta CFI",
        "RMSEA", "\\Delta RMSEA",
        "SRMR", "\\Delta SRMR"
      )
    ) %>%
    kableExtra::pack_rows(
      "SD3",
      start_row = nBPAQ + 1,
      end_row = nBPAQ + nSD3,
      bold = TRUE,
      hline_after = FALSE,
      extra_latex_after = "\\midrule ",
      indent = FALSE,
      escape = FALSE,
      latex_align = "@{}l@{}"
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(invarianceTable) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(invarianceKable),
    "../Tables/invarianceTable.tex"
  )

}
```

#### Reliability

```{r}

bpaqColumns <- names(unlist(responseAlphaReliability))
sd3Columns  <- names(unlist(predictorAlphaReliability))

reliabilityTable <- data.frame(
  Factor = c(
    bpaqColumns,
    sd3Columns
  ),
  Alpha = c(
    unname(unlist(responseAlphaReliability)),
    unname(unlist(predictorAlphaReliability))
  ),
  Omega = c(
    unname(unlist(responseOmegaReliability)),
    unname(unlist(predictorOmegaReliability))
  )
) %>%
  mutate(
    across(
      c(Alpha, Omega),
      ~ sprintf("%.3f", .x)
    )
  ) %>%
  pivot_longer(
    cols = c(Alpha, Omega),
    names_to = "Reliability",
    values_to = "Estimate"
  ) %>%
  pivot_wider(
    names_from = Factor,
    values_from = Estimate
  )


reliabilityGT <- reliabilityTable %>%
  mutate(
    Reliability = recode(
      Reliability, 
      "Alpha" = "α",
      "Omega" = "ω"
    )
  ) %>%
  gt::gt(
    rowname_col = "Reliability"
  ) %>%
  gt::tab_stubhead(label = "Reliability") %>%
  gt::tab_spanner(
    label = "BPAQ",
    columns = all_of(bpaqColumns)
  ) %>%
  gt::tab_spanner(
    label = "SD3",
    columns = all_of(sd3Columns)
  ) %>%
  gt::fmt_markdown(
    columns = -Reliability
  ) %>%
  gt::cols_align(
    align = "center",
    columns = -Reliability
  ) %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(
      groups = everything()
    )
  ) %>%
  gt::tab_options(
    table.font.names = c("Verdana", "Arial", "sans-serif"),
    table.font.size = gt::px(11),
    column_labels.font.weight = "bold",
    column_labels.border.top.width = gt::px(0),
    column_labels.border.bottom.width = gt::px(1),
    table_body.hlines.width = gt::px(0)
  )

reliabilityGT

if(export) {
  
  reliabilityGT_png <- reliabilityGT %>%
    gt::tab_options(
      table.width = gt::px(624)
    )
    
  gt::gtsave(
    reliabilityGT_png,
    filename = "../Tables/reliabilityTable.png",
    zoom = 3.125,
    expand = 0
  )
  
  reliabilityKable <- reliabilityTable %>%
    mutate(
      Reliability = recode(
        Reliability, 
        "Alpha" = "\\alpha",
        "Omega" = "\\omega"
      )
    ) %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", rep("c", 7))
    ) %>%
    kableExtra::add_header_above(
      header = c(
        " " = 1,
        "BPAQ" = length(bpaqColumns),
        "SD3" = length(sd3Columns)
      ),
      bold = TRUE
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(reliabilityTable) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(reliabilityKable),
    "../Tables/reliabilityTable.tex"
  )
  
}
```

#### Latent covariances

```{r}

congenialSingleGroup <- congenialFun(
  measurementFit=list(responseFit, firstOrderFit), 
  covariates=c(
    "Male",
    "Age"
  ),
  data=replicationData
)

# --------------------------- PREPARE TABLE ---------------------------

psiMatrix <- cov2cor(
  lavInspect(congenialSingleGroup, "est")$psi
)

nVariables <- nrow(psiMatrix)

psiFormatted <- matrix(
  sprintf("%.2f", psiMatrix),
  nrow = nVariables,
  dimnames = dimnames(psiMatrix)
)

# Display the lower triangle, with dashes on the diagonal
psiFormatted[upper.tri(psiFormatted)] <- ""
diag(psiFormatted) <- "—"

variableLabels <- paste0(
  seq_len(nVariables),
  ". ",
  rownames(psiMatrix)
)

colnames(psiFormatted) <- as.character(seq_len(nVariables))

psiTable <- data.frame(
  Variable = variableLabels,
  psiFormatted,
  check.names = FALSE,
  row.names = NULL
)

# ------------------------------- GT ----------------------------------

  psiGT <- psiTable %>%
    gt::gt(
      rowname_col = "Variable"
    ) %>%
    gt::tab_stubhead(
      label = "Variable"
    ) %>%
    gt::cols_align(
      align = "center",
      columns = -Variable
    ) %>%
    gt::tab_options(
      table.font.names = c("Verdana", "Arial", "sans-serif"),
      table.font.size = gt::px(11),
      column_labels.font.weight = "bold",
      column_labels.border.top.width = gt::px(0),
      column_labels.border.bottom.width = gt::px(1),
      table_body.hlines.width = gt::px(0)
    )

psiGT

if (export) {
    
  psiGT_png <- psiGT %>%
    gt::tab_options(
      table.width = gt::px(624)
    )
  
  gt::gtsave(
    psiGT_png,
    filename = "../Tables/psiTable.png",
    zoom = 3.125,
    expand = 0
  )

# ------------------------------ LATEX --------------------------------

  psiTableLatex <- psiTable %>%
    mutate(
      across(
        -Variable,
        ~ gsub("—", "\\textemdash{}", .x, fixed = TRUE)
      )
    )
  
  psiKable <- psiTableLatex %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", rep("c", nVariables))
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(psiTableLatex) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(psiKable),
    "../Tables/psiTable.tex"
  )
  
  psiKable
  
}
```

#### Residual covariances

```{r}

set.seed(masterSeed)

psychopathyMeasurement <- paste(
  'Reference =~ ', paste(coreItems, collapse = " + "), ' \n ',
  'Machiavellianism =~ ', paste(machiavellianismItems, collapse = " + "), ' \n ',
  'Narcissism =~ ', paste(narcissismItems, collapse = " + "), ' \n ',
  'Machiavellianism ~~ 0*Reference \n ',
  'Narcissism ~~ 0*Reference \n '
)

psychopathyFit <- cfa(
  psychopathyMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  std.lv = TRUE,
  data = replicationData
)

narcissismMeasurement <- paste(
  'Reference =~ ', paste(coreItems, collapse = " + "), ' \n ',
  'Machiavellianism =~ ', paste(machiavellianismItems, collapse = " + "), ' \n ',
  'Psychopathy =~ ', paste(psychopathyItems, collapse = " + "), ' \n ',
  'Machiavellianism ~~ 0*Reference \n ',
  'Psychopathy ~~ 0*Reference \n '
)

narcissismFit <- cfa(
  narcissismMeasurement,  
  estimator = "MLR",
  meanstructure = TRUE,
  std.lv = TRUE,
  data = replicationData
)

machiavellianismTable <- standardizedSolution(bifactorFit)

machiavellianismTable$reference <- "Mach"

psychopathyTable <- standardizedSolution(psychopathyFit)

psychopathyTable$reference <- "Psych"

narcissismTable <- standardizedSolution(narcissismFit)

narcissismTable$reference <- "Narc"

covarianceTable <- rbind(machiavellianismTable, psychopathyTable, narcissismTable)

covarianceTable <- covarianceTable %>%
  mutate(
    lhs = recode(
      lhs, 
      "Reference" = "Ref", 
      "Machiavellianism" = "Mach",
      "Psychopathy" = "Psych",
      "Narcissism" = "Narc"
    ),
    rhs = recode(
      rhs, 
      "Reference" = "Ref", 
      "Machiavellianism" = "Mach",
      "Psychopathy" = "Psych",
      "Narcissism" = "Narc"
    )
  ) %>%
  filter(
    (lhs %in% c("Psych", "Mach", "Narc")) &
      (op == "~~") & 
      (rhs %in% c("Psych", "Mach", "Narc")) 
      & lhs != rhs
  ) %>%
  mutate(
    stars = case_when(
      pvalue <= 0.001 ~ "***",
      pvalue <= 0.01  ~ "**",
      pvalue <= 0.05  ~ "*",
      .default = ""
    ),
    pFormatted = if_else(
      pvalue < 0.001,
      "&lt;.001",
      paste0("=", sub("^0", "", sprintf("%.3f", pvalue)))
    ),
    Estimate = sprintf(
        "%.3f%s<br>(%.3f)<br>p%s",
        est.std, stars, se, pFormatted
    ),
    Term = paste0("Cor(", lhs, ", ", rhs, " | ", reference, ")")
  ) %>%
  dplyr::select(Term, Estimate) %>%
  pivot_wider(
    names_from = Term,
    values_from = Estimate
  )

covarianceTable

rm(psychopathyFit)
rm(narcissismFit)
```

##### HTML

```{r}

covarianceGT <- covarianceTable %>%
  gt::gt() %>%
  gt::fmt_markdown(columns = everything()) %>%
  gt::cols_align(
    align = "center",
    columns = everything()
  ) %>%
  gt::tab_options(
    table.font.names = c("Verdana", "Arial", "sans-serif"),
    table.font.size = gt::px(11),
    column_labels.font.weight = "bold",
    column_labels.border.top.width = gt::px(0),
    column_labels.border.bottom.width = gt::px(1),
    table_body.hlines.width = gt::px(0)
  )

covarianceGT

if(export) {
    
  covarianceGT_png <- covarianceGT %>%
    gt::tab_options(
      table.width = gt::px(624)
    )
  
  gt::gtsave(
    covarianceGT_png,
    filename = "../Tables/covarianceTable.png",
    zoom = 3.125,
    expand = 0
  )

}
```

##### LaTeX

```{r}

if(export) {
    
  # Convert one HTML-formatted result cell to LaTeX
  toLatexCell <- function(x) {
    if (is.na(x)) {
      return("\\textemdash{}")
    }
    
    x <- gsub("&lt;", "$<$", x, fixed = TRUE)
    
    # Replace each complete star sequence exactly once
    x <- gsub(
      "(\\*{1,3})",
      "{\\\\tiny \\1}",
      x,
      perl = TRUE
    )
    
    lines <- strsplit(x, "<br>", fixed = TRUE)[[1]]
    
    paste0(
      "\\makecell{",
      paste(lines, collapse = " \\\\ "),
      "}"
    )
  }
  
  covarianceTableLatex <- covarianceTable %>%
    mutate(
      across(
        everything(),
        \(x) vapply(x, toLatexCell, character(1))
      )
    )
  
  tableNotes <- r"(Entries are standardized residual covariances (i.e., partial correlations) from the bifactor ($\\mathrm{S}-1$) measurement model under alternative reference facets, with standard errors in parentheses. Mach = Machiavellianism; Psych = Psychopathy; Narc = Narcissism. The factor following the vertical bar corresponds to the bifactor reference facet. Models were estimated by robust maximum likelihood. * p < .05; ** p < .01; *** p < .001.)"
  
  covarianceKable <- covarianceTableLatex %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = rep("c", 3)
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(covarianceKable),
    "../Tables/covarianceTable.tex"
  )

}
```

#### Higher order model

```{r}

set.seed(masterSeed)

higherOrderMeasurement <- paste(
  'Machiavellianism =~ ', paste(machiavellianismItems, collapse = " + "), ' \n ',
  'Psychopathy =~ ', paste(psychopathyItems, collapse = " + "), ' \n ',
  'Narcissism =~ ', paste(narcissismItems, collapse = " + "), ' \n ',
  'Core =~ Machiavellianism + Psychopathy + Narcissism'
)

higherOrderFit <- cfa(
  higherOrderMeasurement,  
  data = replicationData,
  estimator = "MLR",
  meanstructure = TRUE,
  std.lv = TRUE
)

communalities <- lavInspect(higherOrderFit, "rsquare")

higherOrderTable <- standardizedSolution(higherOrderFit) %>%
  dplyr::select(-c(ci.lower, ci.upper)) %>%
  filter((op == "=~") & (rhs %in% c("Psychopathy", "Machiavellianism", "Narcissism"))) %>%
  mutate(
    h2 = sprintf(
      "%.3f",
      unname(communalities[rhs])
    ),
    stars = case_when(
      pvalue <= 0.001 ~ "***",
      pvalue <= 0.01  ~ "**",
      pvalue <= 0.05  ~ "*",
      .default = ""
    ),
    pFormatted = if_else(
      pvalue < 0.001,
      "&lt;.001",
      paste0("=", sub("^0", "", sprintf("%.3f", pvalue)))
    ),
    lambda = sprintf(
      "%.3f%s<br>(%.3f)<br>p%s",
      est.std, stars, se, pFormatted
    )
  ) %>%
  dplyr::select(lhs, rhs, lambda, h2) %>%
  pivot_wider(
    names_from = rhs,
    values_from = c(lambda, h2)
  )

higherOrderTable

rm(higherOrderFit)

```

##### HTML

```{r}

higherOrderGT <- higherOrderTable %>%
  gt::gt(
    rowname_col = "lhs"
  ) %>%
  gt::tab_spanner(
    label = "Machiavellianism",
    columns = ends_with("_Machiavellianism")
  ) %>%
  gt::tab_spanner(
    label = "Psychopathy",
    columns = ends_with("_Psychopathy")
  ) %>%
  gt::tab_spanner(
    label = "Narcissism",
    columns = ends_with("_Narcissism")
  ) %>%
  gt::cols_label(
    starts_with("lambda") ~ "λ",
    starts_with("h2") ~ "h²"
  ) %>%
  gt::tab_stubhead(label = "") %>%
  gt::fmt_markdown(
    columns = -lhs
  ) %>%
  gt::cols_align(
    align = "center",
    columns = -lhs
  ) %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(
      groups = everything()
    )
  ) %>%
  gt::tab_options(
    table.font.names = c("Verdana", "Arial", "sans-serif"),
    table.font.size = gt::px(11),
    column_labels.font.weight = "bold",
    column_labels.border.top.width = gt::px(0),
    column_labels.border.bottom.width = gt::px(1),
    table_body.hlines.width = gt::px(0)
  )

higherOrderGT

if(export) {
  
  higherOrderGT_png <- higherOrderGT %>%
    gt::tab_options(
      table.width = gt::px(624)
    )
  
  gt::gtsave(
    higherOrderGT_png,
    filename = "../Tables/higherOrderTable.png",
    zoom = 3.125,
    expand = 0
  )
  
}
```

##### LaTeX

```{r}

if(export) {
    
  # Convert one HTML-formatted result cell to LaTeX
  toLatexCell <- function(x) {
    if (is.na(x)) {
      return("\\textemdash{}")
    }
    
    x <- gsub("&lt;", "$<$", x, fixed = TRUE)
    
    # Replace each complete star sequence exactly once
    x <- gsub(
      "(\\*{1,3})",
      "{\\\\tiny \\1}",
      x,
      perl = TRUE
    )
    
    lines <- strsplit(x, "<br>", fixed = TRUE)[[1]]
    
    paste0(
      "\\makecell{",
      paste(lines, collapse = " \\\\ "),
      "}"
    )
  }
  
  higherOrderTableLatex <- higherOrderTable %>%
    mutate(
      across(
        -c(lhs),
        \(x) vapply(x, toLatexCell, character(1))
      )
    ) %>%
    dplyr::select(
      1,       # lhs
      2, 5,    # Machiavellianism: lambda, h2
      3, 6,    # Psychopathy: lambda, h2
      4, 7     # Narcissism: lambda, h2
    )
  
  higherOrderKable <- higherOrderTableLatex %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", rep("c", 6)),
      col.names = c(
        "",
        rep(c("\\lambda", "$\\mathrm{h}^2$"), times=3)
      )
    ) %>%
    kableExtra::add_header_above(
      c(
        " " = 1,
        "Machiavellianism" = 2,
        "Psychopathy" = 2,
        "Narcissism" = 2
      ),
      escape = FALSE,
      bold = TRUE
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(higherOrderTable) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(higherOrderKable),
    "../Tables/higherOrderTable.tex"
  )

}
```

## Confirmatory models

### Fit functions

#### Checks

```{r}

checkConvergence <- function(fit) {
  isTRUE(lavInspect(fit, "converged")) &&
    isTRUE(lavInspect(fit, "post.check"))
}

checkPD <- function(fit) {
  tryCatch({
    acovs <- attr(
      lavPredict(fit, acov = "standard"),
      "acov"
    )
    
    if (is.null(acovs) || length(acovs) == 0L) return(FALSE)
    
    all(vapply(acovs, function(acov) {
      if (!is.matrix(acov) || any(!is.finite(acov))) return(FALSE)
      chol(acov)
      TRUE
    }, logical(1)))
  }, error = function(e) FALSE)
}

checkFactorAlignment <- function(fullFit, bootFit) {
  
  lambdaFull <- lavInspect(fullFit, "est")[[1L]]$lambda
  lambdaBoot <- lavInspect(bootFit, "est")[[1L]]$lambda
  
  if (!setequal(rownames(lambdaFull), rownames(lambdaBoot)) ||
      !setequal(colnames(lambdaFull), colnames(lambdaBoot))) {
    stop("The fits do not contain the same items and factors.")
  }
  
  lambdaBoot <- lambdaBoot[
    rownames(lambdaFull),
    colnames(lambdaFull),
    drop = FALSE
  ]
  
  numerator <- colSums(lambdaFull * lambdaBoot)
  denominator <- sqrt(colSums(lambdaFull^2) * colSums(lambdaBoot^2))
  
  if (any(!is.finite(denominator) | denominator == 0)) {
    stop("Cannot calculate a cosine for a zero-length loading vector.")
  }
  
  numerator / denominator
}
```

#### VWLE fun

```{r}

vwleFun <- function(response, g, s, covariates, lambdaMatrix, covMatrix, coefMatrix, stdVec=NULL) {
  
  # Function assumes matrices are properly ordered for multiplication downstream
  
  gBase <- unique(sub(":.*$", "", g)) #No interaction terms
  
  # ----------------- REDUCED FORM COVARIANCES -----------------------
  
  
  phi_g <- covMatrix[rownames(covMatrix) %in% g, colnames(covMatrix) %in% g, drop=FALSE]
  
  phi_s <- covMatrix[rownames(covMatrix) %in% c(unlist(s), covariates), colnames(covMatrix) %in% c(unlist(s), covariates), drop=FALSE]
  
  phi_gs <- covMatrix[rownames(covMatrix) %in% g, colnames(covMatrix) %in% c(unlist(s), covariates), drop=FALSE]
  
  # ----------------- LOADINGS -----------------------
  
  lambda_x <- lambdaMatrix[, !(colnames(lambdaMatrix) %in% gBase), drop = FALSE]
  
  lambda_x_xi <- lambdaMatrix[, gBase, drop = FALSE]
  
  lambda_xi <- solve(t(lambda_x) %*% lambda_x) %*% t(lambda_x) %*% lambda_x_xi

  # Match second order loadings to corresponding columns in the phi_s matrix. We assume the latent manifest interactions have the same loading that the latent variable alone, on the grounds of no cross products: 
  # xi =  lambda * xi_g + xi_s --> xi * m = lambda * xi_g * m + xi_s * m
  
  loadings <- sapply(
    colnames(phi_s), 
    FUN = function(x) {
      base <- sub(":.*$", "", x)
      if(base %in% rownames(lambda_xi)) {
        return(lambda_xi[base,])
      } else {
        return(0)
      }
    }
  )
  
  lambda_xi <- matrix(
    data=rep(loadings, times=ncol(phi_g)), 
    nrow=nrow(phi_s), 
    ncol=ncol(phi_g),
    dimnames = list(rownames(phi_s), colnames(phi_g))
  )
  
  lambda_xi[
    outer(
      sub("^[^:]+", "", rownames(lambda_xi)),
      sub("^[^:]+", "", colnames(lambda_xi)),
      `!=`
    )
  ] <- 0
  
  # Make first order loading matrix consistent with post-measurement standardization 
  if (!is.null(stdVec)) {
    
    unscaled <- setdiff(covariates, names(stdVec))
    stdVec[unscaled] <- 1
    
    rowSD <- stdVec[sub(":.*$", "", rownames(lambda_xi))]
    colSD <- stdVec[sub(":.*$", "", colnames(lambda_xi))]
    
    D_s <- diag(rowSD, nrow = length(rowSD))
    D_g <- diag(colSD, nrow = length(colSD))
    
    dimnames(D_s) <- list(rownames(lambda_xi), rownames(lambda_xi))
    dimnames(D_g) <- list(colnames(lambda_xi), colnames(lambda_xi))
    
    lambda_xi <- solve(D_s) %*% lambda_xi %*% D_g
  }
  
  # ----------------- FIRST ORDER COVARIANCES -----------------------
  
  firstTerm <- lambda_xi %*% phi_g %*% t(lambda_xi)
  
  secondTerm <- lambda_xi %*% phi_gs
  
  thirdTerm <- t(phi_gs) %*% t(lambda_xi)
  
  phi_1 <- firstTerm + secondTerm + thirdTerm + phi_s
  
  # ----------------- COEFFICIENTS -----------------------
  
  gamma <- coefMatrix[rownames(coefMatrix) %in% response, colnames(coefMatrix) %in% c(g, unlist(s), covariates), drop = FALSE]
  
  gamma_g <- gamma[, colnames(gamma) %in% g, drop = FALSE]
  
  gamma_s <- gamma[, colnames(gamma) %in% c(unlist(s), covariates), drop = FALSE]
  
  
  # ----------------- ESTIMATOR -----------------------

  cov_eta_xi <- 
    gamma_g %*% (phi_g %*% t(lambda_xi) + phi_gs) +
    gamma_s %*% (t(phi_gs) %*% t(lambda_xi) + phi_s)
  
  phi <- covMatrix[rownames(covMatrix) %in% c(g, unlist(s), covariates), colnames(covMatrix) %in% c(g, unlist(s), covariates), drop = FALSE]
  
  cov_eta_reduced <- gamma %*% phi
  
  vwle <- do.call(
    cbind,
    lapply(
      X = unique(sub(":.*$", "", unlist(s))),
      FUN = function(i) {
        
        s_j <- unlist(s)[sub(":.*$", "", unlist(s)) == i]
        
        g_i <- g[vapply(
          s,
          function(x) any(x %in% s_j),
          logical(1)
        )]
        
        vwle_j <- do.call(
          rbind,
          lapply(
            seq_len(nrow(gamma)),
            function(r) {
              
              minj <-
                !(colnames(phi) %in% c(g_i, s_j)) &
                gamma[r, colnames(phi)] != 0
              
              cov_j <- cov_eta_xi[r, s_j, drop = FALSE]
              
              var_j <- phi_1[s_j, s_j, drop = FALSE]
              
              if (!any(minj)) {
                return(cov_j %*% solve(var_j))
              }
              
              cov_minj <- cov_eta_reduced[r, minj, drop = FALSE]
              
              var_minj <- phi[minj, minj, drop = FALSE]
              
              prec_minj <- solve(var_minj)
              
              cov_j_minj <-
                phi[s_j, minj, drop = FALSE] +
                lambda_xi[s_j, g_i, drop = FALSE] %*%
                phi[g_i, minj, drop = FALSE]
              
              (cov_j - cov_minj %*% prec_minj %*% t(cov_j_minj)) %*%
                solve(var_j - cov_j_minj %*% prec_minj %*% t(cov_j_minj))
            }
          )
        )
      }
    )
  )
  
  vwle <- vwle[, unlist(s), drop = FALSE]
  
  vwle_std <- do.call(
    rbind, 
    lapply(
      X=1:nrow(vwle), 
      FUN=function(i){
        vwle[i,] * sqrt(diag(phi_1))[sub(":.*$", "", unlist(s))]
      }
    )
  )
  
  rownames(vwle_std) <- rownames(vwle)
  
  if (!is.null(stdVec)) {
    vwle <- vwle %*% solve(
      D_s[colnames(vwle), colnames(vwle), drop = FALSE]
    )
  }
  
  return(list(lvl = vwle, std = vwle_std))
}
```

#### Full fun

```{r}

effectSizesFun <- function(structuralFit) {
  
  responseNames <- lavNames(structuralFit, "ov.y")
  
  predictorNames <- lavNames(structuralFit, "ov.x")
  
  coefMatrix <- as.matrix(lavInspect(structuralFit, "est")$beta[responseNames, predictorNames, drop=FALSE])
  
  responseVar <- diag(as.matrix(lavInspect(structuralFit, "cov.all"))[responseNames, responseNames, drop=FALSE])
  
  predictorMatrix <- as.matrix(lavInspect(structuralFit, "cov.all"))[predictorNames, predictorNames, drop=FALSE]
  
  
  etaSemi <- do.call(
    rbind,
    lapply(
      1:nrow(coefMatrix),
      function(i) {
        betas <- coefMatrix[i, , drop=TRUE]
        mask <- betas != 0
        
        etaSemi <- coefMatrix[i, , drop=FALSE]
        if (!any(mask)) return(etaSemi)
        
        etaSemi[mask] <- betas[mask]^2 / 
          (responseVar[i] * diag(solve(predictorMatrix[mask, mask, drop=FALSE])))
        
        return(etaSemi)
      }
    )
  )
  
}

rSquaredFun <- function(structuralFit) {
  
  responseNames <- lavNames(structuralFit, "ov.y")
  predictorNames <- lavNames(structuralFit, "ov.x")
  
  coefMatrix <- as.matrix(lavInspect(structuralFit, "est")$beta[responseNames, predictorNames, drop=FALSE])
  responseMatrix <- as.matrix(lavInspect(structuralFit, "cov.all"))[responseNames, responseNames, drop=FALSE]
  predictorMatrix <- as.matrix(lavInspect(structuralFit, "cov.all"))[predictorNames, predictorNames, drop=FALSE]
  
  stdMatrix <- 
    diag(1 / sqrt(diag(responseMatrix)), nrow = length(responseNames)) %*% 
    coefMatrix %*% 
    diag(sqrt(diag(predictorMatrix)), nrow = length(predictorNames))
  
  rownames(stdMatrix) <- responseNames
  colnames(stdMatrix) <- predictorNames
  
  corMatrix <- cov2cor(as.matrix(lavInspect(structuralFit, "cov.all")))[responseNames, predictorNames, drop=FALSE]
  
  return(list(corMatrix=corMatrix, stdMatrix=stdMatrix))
}

plausibleFun <- function(draw, structuralModel, measurementFit, VWLE=FALSE, g, s, covariatesVWLE, fullSample = TRUE, data, masterSeed) {
  
  set.seed(masterSeed + draw)

  PVs <- plausibleValues(
    measurementFit,
    nDraws = 1,
    seed = masterSeed + draw,
    method = "Regression"
  )[[1]]
  
  caseIdx <- PVs$case.idx
  
  stdVec <- vapply(PVs, sd, numeric(1))
  
  PVs <- PVs %>%
    dplyr::select(all_of(lavNames(measurementFit, "lv"))) %>%
    mutate(
      across(
        everything(),
        ~ as.numeric(scale(.x))
      )
    )
  
  df <- cbind(data[caseIdx, , drop = FALSE], PVs)
  
  structuralFit <- sem(
    model=structuralModel,
    estimator="MLR",
    meanstructure=TRUE,
    data = df
  )
  
  if (!checkConvergence(structuralFit)) return(NULL)
  
  response <- c(
    lavNames(structuralFit, type = "ov.y"),
    lavNames(structuralFit, type = "lv.y")
  )
  
  # ------------------------VWLE START-----------------------------
  
  if(VWLE) {
    
    coefMatrix <- as.matrix(lavInspect(structuralFit, "est")$beta)[response, ] #Ensure response order
    
    order <- colnames(coefMatrix) #Define predictor order
    
    covMatrix <- as.matrix(lavInspect(structuralFit, "cov.all"))
    
    covMatrix <- covMatrix[order, order, drop=FALSE]
    
    # Loadings are assumed fixed (conditioned on) for the two stage estimation procedure
    lambdaMatrix <- as.matrix(lavInspect(measurementFit, "est")$`0`$lambda)[lavNames(measurementFit, type="ov.ind"), lavNames(measurementFit, type="lv")]
    
    vwleResult <- vwleFun(
      response=response, 
      g=g, 
      s=s, 
      covariates=covariatesVWLE, 
      lambdaMatrix=lambdaMatrix,
      covMatrix=covMatrix,
      coefMatrix=coefMatrix,
      stdVec=stdVec
    )
    
    vwleList <- lapply(
      seq_len(nrow(vwleResult$std)), 
      function(i) {
        out <- lapply(
          seq_len(ncol(vwleResult$std)), 
          function(j){
            return(vwleResult$std[i,j, drop=FALSE])
          }
        )
        return(out)
      }
    )
    
    vwleList <- unlist(vwleList, recursive=FALSE)
    
    vwleRows <- do.call(
      rbind,
      lapply(
        vwleList,
        function(i) {
          left <- rownames(i)
          right <- colnames(i)
          
          target <- coefMatrix[left, right]
          
          if(target == 0) {
            # Do not extract the VWLE if a specific component is absent from the corresponding equation, otherwise the result corresponds to the general component translation into first-order coordinates, which is incomplete for the measured construct.
            return(NULL)
          } else {
            vwleRows <- tibble::tibble(
              lhs = left,
              op = "~",
              rhs = paste0(right, "VWLE"),
              est = as.numeric(i)
            )
            return(vwleRows)
          }
        }
      )
    )
    
  } else {
    vwleRows <- NULL
  }
  
  # ------------------------VWLE END-----------------------------
  
  if(fullSample) {
    
    effectSizes <- effectSizesFun(structuralFit)
    r2Matrices <- rSquaredFun(structuralFit)
    
    estimates <- parameterEstimates(structuralFit) %>%
      rowwise() %>%
      mutate(
        etaSemi = ifelse(
          op == "~" && lhs %in% response,
          effectSizes[lhs, rhs, drop=TRUE],
          NA
        )
      ) %>%
      ungroup()
    
    nobs <- lavInspect(structuralFit, "nobs")
    
    nobsRows <- tibble::tibble(
      lhs = response,
      op = "gof",
      rhs = rep("N", times = length(response)),
      est = rep(nobs, length(response))
    )
    
    estimates <- dplyr::bind_rows(
      estimates,
      vwleRows,
      nobsRows
    )
    
  } else {
    
    estimates <- dplyr::bind_rows(
      parameterEstimates(structuralFit),
      vwleRows
    ) %>%
      mutate(etaSemi = NA_real_)
    
    r2Matrices <- NULL
    
  }
  
  return(list(estimates=estimates, r2Matrices=r2Matrices))
  
}


# -------------------------------- PROCESS RESULTS ------------------------------------

processFunPV <- function(structuralFit) {
  
  structuralFit <- Filter(Negate(is.null), structuralFit)
  
  if (length(structuralFit) == 0L) {
    stop("No successful PV fits.")
  }
  
  estimates <- do.call(
    rbind,
    lapply(
      seq_along(structuralFit),
      function(i) {
        structuralFit[[i]][["estimates"]]
      }
    )
  )
  
  if(!is.null(structuralFit[[1]][["r2Matrices"]])) {
    pooledCorMatrix <- Reduce(
      "+",
      lapply(
        seq_along(structuralFit),
        function(i) {
          structuralFit[[i]][["r2Matrices"]][["corMatrix"]]
        }
      )
    ) / length(structuralFit)
    
    pooledStdMatrix <- Reduce(
      "+",
      lapply(
        seq_along(structuralFit),
        function(i) {
          structuralFit[[i]][["r2Matrices"]][["stdMatrix"]]
        }
      )
    ) / length(structuralFit)
    
    r2 <- rowSums(pooledCorMatrix * pooledStdMatrix)
    
    r2Rows <- tibble::tibble(
      lhs = names(r2),
      op = "gof",
      rhs = rep("R2", times = length(r2)),
      Estimate = as.numeric(r2)
    )
  } else {
    r2Rows <- NULL
  }

  
  processed <- estimates %>%
    dplyr::filter(
      !is.na(est),
      !is.na(se) | op == "gof" | endsWith(rhs, "VWLE")
    ) %>%
    group_by(lhs, op, rhs) %>%
    summarise(
      M = n(),
      Eta2 = mean(etaSemi),
      Estimate = mean(est, na.rm=TRUE),
      WithinVar = mean(se^2, na.rm=TRUE),
      BetweenVar = var(est, na.rm=TRUE),
      .groups = "drop"
    ) %>%
    mutate(
      TotalVar = WithinVar + (1 + 1/M) * BetweenVar,
      SE = ifelse(op %in% c("~", "~1", ":=") & !(endsWith(rhs, "VWLE")), sqrt(TotalVar), NA),
      Z = ifelse(op %in% c("~", "~1", ":=") & !(endsWith(rhs, "VWLE")), Estimate / SE, NA),
      P = ifelse(op %in% c("~", "~1", ":=") & !(endsWith(rhs, "VWLE")), 2 * pnorm(abs(Z), lower.tail = FALSE), NA)
    ) %>%
    dplyr::bind_rows(r2Rows)
  
  return(processed)
  
}
```

#### Bootstrap fun

```{r}

bootFun <- function(draw, mDraws, structuralModel, measurementModel, fullMeasurement, VWLE=FALSE, g, s, covariatesVWLE, congenialCovariates=c("Age"), group=NULL, groupLabels=NULL, invariance=NULL, groupFree=NULL, data, masterSeed) {
  
  bootSeed <- masterSeed + draw * (mDraws + 1L)
  
  set.seed(bootSeed)
  
  idx <- sample.int(nrow(data), size = nrow(data), replace = TRUE)
  
  dataBoot <- data[idx, ]
  
  measurementFit <- lapply(
    seq_along(measurementModel),
    function(i) {
      measurementFit <- cfa(
        measurementModel[[i]],
        estimator = "ML",
        se = "none",
        test = "none",
        baseline = FALSE,
        std.lv = TRUE,
        meanstructure = TRUE,
        group=group,
        group.label = groupLabels,
        group.equal=invariance[[i]],
        group.partial=paste0(groupFree[[i]], "~ 1"),
        data = dataBoot
      )
    }
  )
  
  if (!all(sapply(measurementFit, checkConvergence)) || !all(sapply(measurementFit, checkPD))) return(NULL)

  # ------------------- CONGENIAL START ---------------------------
  
  congenialFit <- congenialFun(
    measurementFit=measurementFit, 
    covariates=congenialCovariates,
    group=group,
    groupLabels = groupLabels,
    data=dataBoot
  )
  
  if (!checkConvergence(congenialFit) || !checkPD(congenialFit)) return(NULL)
  
  cosine <- checkFactorAlignment(fullFit = fullMeasurement, bootFit = congenialFit)
  reversedFactors <- names(cosine)[cosine < 0]
  
  # ------------------- CONGENIAL END ---------------------------

  estimates <- lapply(
    X = 1:mDraws,
    plausibleFun,
    structuralModel=structuralModel,
    measurementFit=congenialFit,
    VWLE=VWLE,
    g=g, 
    s=s,
    covariatesVWLE=covariatesVWLE,
    fullSample=FALSE,
    data=dataBoot,
    masterSeed = bootSeed
  )
  
  estimates <- Filter(Negate(is.null), estimates)
  if (length(estimates) == 0L) return(NULL)
  
  estimates <- estimates <- dplyr::bind_rows(
    lapply(estimates, function(x) x[["estimates"]])
  ) %>%
    filter(
      op == "~" 
      | (op == "~1" & lhs %in% lavNames(lavaanify(structuralModel), type = "ov.y"))
    ) %>%
    dplyr::select(-c(ci.lower, ci.upper, pvalue)) %>%
    filter(
      !is.na(est),
      !is.na(se) | endsWith(rhs, "VWLE")
    ) %>%
    # Flip signs of reversed factors
    dplyr::mutate(
      rhsFactor = sub(":Male$", "", sub("VWLE$", "", rhs)),
      lhsSign = if_else(lhs %in% reversedFactors, -1, 1),
      rhsSign = if_else(rhsFactor %in% reversedFactors, -1, 1),
      est = dplyr::case_when(
        op %in% c("~", "~~") ~ est * lhsSign * rhsSign,
        op == "~1"          ~ est * lhsSign,
        TRUE                ~ est
      )
    ) %>%
    dplyr::select(-rhsFactor, -lhsSign, -rhsSign) %>%
    # Pool
    group_by(lhs, op, rhs) %>%
    summarise(
      M = n(),
      estBoot = mean(est),
      WithinVar = mean(se^2),
      BetweenVar = var(est),
      .groups = "drop"
    ) %>%
    mutate(
      TotalVar = WithinVar + (1 + 1/M) * BetweenVar, # Rubin MI total variance
      seBoot = sqrt(TotalVar)
    ) %>%
    dplyr::select(lhs, op, rhs, estBoot, seBoot)
  
  estimates <- dplyr::bind_rows(
    estimates,
    tibble::tibble(
      lhs = names(cosine),
      op = "cosine",
      rhs = "",
      estBoot = unname(cosine),
      seBoot = NA_real_
    )
  )
  
  estimates$draw <- draw
  
  return(estimates)
}


# -------------------------------- PROCESS RESULTS ------------------------------------

processFunBoot <- function(fullFit, bootFit) {
  
  by <- join_by(lhs, op, rhs)
  
  vwleBoot <- fullFit %>%
    right_join(bootFit, by=by) %>%
    filter(endsWith(rhs, "VWLE")) %>%
    group_by(lhs, op, rhs) %>%
    summarise(
      M=first(M),
      Estimate=first(Estimate),
      WithinVar=first(WithinVar),
      BetweenVar=first(BetweenVar),
      TotalVar=first(TotalVar),
      SE = sd(estBoot, na.rm=TRUE),
      Z = Estimate / SE,
      P = 2 * pnorm(abs(Z), lower.tail = FALSE),
      pBoot = mean(
        abs(estBoot - Estimate) >= abs(Estimate),
        na.rm = TRUE
      ),
      meanBoot = mean(estBoot, na.rm=TRUE),
      biasBoot = meanBoot - Estimate,
      bootSuccess = n_distinct(draw),
    ) %>%
    ungroup()
  
  
  structuralBoot <- fullFit %>%
    dplyr::select(lhs, op, rhs, Estimate, Z) %>%
    right_join(bootFit, by=by) %>%
    filter(!endsWith(rhs, "VWLE"), op != "cosine") %>%
    group_by(lhs, op, rhs) %>%
    mutate(
      zBoot = (estBoot - Estimate) / seBoot,
    ) %>%
    summarise(
      pBoot = mean(
        abs(zBoot) >= abs(first(Z)),
        na.rm = TRUE
      ),
      meanBoot = mean(estBoot, na.rm=TRUE),
      biasBoot = meanBoot - first(Estimate),
      bootSuccess = n_distinct(draw),
    ) %>%
    ungroup()
  
  jointFit <- fullFit %>%
    filter(!endsWith(rhs, "VWLE")) %>%
    left_join(structuralBoot, by = by) %>%
    dplyr::bind_rows(vwleBoot) %>%
    mutate(
      bootCount = attr(bootFit, "lastAttempt"),
      bootRate = bootSuccess / bootCount
    )
}
```

### Model 0 (Null)

#### Naïve sum score differences

```{r}

set.seed(masterSeed)

unconditionalModelBPAQ <- '
  PhysicalSumScore  ~ p0*1 + p1*Male
  VerbalSumScore    ~ v0*1 + v1*Male
  HostilitySumScore ~ h0*1 + h1*Male
  AngerSumScore     ~ a0*1 + a1*Male
  
  PhysicalMale  := p0 + p1
  VerbalMale    := v0 + v1
  HostilityMale := h0 + h1
  AngerMale     := a0 + a1

  PhysicalSumScore ~~ VerbalSumScore
  PhysicalSumScore ~~ HostilitySumScore
  PhysicalSumScore ~~ AngerSumScore
  VerbalSumScore ~~ HostilitySumScore
  VerbalSumScore ~~ AngerSumScore
  HostilitySumScore ~~ AngerSumScore
'

unconditionalFitBPAQ <- sem(
  model=unconditionalModelBPAQ,
  estimator="MLR",
  meanstructure=TRUE,
  data = replicationData
)

unconditionalTableBPAQ <- parameterEstimates(unconditionalFitBPAQ) %>%
  mutate(
    Scale = "BPAQ"
  )

unconditionalTableBPAQ %>%
  filter(
    op %in% c("~", ":=", "gof") & !(rhs %in% c("Age", "N"))
    | lhs %in% lavNames(unconditionalFitBPAQ, "ov.y") & op == "~1"
  ) %>%
  dplyr::select(lhs, rhs, est, se, z, pvalue) %>%
  mutate(
    across(c(est, se, z, pvalue), \(x) round(x, digits = 4))
  ) %>%
  arrange(lhs, rhs)

unconditionalModelSD3 <- '
  MachiavellianismSumScore ~ m0*1 + m1*Male
  PsychopathySumScore      ~ p0*1 + p1*Male
  NarcissismSumScore       ~ n0*1 + n1*Male
  
  MachiavellianismMale  := m0 + m1
  PsychopathyMale       := p0 + p1
  NarcissismMale        := n0 + n1

  MachiavellianismSumScore ~~ PsychopathySumScore
  MachiavellianismSumScore ~~ NarcissismSumScore
  PsychopathySumScore ~~ NarcissismSumScore
'

unconditionalFitSD3 <- sem(
  model=unconditionalModelSD3,
  estimator="MLR",
  meanstructure=TRUE,
  data = replicationData
)

unconditionalTableSD3 <- parameterEstimates(unconditionalFitSD3) %>%
  mutate(
    Scale = "SD3"
  )

unconditionalTableSD3 %>%
  filter(
    op %in% c("~", ":=", "gof") & !(rhs %in% c("Age", "N"))
    | lhs %in% lavNames(unconditionalFitSD3, "ov.y") & op == "~1"
  ) %>%
  dplyr::select(lhs, rhs, est, se, z, pvalue) %>%
  mutate(
    across(c(est, se, z, pvalue), \(x) round(x, digits = 4))
  ) %>%
  arrange(lhs, rhs)

naiveUnconditionalMeans <- dplyr::bind_rows(unconditionalTableBPAQ, unconditionalTableSD3) %>%
  filter(
    op == ":="
    | lhs %in% c(lavNames(unconditionalTableBPAQ, "ov.y"), lavNames(unconditionalFitSD3, "ov.y"))  & op == "~1"
  ) %>%
  mutate(
    Sex = case_when(
      op == "~1" ~ "Female",
      op == ":=" ~ "Male",
    ),
    Variable = sub("Male", "", sub("SumScore", "", lhs)),
    Mean = est,
    Lower = ci.lower,
    Upper = ci.upper,
    Model = "Naive",
    Scale = Scale,
    .keep = "none"
  )

naiveUnconditionalTests <- dplyr::bind_rows(unconditionalTableBPAQ, unconditionalTableSD3) %>%
  filter(
    op == "~"
  ) %>%
  mutate(
    Variable = sub("Male", "", sub("SumScore", "", lhs)),
    Difference = est,
    SE = se,
    Z = z,
    P = pvalue,
    Stars = case_when(
      pvalue < .001 ~ "***",
      pvalue < .01  ~ "**",
      pvalue < .05  ~ "*",
      .default = ""
    ),
    Model = "Naive",
    Scale = Scale,
    .keep = "none"
  ) %>%
  dplyr::select(
    Variable, Difference, SE, Z, P, Stars, Model, Scale
  )

naiveUnconditionalTests %>%  
  mutate(
    across(c(Difference, SE, Z, P), \(x) round(x, digits = 3))
  )
```

#### Invariant model-based differences

```{r}

set.seed(masterSeed)

Z95 <- qnorm(0.975, lower.tail = TRUE)

unconditionalModelBPAQ <- '
  Physical  ~ p0*1 + p1*Male
  Verbal    ~ v0*1 + v1*Male
  Hostility ~ h0*1 + h1*Male
  Anger     ~ a0*1 + a1*Male
  
  PhysicalMale  := p0 + p1
  VerbalMale    := v0 + v1
  HostilityMale := h0 + h1
  AngerMale     := a0 + a1

  Physical ~~ Verbal
  Physical ~~ Hostility
  Physical ~~ Anger
  Verbal ~~ Hostility
  Verbal ~~ Anger
  Hostility ~~ Anger
'

if (parallelSupported) {
  structuralFit <- pbmcapply::pbmclapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = unconditionalModelBPAQ, 
    measurementFit = congenialPartialFit,
    VWLE=FALSE,
    g=NULL,
    s=NULL,
    covariatesVWLE = NULL,
    data = replicationData,
    masterSeed = masterSeed,
    mc.cores = availableCores,
    mc.set.seed = TRUE
  )
} else {
  structuralFit <- lapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = unconditionalModelBPAQ, 
    measurementFit = congenialPartialFit,
    VWLE=FALSE,
    g=NULL,
    s=NULL,
    covariatesVWLE = NULL,
    data = replicationData,
    masterSeed = masterSeed
  )
}

unconditionalFitBPAQ <- processFunPV(structuralFit) %>%
  mutate(
    Scale = "BPAQ"
  )

unconditionalFitBPAQ %>%
  filter(
    op %in% c("~", ":=", "gof") & !(rhs %in% c("Age", "N"))
    | lhs %in% lavNames(congenialPartialFit, "lv") & op == "~1"
  ) %>%
  dplyr::select(lhs, rhs, Eta2, Estimate, SE, Z, P) %>%
  mutate(
    across(c(Eta2, Estimate, SE, Z, P), \(x) round(x, digits = 4))
  ) %>%
  arrange(lhs, rhs)

unconditionalModelSD3 <- '
  Machiavellianism ~ m0*1 + m1*Male
  Psychopathy      ~ p0*1 + p1*Male
  Narcissism       ~ n0*1 + n1*Male
  
  MachiavellianismMale  := m0 + m1
  PsychopathyMale       := p0 + p1
  NarcissismMale        := n0 + n1

  Machiavellianism ~~ Psychopathy
  Machiavellianism ~~ Narcissism
  Psychopathy ~~ Narcissism
'

if (parallelSupported) {
  structuralFit <- pbmcapply::pbmclapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = unconditionalModelSD3, 
    measurementFit = congenialFirstOrderFit,
    VWLE=FALSE,
    g=NULL,
    s=NULL,
    covariatesVWLE = NULL,
    data = replicationData,
    masterSeed = masterSeed,
    mc.cores = availableCores,
    mc.set.seed = TRUE
  )
} else {
  structuralFit <- lapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = unconditionalModelSD3, 
    measurementFit = congenialFirstOrderFit,
    VWLE=FALSE,
    g=NULL,
    s=NULL,
    covariatesVWLE = NULL,
    data = replicationData,
    masterSeed = masterSeed
  )
}

unconditionalFitSD3 <- processFunPV(structuralFit) %>%
  mutate(
    Scale = "SD3"
  )

unconditionalFitSD3 %>%
  filter(
    op %in% c("~", ":=", "gof") & !(rhs %in% c("Age", "N"))
    | lhs %in% lavNames(congenialPartialFit, "lv") & op == "~1"
  ) %>%
  dplyr::select(lhs, rhs, Eta2, Estimate, SE, Z, P) %>%
  mutate(
    across(c(Eta2, Estimate, SE, Z, P), \(x) round(x, digits = 4))
  ) %>%
  arrange(lhs, rhs)



invariantUnconditionalMeans <- dplyr::bind_rows(unconditionalFitBPAQ, unconditionalFitSD3) %>%
  filter(
    op == ":="
    | lhs %in% lavNames(congenialFirstOrderFit, "lv")  & op == "~1"
  ) %>%
  mutate(
    Sex = case_when(
      op == "~1" ~ "Female",
      op == ":=" ~ "Male",
    ),
    Variable = sub("Male", "", lhs),
    Mean = Estimate,
    Lower = Estimate - Z95 * SE, 
    Upper = Estimate + Z95 * SE,
    Model = "Invariant",
    Scale = Scale,
    .keep = "none"
  )

invariantUnconditionalTests <- dplyr::bind_rows(unconditionalFitBPAQ, unconditionalFitSD3) %>%
  filter(
    op == "~"
  ) %>%
  mutate(
    Variable = sub("Male", "", lhs),
    Eta2 = Eta2,
    Difference = Estimate,
    SE = SE,
    Z = Z,
    P = P,
    Stars = case_when(
      P < .001 ~ "***",
      P < .01  ~ "**",
      P < .05  ~ "*",
      .default = ""
    ),
    Model = "Invariant",
    Scale = Scale,
    .keep = "none"
  ) %>%
  dplyr::select(
    Variable, Eta2, Difference, SE, Z, P, Stars, Model, Scale
  )

invariantUnconditionalTests %>%
  mutate(
    across(c(Eta2, Difference, SE, Z, P), \(x) round(x, digits = 3))
  )
```

#### Plot

```{r}

variableOrder <- c(
  "Physical",
  "Verbal",
  "Hostility",
  "Anger",
  "Machiavellianism",
  "Psychopathy",
  "Narcissism"
)

# 1. Manually compute the X-axis coordinates to force perfect clustering
plotDf <- dplyr::bind_rows(naiveUnconditionalMeans, invariantUnconditionalMeans) %>%
  mutate(
    Variable = factor(Variable, levels = variableOrder),
    Model = factor(Model, levels = c("Naive", "Invariant")),
    Sex = factor(Sex, levels = c("Female", "Male")),
    
    # Base integer position for the variable (1, 2, 3...)
    x_base = as.numeric(Variable),
    # Offset the Model: Naive shifts left, Invariant shifts right
    x_model = ifelse(Model == "Naive", -0.15, 0.15),
    # Offset the Sex within the Model cluster
    x_sex = ifelse(Sex == "Female", -0.05, 0.05),
    # Final coordinate
    x_pos = x_base + x_model + x_sex
  )

# 2. Compute coordinates for the significance markers so they align over their respective models
testsDf <- dplyr::bind_rows(naiveUnconditionalTests, invariantUnconditionalTests) %>%
  mutate(
    Variable = factor(Variable, levels = variableOrder),
    Model = factor(Model, levels = c("Naive", "Invariant")),
    x_base = as.numeric(Variable),
    x_model = ifelse(Model == "Naive", -0.15, 0.15),
    x_pos = x_base + x_model
  )

descriptivePlot <- ggplot(plotDf, aes(x=x_pos, y=Mean, color=Model, shape=Sex)) +
  geom_linerange(
    aes(ymin = Lower, ymax = Upper),
    linewidth = 0.5,
    color = "grey65",
    show.legend = FALSE
  ) +
  geom_point(
    size = 2.5,
    show.legend = FALSE
  ) +
  geom_text(
    data = testsDf,
    aes(x = x_pos, y = max(plotDf$Upper, na.rm = TRUE) + 0.1, label = Stars),
    inherit.aes = FALSE,
    size = 3,
    fontface = "bold"
  ) +
  scale_color_manual(
    values  = c("Naive" = "lightcoral" , "Invariant" = "steelblue"),
  ) +
  scale_shape_manual(
    values  = c("Female" = 17, "Male" = 16),
  ) +
  # Map the numeric X-axis back to the variable names
  scale_x_continuous(
    breaks = 1:length(variableOrder),
    labels = variableOrder
  ) +
  facet_wrap(~Scale, scales = "free", ncol = 1) +
  labs(x=NULL, y="Standardized score") +
  theme_minimal(
    base_family = "serif",
    base_size = 10
  ) +
  guides(shape = "none") +
  theme(
    panel.spacing = unit(1.5, "lines"),
    strip.text = element_blank(),
    axis.text.x = element_text(
      angle = 0,
      hjust = 0.5,
      size = 9,
      face = "bold"
    ),
    axis.title.y = element_text(
      size = 9,
      face = "bold"
    ),
    legend.position = "top",
    legend.title = element_blank(),
    legend.text = element_text(size = 9),
    panel.grid.minor = element_blank()
  )

descriptivePlot

if(export){
  ggsave(
    "../Plots/descriptivePlot.pdf",
    plot = descriptivePlot,
    device = "pdf",
    width = 5.5,
    height = 3.6,
    units = "in",
    useDingbats = FALSE
  )
  
  ggsave(
    "../Plots/descriptivePlot.png",
    plot = descriptivePlot,
    width = 5.5,
    height = 3.6,
    units = "in",
    dpi = 600,
    bg = "white"
  ) 
}
```

### Model 1 (Base)

```{r}

baselineModel <- '
  Physical ~ Male + Reference + Psychopathy + Age
  Verbal ~ Male + Reference + Psychopathy + Age
  Hostility ~ Male + Reference + Narcissism + Age
  Anger ~ Male + Reference + Age
  
  Physical ~~ Verbal
  Physical ~~ Hostility
  Physical ~~ Anger
  Verbal ~~ Hostility
  Verbal ~~ Anger
  Hostility ~~ Anger
'

if (parallelSupported) {
  structuralFit <- pbmcapply::pbmclapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = baselineModel, 
    measurementFit = congenialPartialFit,
    VWLE=TRUE,
    g=c("Reference"),
    s=list(c("Psychopathy", "Narcissism")),
    covariatesVWLE = c("Male", "Age"),
    data = replicationData,
    masterSeed = masterSeed,
    mc.cores = availableCores,
    mc.set.seed = TRUE
  )
} else {
  structuralFit <- lapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = baselineModel, 
    measurementFit = congenialPartialFit,
    VWLE=TRUE,
    g=c("Reference"),
    s=list(c("Psychopathy", "Narcissism")),
    covariatesVWLE = c("Male", "Age"),
    data = replicationData,
    masterSeed = masterSeed
  )
}

baselineFit <- processFunPV(structuralFit)

baselineFit %>%
  filter(op %in% c("~", "gof") & !(rhs %in% c("N"))) %>%
  dplyr::select(lhs, rhs, Eta2, Estimate, SE, Z, P) %>%
  mutate(
    across(c(Eta2, Estimate, SE, Z, P), \(x) round(x, digits = 3))
  )
```

#### Bootstrap

```{r}

bootPath <- "../Data/baselineBoot.rds"

targetReached <- FALSE
restartLocal <- restartBootstraps

while (runBootstraps && !targetReached) {
  
  if(!restartLocal) {
    storedResults <- readRDS(bootPath)
    lastAttempt <- attr(storedResults, "lastAttempt")
    setStart <- lastAttempt + 1L
    remainingDraws <- B - n_distinct(storedResults$draw)
    setEnd <- setStart + remainingDraws - 1L
  } else {
    setStart <- 1
    setEnd <- B
  }
  
  targetReached <- setStart > setEnd
  
  if (!targetReached) {
    
    if (parallelSupported && setStart < setEnd) {
      structuralFit <- pbmcapply::pbmclapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = baselineModel, 
        measurementModel = list(responseMeasurement, bifactorMeasurement),
        fullMeasurement = congenialPartialFit,
        VWLE=TRUE,
        g=c("Reference"),
        s=list(c("Psychopathy", "Narcissism")),
        covariatesVWLE = c("Male", "Age"),
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed,
        mc.cores = availableCores,
        mc.set.seed = TRUE
      )
    } else {
      structuralFit <- lapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = baselineModel, 
        measurementModel = list(responseMeasurement, bifactorMeasurement),
        fullMeasurement = congenialPartialFit,
        VWLE=TRUE,
        g=c("Reference"),
        s=list(c("Psychopathy", "Narcissism")),
        covariatesVWLE = c("Male", "Age"),
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed
      )
    }
    
    if(!restartLocal) {
      structuralFit <- dplyr::bind_rows(storedResults, structuralFit)
      rm(storedResults)
    } else {
      structuralFit <- dplyr::bind_rows(structuralFit)
    }
    
    attr(structuralFit, "lastAttempt") <- setEnd
    
    saveRDS(structuralFit, bootPath)
    
    restartLocal <- FALSE
    
    rm(structuralFit)
  }
}
```

```{r}

baselineBoot <- processFunBoot(baselineFit, readRDS("../Data/baselineBoot.rds"))

baselineBoot %>%
  filter(op %in% c("~", "gof") & rhs != "N") %>%
  dplyr::select(lhs, rhs, Eta2, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootSuccess, bootRate) %>%
  mutate(
    across(c(Eta2, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootRate), \(x) round(x, digits = 3))
  )
```

### Model 2 (Moderated)

```{r}

moderatedModel <- '
  Physical ~ Male + Reference + Psychopathy + Reference:Male + Psychopathy:Male + Age
  Verbal ~ Male + Reference + Psychopathy + Reference:Male + Psychopathy:Male + Age
  Hostility ~ Male + Reference + Reference:Male + Narcissism + Age
  Anger ~ Male + Reference + Age
  
  Physical ~~ Verbal
  Physical ~~ Hostility
  Physical ~~ Anger
  Verbal ~~ Hostility
  Verbal ~~ Anger
  Hostility ~~ Anger
'

if (parallelSupported) {
  structuralFit <- pbmcapply::pbmclapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = moderatedModel, 
    measurementFit = congenialPartialFit,
    VWLE=TRUE,
    g=c("Reference", "Reference:Male"),
    s=list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male")),
    covariatesVWLE = c("Male", "Age"),
    data = replicationData,
    masterSeed = masterSeed,
    mc.cores = availableCores,
    mc.set.seed = TRUE
  )
} else {
  structuralFit <- lapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = moderatedModel, 
    measurementFit = congenialPartialFit,
    VWLE=TRUE,
    g=c("Reference", "Reference:Male"),
    s=list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male")),
    covariatesVWLE = c("Male", "Age"),
    data = replicationData,
    masterSeed = masterSeed
  )
}

moderatedFit <- processFunPV(structuralFit)

moderatedFit %>%
  filter(op %in% c("~", "gof") & !(rhs %in% c("N"))) %>%
  dplyr::select(lhs, rhs, Estimate, SE, Z, P) %>%
  mutate(
    across(c(Estimate, SE, Z, P), \(x) round(x, digits = 4))
  )
```

#### Bootstrap

```{r}

bootPath <- "../Data/moderatedBoot.rds"

targetReached <- FALSE
restartLocal <- restartBootstraps

while (runBootstraps && !targetReached) {
  
  if(!restartLocal) {
    storedResults <- readRDS(bootPath)
    lastAttempt <- attr(storedResults, "lastAttempt")
    setStart <- lastAttempt + 1L
    remainingDraws <- B - n_distinct(storedResults$draw)
    setEnd <- setStart + remainingDraws - 1L
  } else {
    setStart <- 1
    setEnd <- B
  }
  
  targetReached <- setStart > setEnd
  
  if (!targetReached) {
    
    if (parallelSupported && setStart < setEnd) {
      structuralFit <- pbmcapply::pbmclapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = moderatedModel, 
        measurementModel = list(responseMeasurement, bifactorMeasurement),
        fullMeasurement = congenialPartialFit,
        VWLE=TRUE,
        g=c("Reference", "Reference:Male"),
        s=list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male")),
        covariatesVWLE = c("Male", "Age"),
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed,
        mc.cores = availableCores,
        mc.set.seed = TRUE
      )
    } else {
      structuralFit <- lapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = moderatedModel, 
        measurementModel = list(responseMeasurement, bifactorMeasurement),
        fullMeasurement = congenialPartialFit,
        VWLE=TRUE,
        g=c("Reference", "Reference:Male"),
        s=list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male")),
        covariatesVWLE = c("Male", "Age"),
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed
      )
    }
    
    if(!restartLocal) {
      structuralFit <- dplyr::bind_rows(storedResults, structuralFit)
      rm(storedResults)
    } else {
      structuralFit <- dplyr::bind_rows(structuralFit)
    }
    
    attr(structuralFit, "lastAttempt") <- setEnd
    
    saveRDS(structuralFit, bootPath)
    
    restartLocal <- FALSE
    
    rm(structuralFit)
  }
}
```

```{r}

moderatedBoot <- processFunBoot(moderatedFit, readRDS("../Data/moderatedBoot.rds"))

moderatedBoot %>%
  filter(op %in% c("~", "gof") & rhs != "N") %>%
  dplyr::select(lhs, rhs, Eta2, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootSuccess, bootRate) %>%
  mutate(
    across(c(Eta2, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootRate), \(x) round(x, digits = 3))
  )
```

### Confirmatory table

#### HTML

```{r}

outcomeLevels <- c(
  "Physical",
  "Verbal",
  "Hostility",
  "Anger"
)

outcomeLabels <- c(
  "Physical (Z)",
  "Verbal (Z)",
  "Hostility (Z)",
  "Anger (Z)"
)

termLevels <- c(
  "Male",
  "Reference",
  "Reference:Male",
  "Psychopathy",
  "Psychopathy:Male",
  "Narcissism",
  "Age",
  "",
  "R2",
  "N"
)

termLabels <- c(
  "Male",
  "Reference (Z)",
  "Reference × Male",
  "Psychopathy (Z)",
  "Psychopathy × Male",
  "Narcissism (Z)",
  "Age",
  "Intercept",
  "R²",
  "N"
)

modelLevels <- c("baseline", "moderated")
modelLabels <- c("C1", "C2")

baselineBoot$model <- "baseline"
moderatedBoot$model <- "moderated"

confirmatoryTable <- dplyr::bind_rows(baselineBoot, moderatedBoot) %>%
  filter(op %in% c("~", "gof") | (lhs %in% outcomeLevels & op == "~1")) %>%
  mutate(
    stars = case_when(
      P <= 0.001 ~ "***",
      P <= 0.01  ~ "**",
      P <= 0.05  ~ "*",
      .default = ""
    ),
    pFormatted = if_else(
      P < 0.001,
      "&lt;.001",
      paste0("=", sub("^0", "", sprintf("%.3f", P)))
    ),
    Estimate = case_when(
      endsWith(rhs, "VWLE") ~ sprintf(
        "%.3f%s<br>(%.3f)",
        Estimate, stars, SE
      ),
      op %in% c("~", "~1") ~ sprintf(
        "%.3f%s<br>(%.3f)<br>p%s",
        Estimate, stars, SE, pFormatted
      ),
      rhs == "N" ~ sprintf("%.0f", Estimate),
      .default = sprintf("%.3f", Estimate)
    ),
    Outcome = factor(
      lhs,
      levels = outcomeLevels,
      labels = outcomeLabels
    ),
    Model = factor(
      model,
      levels = modelLevels,
      labels = modelLabels
    ),
    Panel = factor(
      case_when(
        op %in% c("~", "~1") & !endsWith(rhs, "VWLE") ~ "Structural",
        op %in% c("~", "~1") & endsWith(rhs, "VWLE") ~ "VWLE",
        op == "gof" ~ "Model information",
        .default = ""
      ),
      levels = c("Structural", "VWLE", "Model information")
    ),
    Term = factor(
      sub("VWLE$", "", rhs), 
      levels = termLevels,
      labels = termLabels
    )
  ) %>%
  dplyr::select(
    Outcome,
    Term,
    Model,
    Estimate,
    Panel
  )

confirmatoryTableFull <- confirmatoryTable %>%
  tidyr::pivot_wider(
    id_cols = c(Panel, Term),
    names_from = c(Outcome, Model),
    values_from = Estimate,
    names_sep = "_",
    names_expand = TRUE
  ) %>%
  arrange(Panel, Term)

confirmatoryTableLean <- confirmatoryTable %>%
  filter(Outcome != "Anger (Z)") %>%
  droplevels() %>%
  tidyr::pivot_wider(
    id_cols = c(Panel, Term),
    names_from = c(Outcome, Model),
    values_from = Estimate,
    names_sep = "_",
    names_expand = TRUE
  ) %>%
  filter(!(Term %in% c("Age", "Intercept"))) %>%
  arrange(Panel, Term)

confirmatoryGT <- confirmatoryTableLean %>%
  gt::gt(
    rowname_col = "Term",
    groupname_col = "Panel"
  ) %>%
  gt::tab_spanner(
    label = "Physical (Z)",
    columns = starts_with("Physical")
  ) %>%
  gt::tab_spanner(
    label = "Verbal (Z)",
    columns = starts_with("Verbal")
  ) %>%
  gt::tab_spanner(
    label = "Hostility (Z)",
    columns = starts_with("Hostility")
  ) %>%
  gt::cols_label(
    ends_with("C1") ~ "C1",
    ends_with("C2") ~ "C2"
  ) %>%
  gt::fmt_markdown(
    columns = -Term
  ) %>%
  gt::cols_align(
    align = "center",
    columns = -Term
  ) %>%
  gt::sub_missing(
    columns = -Term,
    missing_text = "—"
  ) %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(
      groups = everything()
    )
  ) %>%
  gt::tab_options(
    table.font.names = c("Verdana", "Arial", "sans-serif"),
    table.font.size = gt::px(11),
    column_labels.font.weight = "bold",
    column_labels.border.top.width = gt::px(0),
    column_labels.border.bottom.width = gt::px(1),
    table_body.hlines.width = gt::px(0)
  )

confirmatoryGT

if(export) {
  confirmatoryGT_png <- confirmatoryGT %>%
    gt::tab_options(
      table.width = gt::px(624)
    )
  
  gt::gtsave(
    confirmatoryGT_png,
    filename = "../Tables/confirmatoryTable.png",
    zoom = 3.125,
    expand = 0
  ) 
}
```

#### LaTeX

```{r}

if(export) {
  
  # Convert one HTML-formatted result cell to LaTeX
  toLatexCell <- function(x) {
    if (is.na(x)) {
      return("\\textemdash{}")
    }
    
    x <- gsub("&lt;", "$<$", x, fixed = TRUE)
    
    # Replace each complete star sequence exactly once
    x <- gsub(
      "(\\*{1,3})",
      "{\\\\tiny \\1}",
      x,
      perl = TRUE
    )
    
    lines <- strsplit(x, "<br>", fixed = TRUE)[[1]]
    
    paste0(
      "\\makecell{",
      paste(lines, collapse = " \\\\ "),
      "}"
    )
  }
  
  # ------------------------------------ LEAN TABLE ---------------------------------------
  
  confirmatoryTableLatex <- confirmatoryTableLean %>%
    mutate(
      Panel = as.character(Panel),
      Term = as.character(Term),
      Term = recode(
        Term,
        "Reference × Male" = "Reference $\\times$ Male",
        "Psychopathy × Male" = "Psychopathy $\\times$ Male",
        "Narcissism × Male" = "Narcissism $\\times$ Male",
        "R²" = "$\\text{R}^2$"
      )
    ) %>%
    mutate(
      across(
        -c(Panel, Term),
        \(x) vapply(x, toLatexCell, character(1))
      )
    )
  
  
  # Determine panel positions automatically
  panelRuns <- rle(confirmatoryTableLatex$Panel)
  
  panelIndex <- stats::setNames(
    panelRuns$lengths,
    panelRuns$values
  )
  
  panelSizes <- table(confirmatoryTableLatex$Panel)
  
  nPredictors <- unname(panelSizes["Structural"])
  nVWLE <- unname(panelSizes["VWLE"])
  nModelInfo <- unname(panelSizes["Model information"])
  
  confirmatoryKable <- confirmatoryTableLatex %>%
    dplyr::select(-Panel) %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", rep("c", 6)),
      col.names = c("Structural", rep(c("C1", "C2"), 3))
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(confirmatoryTableLatex) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::add_header_above(
      c(
        " " = 1,
        "Physical (Z)" = 2,
        "Verbal (Z)" = 2,
        "Hostility (Z)" = 2
      ),
      escape = FALSE,
      bold = TRUE
    ) %>%
    kableExtra::pack_rows(
      "VWLE",
      start_row = nPredictors + 1,
      end_row = nPredictors + nVWLE,
      bold = TRUE,
      hline_after = FALSE,
      extra_latex_after = "\\midrule ",
      indent = FALSE,
      escape = FALSE,
      latex_align = "@{}l@{}"
    ) %>%
    kableExtra::pack_rows(
      "Model information",
      start_row = nPredictors + nVWLE + 1,
      end_row = nPredictors + nVWLE + nModelInfo,
      bold = TRUE,
      hline_after = FALSE,
      extra_latex_after = "\\midrule ",
      indent = FALSE,
      escape = FALSE,
      latex_align = "@{}l@{}"
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(confirmatoryKable),
    "../Tables/confirmatoryTable.tex"
  )
  
  # ------------------------------------ FULL TABLE ---------------------------------------
  
  confirmatoryFullLatex <- confirmatoryTableFull %>%
    mutate(
      Panel = as.character(Panel),
      Term = as.character(Term),
      Term = recode(
        Term,
        "Reference × Male" = "Reference $\\times$ Male",
        "Psychopathy × Male" = "Psychopathy $\\times$ Male",
        "Narcissism × Male" = "Narcissism $\\times$ Male",
        "R²" = "$\\text{R}^2$"
      )
    ) %>%
    mutate(
      across(
        -c(Panel, Term),
        \(x) vapply(x, toLatexCell, character(1))
      )
    )
  
  
  # Determine panel positions automatically
  panelRuns <- rle(confirmatoryFullLatex$Panel)
  
  panelIndex <- stats::setNames(
    panelRuns$lengths,
    panelRuns$values
  )
  
  panelSizes <- table(confirmatoryFullLatex$Panel)
  
  nPredictors <- unname(panelSizes["Structural"])
  nVWLE <- unname(panelSizes["VWLE"])
  nModelInfo <- unname(panelSizes["Model information"])
  
  confirmatoryFullKable <- confirmatoryFullLatex %>%
    dplyr::select(-Panel) %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", rep("c", 8)),
      col.names = c("Structural", rep(c("C1", "C2"), 4))
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(confirmatoryFullLatex) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::add_header_above(
      c(
        " " = 1,
        "Physical (Z)" = 2,
        "Verbal (Z)" = 2,
        "Hostility (Z)" = 2,
        "Anger (Z)" = 2
      ),
      escape = FALSE,
      bold = TRUE
    ) %>%
    kableExtra::pack_rows(
      "VWLE",
      start_row = nPredictors + 1,
      end_row = nPredictors + nVWLE,
      bold = TRUE,
      hline_after = FALSE,
      extra_latex_after = "\\midrule ",
      indent = FALSE,
      escape = FALSE,
      latex_align = "@{}l@{}"
    ) %>%
    kableExtra::pack_rows(
      "Model information",
      start_row = nPredictors + nVWLE + 1,
      end_row = nPredictors + nVWLE + nModelInfo,
      bold = TRUE,
      hline_after = FALSE,
      extra_latex_after = "\\midrule ",
      indent = FALSE,
      escape = FALSE,
      latex_align = "@{}l@{}"
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(confirmatoryFullKable),
    "../Tables/confirmatoryTableFull.tex"
  )
}
```

## Exploratory models

### Saturated model

```{r}

saturatedModel <- '
  Physical ~ Male + Reference + Psychopathy + Narcissism + Reference:Male + Psychopathy:Male + Narcissism:Male
  Verbal ~ Male + Reference + Psychopathy + Narcissism + Reference:Male + Psychopathy:Male + Narcissism:Male
  Hostility ~ Male + Reference + Psychopathy + Narcissism + Reference:Male + Psychopathy:Male + Narcissism:Male
  Anger ~ Male + Reference + Psychopathy + Narcissism + Reference:Male + Psychopathy:Male + Narcissism:Male
  
  Physical ~~ Verbal
  Physical ~~ Hostility
  Physical ~~ Anger
  Verbal ~~ Hostility
  Verbal ~~ Anger
  Hostility ~~ Anger
'

if (parallelSupported) {
  structuralFit <- pbmcapply::pbmclapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = saturatedModel, 
    measurementFit = congenialPartialFit,
    VWLE=TRUE,
    g=c("Reference", "Reference:Male"),
    s=list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male", "Narcissism:Male")),
    covariatesVWLE = c("Male"),
    data = replicationData,
    masterSeed = masterSeed,
    mc.cores = availableCores,
    mc.set.seed = TRUE
  )
} else {
  structuralFit <- lapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = saturatedModel, 
    measurementFit = congenialPartialFit,
    VWLE=TRUE,
    g=c("Reference", "Reference:Male"),
    s=list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male", "Narcissism:Male")),
    covariatesVWLE = c("Male"),
    data = replicationData,
    masterSeed = masterSeed
  )
}

saturatedFit <- processFunPV(structuralFit)

saturatedFit %>%
  filter(op %in% c("~", "gof") & !(rhs %in% c("N"))) %>%
  dplyr::select(lhs, rhs, Eta2, Estimate, SE, Z, P) %>%
  mutate(
    across(c(Eta2, Estimate, SE, Z, P), \(x) round(x, digits = 4))
  )
```

#### Bootstrap

```{r}

bootPath <- "../Data/saturatedBoot.rds"

targetReached <- FALSE
restartLocal <- restartBootstraps

while (runBootstraps && !targetReached) {
  
  if(!restartLocal) {
    storedResults <- readRDS(bootPath)
    lastAttempt <- attr(storedResults, "lastAttempt")
    setStart <- lastAttempt + 1L
    remainingDraws <- B - n_distinct(storedResults$draw)
    setEnd <- setStart + remainingDraws - 1L
  } else {
    setStart <- 1
    setEnd <- B
  }
  
  targetReached <- setStart > setEnd
  
  if (!targetReached) {
    
    if (parallelSupported && setStart < setEnd) {
      structuralFit <- pbmcapply::pbmclapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = saturatedModel, 
        measurementModel = list(responseMeasurement, bifactorMeasurement),
        fullMeasurement = congenialPartialFit,
        VWLE=TRUE,
        g=c("Reference", "Reference:Male"),
        s=list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male", "Narcissism:Male")),
        covariatesVWLE = c("Male"),
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed,
        mc.cores = availableCores,
        mc.set.seed = TRUE
      )
    } else {
      structuralFit <- lapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = saturatedModel, 
        measurementModel = list(responseMeasurement, bifactorMeasurement),
        fullMeasurement = congenialPartialFit,
        VWLE=TRUE,
        g=c("Reference", "Reference:Male"),
        s=list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male", "Narcissism:Male")),
        covariatesVWLE = c("Male"),
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed
      )
    }
    
    if(!restartLocal) {
      structuralFit <- dplyr::bind_rows(storedResults, structuralFit)
      rm(storedResults)
    } else {
      structuralFit <- dplyr::bind_rows(structuralFit)
    }
    
    attr(structuralFit, "lastAttempt") <- setEnd
    
    saveRDS(structuralFit, bootPath)
    
    restartLocal <- FALSE
    
    rm(structuralFit)
  }
}
```

```{r}

saturatedBoot <- processFunBoot(saturatedFit, readRDS("../Data/saturatedBoot.rds"))

saturatedBoot %>%
  filter(op %in% c("~", "gof") & rhs != "N") %>%
  dplyr::select(lhs, rhs, Eta2, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootSuccess, bootRate) %>%
  mutate(
    across(c(Eta2, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootRate), \(x) round(x, digits = 3))
  )
```

### Parsimonious model

```{r}

parsimoniousModel <- '
  Physical ~ Male + Reference + Psychopathy + Narcissism
  Verbal ~ Male + Reference + Psychopathy + Narcissism
  Hostility ~ Male + Reference + Psychopathy + Narcissism
  Anger ~ Male + Reference + Psychopathy + Narcissism
  
  Physical ~~ Verbal
  Physical ~~ Hostility
  Physical ~~ Anger
  Verbal ~~ Hostility
  Verbal ~~ Anger
  Hostility ~~ Anger
'

if (parallelSupported) {
  structuralFit <- pbmcapply::pbmclapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = parsimoniousModel, 
    measurementFit = congenialPartialFit,
    VWLE=TRUE,
    g=c("Reference"),
    s=list(c("Psychopathy", "Narcissism")),
    covariatesVWLE = c("Male"),
    data = replicationData,
    masterSeed = masterSeed,
    mc.cores = availableCores,
    mc.set.seed = TRUE
  )
} else {
  structuralFit <- lapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = parsimoniousModel, 
    measurementFit = congenialPartialFit,
    VWLE=TRUE,
    g=c("Reference"),
    s=list(c("Psychopathy", "Narcissism")),
    covariatesVWLE = c("Male"),
    data = replicationData,
    masterSeed = masterSeed
  )
}

parsimoniousFit <- processFunPV(structuralFit)

parsimoniousFit %>%
  filter(op %in% c("~", "gof") & !(rhs %in% c("N"))) %>%
  dplyr::select(lhs, rhs, Eta2, Estimate, SE, Z, P) %>%
  mutate(
    across(c(Eta2, Estimate, SE, Z, P), \(x) round(x, digits = 4))
  )
```

#### Bootstrap

```{r}

bootPath <- "../Data/parsimoniousBoot.rds"

targetReached <- FALSE
restartLocal <- restartBootstraps

while (runBootstraps && !targetReached) {
  
  if(!restartLocal) {
    storedResults <- readRDS(bootPath)
    lastAttempt <- attr(storedResults, "lastAttempt")
    setStart <- lastAttempt + 1L
    remainingDraws <- B - n_distinct(storedResults$draw)
    setEnd <- setStart + remainingDraws - 1L
  } else {
    setStart <- 1
    setEnd <- B
  }
  
  targetReached <- setStart > setEnd
  
  if (!targetReached) {
    
    if (parallelSupported && setStart < setEnd) {
      structuralFit <- pbmcapply::pbmclapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = parsimoniousModel, 
        measurementModel = list(responseMeasurement, bifactorMeasurement),
        fullMeasurement = congenialPartialFit,
        VWLE=TRUE,
        g=c("Reference"),
        s=list(c("Psychopathy", "Narcissism")),
        covariatesVWLE = c("Male"),
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed,
        mc.cores = availableCores,
        mc.set.seed = TRUE
      )
    } else {
      structuralFit <- lapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = parsimoniousModel, 
        measurementModel = list(responseMeasurement, bifactorMeasurement),
        fullMeasurement = congenialPartialFit,
        VWLE=TRUE,
        g=c("Reference"),
        s=list(c("Psychopathy", "Narcissism")),
        covariatesVWLE = c("Male"),
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed
      )
    }
    
    if(!restartLocal) {
      structuralFit <- dplyr::bind_rows(storedResults, structuralFit)
      rm(storedResults)
    } else {
      structuralFit <- dplyr::bind_rows(structuralFit)
    }
    
    attr(structuralFit, "lastAttempt") <- setEnd
    
    saveRDS(structuralFit, bootPath)
    
    restartLocal <- FALSE
    
    rm(structuralFit)
  }
}
```

```{r}

parsimoniousBoot <- processFunBoot(parsimoniousFit, readRDS("../Data/parsimoniousBoot.rds"))

parsimoniousBoot %>%
  filter(op %in% c("~", "gof") & rhs != "N") %>%
  dplyr::select(lhs, rhs, Eta2, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootSuccess, bootRate) %>%
  mutate(
    across(c(Eta2, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootRate), \(x) round(x, digits = 3))
  )
```

### Exploratory table

#### HTML

```{r}

outcomeLevels <- c(
  "Physical",
  "Verbal",
  "Hostility",
  "Anger"
)

outcomeLabels <- c(
  "Physical (Z)",
  "Verbal (Z)",
  "Hostility (Z)",
  "Anger (Z)"
)

termLevels <- c(
  "Male",
  "Reference",
  "Reference:Male",
  "Psychopathy",
  "Psychopathy:Male",
  "Narcissism",
  "Narcissism:Male",
  "",
  "R2",
  "N"
)

termLabels <- c(
  "Male",
  "Reference (Z)",
  "Reference × Male",
  "Psychopathy (Z)",
  "Psychopathy × Male",
  "Narcissism (Z)",
  "Narcissism × Male",
  "Intercept",
  "R²",
  "N"
)

modelLevels <- c("saturated", "parsimonious")
modelLabels <- c("E1", "E2")

saturatedBoot$model <- "saturated"
parsimoniousBoot$model <- "parsimonious"

exploratoryTable <- dplyr::bind_rows(saturatedBoot, parsimoniousBoot) %>%
  filter(op %in% c("~", "gof") | (lhs %in% outcomeLevels & op == "~1")) %>%
  mutate(
    stars = case_when(
      pBoot <= 0.001 ~ "***",
      pBoot <= 0.01  ~ "**",
      pBoot <= 0.05  ~ "*",
      is.na(pBoot) & P <= 0.001 ~ "***",
      is.na(pBoot) & P <= 0.01  ~ "**",
      is.na(pBoot) & P <= 0.05  ~ "*",
      .default = ""
    ),
    pFormatted = case_when(
      pBoot < 0.001 ~ "&lt;.001",
      pBoot >= 0.001 ~ paste0("=", sub("^0", "", sprintf("%.3f", pBoot))),
      is.na(pBoot) & P < 0.001 ~ "&lt;.001",
      .default = paste0("=", sub("^0", "", sprintf("%.3f", P))),
    ),
    Estimate = case_when(
      endsWith(rhs, "VWLE") ~ sprintf(
        "%.3f%s<br>(%.3f)",
        Estimate, stars, SE
      ),
      op %in% c("~", "~1") ~ sprintf(
        "%.3f%s<br>(%.3f)<br>p%s",
        Estimate, stars, SE, pFormatted
      ),
      rhs == "N" ~ sprintf("%.0f", Estimate),
      .default = sprintf("%.3f", Estimate)
    ),
    Outcome = factor(
      lhs,
      levels = outcomeLevels,
      labels = outcomeLabels
    ),
    Model = factor(
      model,
      levels = modelLevels,
      labels = modelLabels
    ),
    Panel = factor(
      case_when(
        op %in% c("~", "~1") & !endsWith(rhs, "VWLE") ~ "Structural",
        op %in% c("~", "~1") & endsWith(rhs, "VWLE") ~ "VWLE",
        op == "gof" ~ "Model information",
        .default = ""
      ),
      levels = c("Structural", "VWLE", "Model information")
    ),
    Term = factor(
      sub("VWLE$", "", rhs), 
      levels = termLevels,
      labels = termLabels
    )
  ) %>%
  dplyr::select(
    Outcome,
    Term,
    Model,
    Estimate,
    Panel
  )

exploratoryTableFull <- exploratoryTable %>%
  tidyr::pivot_wider(
    id_cols = c(Panel, Term),
    names_from = c(Outcome, Model),
    values_from = Estimate,
    names_sep = "_",
    names_expand = TRUE
  ) %>%
  arrange(Panel, Term)

exploratoryTableLean <- exploratoryTable %>%
  tidyr::pivot_wider(
    id_cols = c(Panel, Term),
    names_from = c(Outcome, Model),
    values_from = Estimate,
    names_sep = "_",
    names_expand = TRUE
  ) %>%
  filter(!(Term %in% c("Age", "Intercept"))) %>%
  arrange(Panel, Term)

exploratoryGT <- exploratoryTableLean %>%
  gt::gt(
    rowname_col = "Term",
    groupname_col = "Panel"
  ) %>%
  gt::tab_spanner(
    label = "Physical (Z)",
    columns = starts_with("Physical")
  ) %>%
  gt::tab_spanner(
    label = "Verbal (Z)",
    columns = starts_with("Verbal")
  ) %>%
  gt::tab_spanner(
    label = "Hostility (Z)",
    columns = starts_with("Hostility")
  ) %>%
  gt::tab_spanner(
    label = "Anger (Z)",
    columns = starts_with("Anger")
  ) %>%
  gt::cols_label(
    ends_with("E1") ~ "E1",
    ends_with("E2") ~ "E2"
  ) %>%
  gt::fmt_markdown(
    columns = -Term
  ) %>%
  gt::cols_align(
    align = "center",
    columns = -Term
  ) %>%
  gt::sub_missing(
    columns = -Term,
    missing_text = "—"
  ) %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(
      groups = everything()
    )
  ) %>%
  gt::tab_options(
    table.font.names = c("Verdana", "Arial", "sans-serif"),
    table.font.size = gt::px(11),
    column_labels.font.weight = "bold",
    column_labels.border.top.width = gt::px(0),
    column_labels.border.bottom.width = gt::px(1),
    table_body.hlines.width = gt::px(0)
  )

exploratoryGT

if(export) {
  exploratoryGT_png <- exploratoryGT %>%
    gt::tab_options(
      table.width = gt::px(624)
    )
  
  gt::gtsave(
    exploratoryGT_png,
    filename = "../Tables/exploratoryTable.png",
    zoom = 3.125,
    expand = 0
  ) 
}
```

#### LaTeX

```{r}

if(export) {
  
  # Convert one HTML-formatted result cell to LaTeX
  toLatexCell <- function(x) {
    if (is.na(x)) {
      return("\\textemdash{}")
    }
    
    x <- gsub("&lt;", "$<$", x, fixed = TRUE)
    
    # Replace each complete star sequence exactly once
    x <- gsub(
      "(\\*{1,3})",
      "{\\\\tiny \\1}",
      x,
      perl = TRUE
    )
    
    lines <- strsplit(x, "<br>", fixed = TRUE)[[1]]
    
    paste0(
      "\\makecell{",
      paste(lines, collapse = " \\\\ "),
      "}"
    )
  }
  
  # ------------------------------------ LEAN TABLE ---------------------------------------
  
  exploratoryTableLatex <- exploratoryTableLean %>%
    mutate(
      Panel = as.character(Panel),
      Term = as.character(Term),
      Term = recode(
        Term,
        "Reference × Male" = "Reference $\\times$ Male",
        "Psychopathy × Male" = "Psychopathy $\\times$ Male",
        "Narcissism × Male" = "Narcissism $\\times$ Male",
        "R²" = "$\\text{R}^2$"
      )
    ) %>%
    mutate(
      across(
        -c(Panel, Term),
        \(x) vapply(x, toLatexCell, character(1))
      )
    )
  
  
  # Determine panel positions automatically
  panelRuns <- rle(exploratoryTableLatex$Panel)
  
  panelIndex <- stats::setNames(
    panelRuns$lengths,
    panelRuns$values
  )
  
  panelSizes <- table(exploratoryTableLatex$Panel)
  
  nPredictors <- unname(panelSizes["Structural"])
  nVWLE <- unname(panelSizes["VWLE"])
  nModelInfo <- unname(panelSizes["Model information"])
  
  exploratoryKable <- exploratoryTableLatex %>%
    dplyr::select(-Panel) %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", rep("c", 8)),
      col.names = c("Structural", rep(c("E1", "E2"), 4))
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(exploratoryTableLatex) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::add_header_above(
      c(
        " " = 1,
        "Physical (Z)" = 2,
        "Verbal (Z)" = 2,
        "Hostility (Z)" = 2,
        "Anger (Z)" = 2
      ),
      escape = FALSE,
      bold = TRUE
    ) %>%
    kableExtra::pack_rows(
      "VWLE",
      start_row = nPredictors + 1,
      end_row = nPredictors + nVWLE,
      bold = TRUE,
      hline_after = FALSE,
      extra_latex_after = "\\midrule ",
      indent = FALSE,
      escape = FALSE,
      latex_align = "@{}l@{}"
    ) %>%
    kableExtra::pack_rows(
      "Model information",
      start_row = nPredictors + nVWLE + 1,
      end_row = nPredictors + nVWLE + nModelInfo,
      bold = TRUE,
      hline_after = FALSE,
      extra_latex_after = "\\midrule ",
      indent = FALSE,
      escape = FALSE,
      latex_align = "@{}l@{}"
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(exploratoryKable),
    "../Tables/exploratoryTable.tex"
  )
  
  # ------------------------------------ FULL TABLE ---------------------------------------
  
  exploratoryFullLatex <- exploratoryTableFull %>%
    mutate(
      Panel = as.character(Panel),
      Term = as.character(Term),
      Term = recode(
        Term,
        "Reference × Male" = "Reference $\\times$ Male",
        "Psychopathy × Male" = "Psychopathy $\\times$ Male",
        "Narcissism × Male" = "Narcissism $\\times$ Male",
        "R²" = "$\\text{R}^2$"
      )
    ) %>%
    mutate(
      across(
        -c(Panel, Term),
        \(x) vapply(x, toLatexCell, character(1))
      )
    )
  
  
  # Determine panel positions automatically
  panelRuns <- rle(exploratoryFullLatex$Panel)
  
  panelIndex <- stats::setNames(
    panelRuns$lengths,
    panelRuns$values
  )
  
  panelSizes <- table(exploratoryFullLatex$Panel)
  
  nPredictors <- unname(panelSizes["Structural"])
  nVWLE <- unname(panelSizes["VWLE"])
  nModelInfo <- unname(panelSizes["Model information"])
  
  exploratoryFullKable <- exploratoryFullLatex %>%
    dplyr::select(-Panel) %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", rep("c", 8)),
      col.names = c("Structural", rep(c("E1", "E2"), 4))
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(exploratoryFullLatex) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::add_header_above(
      c(
        " " = 1,
        "Physical (Z)" = 2,
        "Verbal (Z)" = 2,
        "Hostility (Z)" = 2,
        "Anger (Z)" = 2
      ),
      escape = FALSE,
      bold = TRUE
    ) %>%
    kableExtra::pack_rows(
      "VWLE",
      start_row = nPredictors + 1,
      end_row = nPredictors + nVWLE,
      bold = TRUE,
      hline_after = FALSE,
      extra_latex_after = "\\midrule ",
      indent = FALSE,
      escape = FALSE,
      latex_align = "@{}l@{}"
    ) %>%
    kableExtra::pack_rows(
      "Model information",
      start_row = nPredictors + nVWLE + 1,
      end_row = nPredictors + nVWLE + nModelInfo,
      bold = TRUE,
      hline_after = FALSE,
      extra_latex_after = "\\midrule ",
      indent = FALSE,
      escape = FALSE,
      latex_align = "@{}l@{}"
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(exploratoryFullKable),
    "../Tables/exploratoryTableFull.tex"
  )
  
}
```

### Exploratory plot

#### Trait slopes

```{r}

DTFS <- lavPredict(congenialPartialFit, method = "Regression", transform = FALSE)
caseIdx <- unlist(lavInspect(congenialPartialFit, "case.idx"), use.names = FALSE)
DTFSmat <- do.call(rbind, DTFS)
FSDF <- cbind(
  replicationData[caseIdx, , drop = FALSE],
  DTFSmat
)

pMale <- mean(replicationData$Male)
pFemale <- 1 - pMale

gBase <- c("Reference")

# ------------------------------------ POOLED MOMENTS --------------------------------------

groupCov  <- lavInspect(congenialPartialFit, "cov.lv")
groupMean <- lavInspect(congenialPartialFit, "mean.lv")

meanDifference <- groupMean[[1]] - groupMean[[2]]

pooledCov <-
  pFemale * groupCov[[1]] +
  pMale   * groupCov[[2]] +
  pFemale * pMale * tcrossprod(meanDifference)

pooledMean <-
  pFemale * groupMean[[1]] +
  pMale   * groupMean[[2]]

# --------------------------------- REDUCED FORM COVARIANCE --------------------------------

phi_g <- pooledCov[rownames(pooledCov) %in% gBase, colnames(pooledCov) %in% gBase, drop=FALSE]

phi_s <- pooledCov[!(rownames(pooledCov) %in% gBase), !(colnames(pooledCov) %in% gBase), drop=FALSE]

phi_gs <- pooledCov[rownames(pooledCov) %in% gBase, !(colnames(pooledCov) %in% gBase), drop=FALSE]

# ---------------------------------- FIRST ORDER LOADINGS ----------------------------------

lambdaMatrix <- as.matrix(lavInspect(congenialPartialFit, "est")$`0`$lambda)[lavNames(congenialPartialFit, type="ov.ind"), lavNames(congenialPartialFit, type="lv")]

lambda_x <- lambdaMatrix[, !(colnames(lambdaMatrix) %in% gBase), drop = FALSE]

lambda_x_xi <- lambdaMatrix[, gBase, drop = FALSE]

lambda_xi <- solve(t(lambda_x) %*% lambda_x) %*% t(lambda_x) %*% lambda_x_xi

# ---------------------------------- FIRST ORDER MOMENTS ----------------------------------

firstTerm <- lambda_xi %*% phi_g %*% t(lambda_xi)

secondTerm <- lambda_xi %*% phi_gs

thirdTerm <- t(phi_gs) %*% t(lambda_xi)

phi_1 <- firstTerm + secondTerm + thirdTerm + phi_s

mean_1 <- setNames(
  as.numeric(
    lambda_xi %*% pooledMean[gBase] +
      pooledMean[rownames(lambda_xi)]
  ),
  rownames(lambda_xi)
)

# ----------------------------- IMPLIED FIRST ORDER PREDICTORS ------------------------------

FSDF$PsychopathyFO <-
  lambda_xi["Psychopathy", "Reference"] * FSDF$Reference +
  FSDF$Psychopathy

FSDF$NarcissismFO <-
  lambda_xi["Narcissism", "Reference"] * FSDF$Reference +
  FSDF$Narcissism

FSDF$PsychopathyFO <-
  (FSDF$PsychopathyFO - mean_1["Psychopathy"]) /
  sqrt(phi_1["Psychopathy", "Psychopathy"])

FSDF$NarcissismFO <-
  (FSDF$NarcissismFO - mean_1["Narcissism"]) /
  sqrt(phi_1["Narcissism", "Narcissism"])

lvNames <- lavNames(congenialPartialFit, "lv")

FSDF[, lvNames] <- sweep(
  sweep(
    as.matrix(FSDF[, lvNames]),
    MARGIN = 2,
    STATS = pooledMean[lvNames],
    FUN = "-"
  ),
  MARGIN = 2,
  STATS = sqrt(diag(pooledCov))[lvNames],
  FUN = "/"
)

# ---------------------------------- PHYSICAL -------------------------------------

physicalCoefs <- parsimoniousFit %>%
  filter(lhs=="Physical" & op %in% c("~", "~1")) %>%
  mutate(
    rhs = ifelse(op == "~1", "Intercept", rhs)
  ) %>%
  pull(Estimate, name = rhs)

dataPhysMach <- FSDF %>%
  mutate(
    fittedValue =
      physicalCoefs[["Intercept"]] +
      physicalCoefs[["Reference"]] * Reference,
    responseValue = Physical - 
      physicalCoefs[["Male"]] * Male -
      physicalCoefs[["Narcissism"]] * Narcissism -
      physicalCoefs[["Psychopathy"]] * Psychopathy,
    predictorValue = Reference,
    response = "Physical",
    predictor = "Machiavellianism",
    .keep = "none"
  )

dataPhysPsych <- FSDF %>%
  mutate(
    fittedValue =
      physicalCoefs[["Intercept"]] +
      physicalCoefs[["PsychopathyVWLE"]] * PsychopathyFO,
    responseValue = Physical - 
      physicalCoefs[["Male"]] * Male -
      physicalCoefs[["Narcissism"]] * Narcissism,
    predictorValue = PsychopathyFO,
    response = "Physical",
    predictor = "Psychopathy",
    .keep = "none"
  )

dataPhysNarc <- FSDF %>%
  mutate(
    fittedValue =
      physicalCoefs[["Intercept"]] +
      physicalCoefs[["NarcissismVWLE"]] * NarcissismFO,
    responseValue = Physical - 
      physicalCoefs[["Male"]] * Male -
      physicalCoefs[["Psychopathy"]] * Psychopathy,
    predictorValue = NarcissismFO,
    response = "Physical",
    predictor = "Narcissism",
    .keep = "none"
  )

# -------------------------------------- VERBAL ------------------------------------------

verbalCoefs <- parsimoniousFit %>%
  filter(lhs=="Verbal" & op %in% c("~", "~1")) %>%
  mutate(
    rhs = ifelse(op == "~1", "Intercept", rhs)
  ) %>%
  pull(Estimate, name = rhs)

dataVerbMach <- FSDF %>%
  mutate(
    fittedValue =
      verbalCoefs[["Intercept"]] +
      verbalCoefs[["Reference"]] * Reference,
    responseValue = Verbal - 
      verbalCoefs[["Male"]] * Male -
      verbalCoefs[["Narcissism"]] * Narcissism -
      verbalCoefs[["Psychopathy"]] * Psychopathy,
    predictorValue = Reference,
    response = "Verbal",
    predictor = "Machiavellianism",
    .keep = "none"
  )

dataVerbPsych <- FSDF %>%
  mutate(
    fittedValue =
      verbalCoefs[["Intercept"]] +
      verbalCoefs[["PsychopathyVWLE"]] * PsychopathyFO,
    responseValue = Verbal - 
      verbalCoefs[["Male"]] * Male -
      verbalCoefs[["Narcissism"]] * Narcissism,
    predictorValue = PsychopathyFO,
    response = "Verbal",
    predictor = "Psychopathy",
    .keep = "none"
  )

dataVerbNarc <- FSDF %>%
  mutate(
    fittedValue =
      verbalCoefs[["Intercept"]] +
      verbalCoefs[["NarcissismVWLE"]] * NarcissismFO,
    responseValue = Verbal - 
      verbalCoefs[["Male"]] * Male -
      verbalCoefs[["Psychopathy"]] * Psychopathy,
    predictorValue = NarcissismFO,
    response = "Verbal",
    predictor = "Narcissism",
    .keep = "none"
  )


# -------------------------------------- HOSTILITY ------------------------------------------

hostilityCoefs <- parsimoniousFit %>%
  filter(lhs=="Hostility" & op %in% c("~", "~1")) %>%
  mutate(
    rhs = ifelse(op == "~1", "Intercept", rhs)
  ) %>%
  pull(Estimate, name = rhs)

dataHostMach <- FSDF %>%
  mutate(
    fittedValue =
      hostilityCoefs[["Intercept"]] +
      hostilityCoefs[["Reference"]] * Reference,
    responseValue = Hostility - 
      hostilityCoefs[["Male"]] * Male -
      hostilityCoefs[["Narcissism"]] * Narcissism -
      hostilityCoefs[["Psychopathy"]] * Psychopathy,
    predictorValue = Reference,
    response = "Hostility",
    predictor = "Machiavellianism",
    .keep = "none"
  )

dataHostPsych <- FSDF %>%
  mutate(
    fittedValue =
      hostilityCoefs[["Intercept"]] +
      hostilityCoefs[["PsychopathyVWLE"]] * PsychopathyFO,
    responseValue = Hostility - 
      hostilityCoefs[["Male"]] * Male -
      hostilityCoefs[["Narcissism"]] * Narcissism,
    predictorValue = PsychopathyFO,
    response = "Hostility",
    predictor = "Psychopathy",
    .keep = "none"
  )

dataHostNarc <- FSDF %>%
  mutate(
    fittedValue =
      hostilityCoefs[["Intercept"]] +
      hostilityCoefs[["NarcissismVWLE"]] * NarcissismFO,
    responseValue = Hostility - 
      hostilityCoefs[["Male"]] * Male -
      hostilityCoefs[["Psychopathy"]] * Psychopathy,
    predictorValue = NarcissismFO,
    response = "Hostility",
    predictor = "Narcissism",
    .keep = "none"
  )

# -------------------------------------- ANGER ------------------------------------------

angerCoefs <- parsimoniousFit %>%
  filter(lhs=="Anger" & op %in% c("~", "~1")) %>%
  mutate(
    rhs = ifelse(op == "~1", "Intercept", rhs)
  ) %>%
  pull(Estimate, name = rhs)

dataAngerMach <- FSDF %>%
  mutate(
    fittedValue =
      angerCoefs[["Intercept"]] +
      angerCoefs[["Reference"]] * Reference,
    responseValue = Anger - 
      angerCoefs[["Male"]] * Male -
      angerCoefs[["Narcissism"]] * Narcissism -
      angerCoefs[["Psychopathy"]] * Psychopathy,
    predictorValue = Reference,
    response = "Anger",
    predictor = "Machiavellianism",
    .keep = "none"
  )

dataAngerPsych <- FSDF %>%
  mutate(
    fittedValue =
      angerCoefs[["Intercept"]] +
      angerCoefs[["PsychopathyVWLE"]] * PsychopathyFO,
    responseValue = Anger - 
      angerCoefs[["Male"]] * Male -
      angerCoefs[["Narcissism"]] * Narcissism,
    predictorValue = PsychopathyFO,
    response = "Anger",
    predictor = "Psychopathy",
    .keep = "none"
  )

dataAngerNarc <- FSDF %>%
  mutate(
    fittedValue =
      angerCoefs[["Intercept"]] +
      angerCoefs[["NarcissismVWLE"]] * NarcissismFO,
    responseValue = Anger - 
      angerCoefs[["Male"]] * Male -
      angerCoefs[["Psychopathy"]] * Psychopathy,
    predictorValue = NarcissismFO,
    response = "Anger",
    predictor = "Narcissism",
    .keep = "none"
  )


responseLevels <- c(
  "Physical",
  "Verbal",
  "Hostility",
  "Anger"
)

predictorLevels <- c(
  "Machiavellianism",
  "Psychopathy",
  "Narcissism"
)

dataPlot <- dplyr::bind_rows(
  dataPhysMach,
  dataPhysPsych,
  dataPhysNarc,
  dataVerbMach,
  dataVerbPsych,
  dataVerbNarc,
  dataHostMach,
  dataHostPsych,
  dataHostNarc,
  dataAngerMach,
  dataAngerPsych,
  dataAngerNarc
) %>%
  mutate(
    response = factor(response, levels = responseLevels),
    predictor = factor(predictor, levels = predictorLevels)
  )
  
exploratoryPlot <- ggplot(dataPlot, aes(x=predictorValue, y=responseValue, color=predictor))+
  geom_point(
    alpha = 0.5,
    size = 0.05,
    show.legend = FALSE
  ) +
  geom_line(
    aes(y = fittedValue),
    linewidth = 0.75,
    show.legend = TRUE
  ) +
  scale_color_manual(
    values = c(
      Machiavellianism = "seagreen",
      Psychopathy      = "darkgoldenrod1",
      Narcissism       = "dodgerblue2"
    )
  ) +
  facet_wrap(~response, ncol = 2, scales = "fixed") +
  labs(
    title = NULL,
    x = NULL,
    y = NULL
  ) +
  theme_minimal(
    base_family = "serif",
    base_size = 9.5
  ) +
  theme(
    strip.text = element_text(
      face = "bold",
      size = 11
    ),
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.text = element_text(size = 8),
    legend.text = element_text(
      face = "bold",
      size = 10
    ),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(
      linewidth = 0.25,
      colour = "grey88"
    )
  ) +
  guides(
    color = guide_legend(
      override.aes = list(
        linewidth = 1.5,
        alpha = 1
      )
    )
  )

if(export) {
  ggsave(
    "../Plots/exploratoryPlot.pdf",
    plot = exploratoryPlot,
    device = "pdf",
    width = 7,
    height = 4.6,
    units = "in",
    useDingbats = FALSE
  )
  
  ggsave(
    "../Plots/exploratoryPlot.png",
    plot = exploratoryPlot,
    #width = 5.645,
    #height = 4,
    width = 7,
    height = 4.6,
    units = "in",
    dpi = 600,
    bg = "white"
  ) 
}
```

#### Sex differences

```{r}

DTFS <- lavPredict(congenialPartialFit, method = "Regression", transform = FALSE)
caseIdx <- unlist(lavInspect(congenialPartialFit, "case.idx"), use.names = FALSE)
DTFSmat <- do.call(rbind, DTFS)
FSDF <- cbind(
  replicationData[caseIdx, , drop = FALSE],
  DTFSmat
)

pMale <- mean(replicationData$Male)
pFemale <- 1 - pMale

gBase <- c("Reference")

# ------------------------------------ POOLED MOMENTS --------------------------------------

groupCov  <- lavInspect(congenialPartialFit, "cov.lv")
groupMean <- lavInspect(congenialPartialFit, "mean.lv")

meanDifference <- groupMean[[1]] - groupMean[[2]]

pooledCov <-
  pFemale * groupCov[[1]] +
  pMale   * groupCov[[2]] +
  pFemale * pMale * tcrossprod(meanDifference)

pooledMean <-
  pFemale * groupMean[[1]] +
  pMale   * groupMean[[2]]

# --------------------------------- REDUCED FORM COVARIANCE --------------------------------

phi_g <- pooledCov[rownames(pooledCov) %in% gBase, colnames(pooledCov) %in% gBase, drop=FALSE]

phi_s <- pooledCov[!(rownames(pooledCov) %in% gBase), !(colnames(pooledCov) %in% gBase), drop=FALSE]

phi_gs <- pooledCov[rownames(pooledCov) %in% gBase, !(colnames(pooledCov) %in% gBase), drop=FALSE]

# ---------------------------------- FIRST ORDER LOADINGS ----------------------------------

lambdaMatrix <- as.matrix(lavInspect(congenialPartialFit, "est")$`0`$lambda)[lavNames(congenialPartialFit, type="ov.ind"), lavNames(congenialPartialFit, type="lv")]

lambda_x <- lambdaMatrix[, !(colnames(lambdaMatrix) %in% gBase), drop = FALSE]

lambda_x_xi <- lambdaMatrix[, gBase, drop = FALSE]

lambda_xi <- solve(t(lambda_x) %*% lambda_x) %*% t(lambda_x) %*% lambda_x_xi

# ---------------------------------- FIRST ORDER MOMENTS ----------------------------------

firstTerm <- lambda_xi %*% phi_g %*% t(lambda_xi)

secondTerm <- lambda_xi %*% phi_gs

thirdTerm <- t(phi_gs) %*% t(lambda_xi)

phi_1 <- firstTerm + secondTerm + thirdTerm + phi_s

mean_1 <- setNames(
  as.numeric(
    lambda_xi %*% pooledMean[gBase] +
      pooledMean[rownames(lambda_xi)]
  ),
  rownames(lambda_xi)
)

# ----------------------------- IMPLIED FIRST ORDER PREDICTORS ------------------------------

FSDF$PsychopathyFO <-
  lambda_xi["Psychopathy", "Reference"] * FSDF$Reference +
  FSDF$Psychopathy

FSDF$NarcissismFO <-
  lambda_xi["Narcissism", "Reference"] * FSDF$Reference +
  FSDF$Narcissism

FSDF$PsychopathyFO <-
  (FSDF$PsychopathyFO - mean_1["Psychopathy"]) /
  sqrt(phi_1["Psychopathy", "Psychopathy"])

FSDF$NarcissismFO <-
  (FSDF$NarcissismFO - mean_1["Narcissism"]) /
  sqrt(phi_1["Narcissism", "Narcissism"])

lvNames <- lavNames(congenialPartialFit, "lv")

FSDF[, lvNames] <- sweep(
  sweep(
    as.matrix(FSDF[, lvNames]),
    MARGIN = 2,
    STATS = pooledMean[lvNames],
    FUN = "-"
  ),
  MARGIN = 2,
  STATS = sqrt(diag(pooledCov))[lvNames],
  FUN = "/"
)

# ---------------------------------- PHYSICAL -------------------------------------

physicalCoefs <- saturatedFit%>%
  filter(lhs=="Physical" & op %in% c("~", "~1")) %>%
  mutate(
    rhs = ifelse(op == "~1", "Intercept", rhs)
  ) %>%
  pull(Estimate, name = rhs)

dataPhysMach <- FSDF %>%
  mutate(
    fittedValue =
      physicalCoefs[["Intercept"]] +
      physicalCoefs[["Male"]] * Male +
      physicalCoefs[["Reference"]] * Reference +
      physicalCoefs[["Reference:Male"]] * Reference * Male,
    responseValue = Physical - 
      physicalCoefs[["Narcissism"]] * Narcissism -
      physicalCoefs[["Narcissism:Male"]] * Narcissism * Male -
      physicalCoefs[["Psychopathy"]] * Psychopathy -
      physicalCoefs[["Psychopathy:Male"]] * Psychopathy * Male,
    predictorValue = Reference,
    response = "Physical",
    predictor = "Machiavellianism",
    sex = as.factor(ifelse(Male==1, "Male", "Female")),
    .keep = "none"
  )

dataPhysPsych <- FSDF %>%
  mutate(
    fittedValue =
      physicalCoefs[["Intercept"]] +
      physicalCoefs[["Male"]] * Male +
      physicalCoefs[["PsychopathyVWLE"]] * PsychopathyFO +
      physicalCoefs[["Psychopathy:MaleVWLE"]] * PsychopathyFO * Male,
    responseValue = Physical - 
      physicalCoefs[["Narcissism"]] * Narcissism -
      physicalCoefs[["Narcissism:Male"]] * Narcissism * Male,
    predictorValue = PsychopathyFO,
    response = "Physical",
    predictor = "Psychopathy",
    sex = as.factor(ifelse(Male==1, "Male", "Female")),
    .keep = "none"
  )

dataPhysNarc <- FSDF %>%
  mutate(
    fittedValue =
      physicalCoefs[["Intercept"]] +
      physicalCoefs[["Male"]] * Male +
      physicalCoefs[["NarcissismVWLE"]] * NarcissismFO +
      physicalCoefs[["Narcissism:MaleVWLE"]] * NarcissismFO * Male,
    responseValue = Physical - 
      physicalCoefs[["Psychopathy"]] * Psychopathy -
      physicalCoefs[["Psychopathy:Male"]] * Psychopathy * Male,
    predictorValue = NarcissismFO,
    response = "Physical",
    predictor = "Narcissism",
    sex = as.factor(ifelse(Male==1, "Male", "Female")),
    .keep = "none"
  )

# -------------------------------------- VERBAL ------------------------------------------

verbalCoefs <- saturatedFit%>%
  filter(lhs=="Verbal" & op %in% c("~", "~1")) %>%
  mutate(
    rhs = ifelse(op == "~1", "Intercept", rhs)
  ) %>%
  pull(Estimate, name = rhs)

dataVerbMach <- FSDF %>%
  mutate(
    fittedValue =
      verbalCoefs[["Intercept"]] +
      verbalCoefs[["Male"]] * Male +
      verbalCoefs[["Reference"]] * Reference +
      verbalCoefs[["Reference:Male"]] * Reference * Male,
    responseValue = Verbal - 
      verbalCoefs[["Narcissism"]] * Narcissism -
      verbalCoefs[["Narcissism:Male"]] * Narcissism * Male -
      verbalCoefs[["Psychopathy"]] * Psychopathy -
      verbalCoefs[["Psychopathy:Male"]] * Psychopathy * Male,
    predictorValue = Reference,
    response = "Verbal",
    predictor = "Machiavellianism",
    sex = as.factor(ifelse(Male==1, "Male", "Female")),
    .keep = "none"
  )

dataVerbPsych <- FSDF %>%
  mutate(
    fittedValue =
      verbalCoefs[["Intercept"]] +
      verbalCoefs[["Male"]] * Male +
      verbalCoefs[["PsychopathyVWLE"]] * PsychopathyFO +
      verbalCoefs[["Psychopathy:MaleVWLE"]] * PsychopathyFO * Male,
    responseValue = Verbal - 
      verbalCoefs[["Narcissism"]] * Narcissism -
      verbalCoefs[["Narcissism:Male"]] * Narcissism * Male,
    predictorValue = PsychopathyFO,
    response = "Verbal",
    predictor = "Psychopathy",
    sex = as.factor(ifelse(Male==1, "Male", "Female")),
    .keep = "none"
  )

dataVerbNarc <- FSDF %>%
  mutate(
    fittedValue =
      verbalCoefs[["Intercept"]] +
      verbalCoefs[["Male"]] * Male +
      verbalCoefs[["NarcissismVWLE"]] * NarcissismFO +
      verbalCoefs[["Narcissism:MaleVWLE"]] * NarcissismFO * Male,
    responseValue = Verbal - 
      verbalCoefs[["Psychopathy"]] * Psychopathy -
      verbalCoefs[["Psychopathy:Male"]] * Psychopathy * Male,
    predictorValue = NarcissismFO,
    response = "Verbal",
    predictor = "Narcissism",
    sex = as.factor(ifelse(Male==1, "Male", "Female")),
    .keep = "none"
  )


# -------------------------------------- HOSTILITY ------------------------------------------

hostilityCoefs <- saturatedFit%>%
  filter(lhs=="Hostility" & op %in% c("~", "~1")) %>%
  mutate(
    rhs = ifelse(op == "~1", "Intercept", rhs)
  ) %>%
  pull(Estimate, name = rhs)

dataHostMach <- FSDF %>%
  mutate(
    fittedValue =
      hostilityCoefs[["Intercept"]] +
      hostilityCoefs[["Male"]] * Male +
      hostilityCoefs[["Reference"]] * Reference +
      hostilityCoefs[["Reference:Male"]] * Reference * Male,
    responseValue = Hostility - 
      hostilityCoefs[["Narcissism"]] * Narcissism -
      hostilityCoefs[["Narcissism:Male"]] * Narcissism * Male -
      hostilityCoefs[["Psychopathy"]] * Psychopathy -
      hostilityCoefs[["Psychopathy:Male"]] * Psychopathy * Male,
    predictorValue = Reference,
    response = "Hostility",
    predictor = "Machiavellianism",
    sex = as.factor(ifelse(Male==1, "Male", "Female")),
    .keep = "none"
  )

dataHostPsych <- FSDF %>%
  mutate(
    fittedValue =
      hostilityCoefs[["Intercept"]] +
      hostilityCoefs[["Male"]] * Male +
      hostilityCoefs[["PsychopathyVWLE"]] * PsychopathyFO +
      hostilityCoefs[["Psychopathy:MaleVWLE"]] * PsychopathyFO * Male,
    responseValue = Hostility - 
      hostilityCoefs[["Narcissism"]] * Narcissism -
      hostilityCoefs[["Narcissism:Male"]] * Narcissism * Male,
    predictorValue = PsychopathyFO,
    response = "Hostility",
    predictor = "Psychopathy",
    sex = as.factor(ifelse(Male==1, "Male", "Female")),
    .keep = "none"
  )

dataHostNarc <- FSDF %>%
  mutate(
    fittedValue =
      hostilityCoefs[["Intercept"]] +
      hostilityCoefs[["Male"]] * Male +
      hostilityCoefs[["NarcissismVWLE"]] * NarcissismFO +
      hostilityCoefs[["Narcissism:MaleVWLE"]] * NarcissismFO * Male,
    responseValue = Hostility - 
      hostilityCoefs[["Psychopathy"]] * Psychopathy -
      hostilityCoefs[["Psychopathy:Male"]] * Psychopathy * Male,
    predictorValue = NarcissismFO,
    response = "Hostility",
    predictor = "Narcissism",
    sex = as.factor(ifelse(Male==1, "Male", "Female")),
    .keep = "none"
  )

# -------------------------------------- ANGER ------------------------------------------

angerCoefs <- saturatedFit%>%
  filter(lhs=="Anger" & op %in% c("~", "~1")) %>%
  mutate(
    rhs = ifelse(op == "~1", "Intercept", rhs)
  ) %>%
  pull(Estimate, name = rhs)

dataAngerMach <- FSDF %>%
  mutate(
    fittedValue =
      angerCoefs[["Intercept"]] +
      angerCoefs[["Male"]] * Male +
      angerCoefs[["Reference"]] * Reference +
      angerCoefs[["Reference:Male"]] * Reference * Male,
    responseValue = Anger - 
      angerCoefs[["Narcissism"]] * Narcissism -
      angerCoefs[["Narcissism:Male"]] * Narcissism * Male -
      angerCoefs[["Psychopathy"]] * Psychopathy -
      angerCoefs[["Psychopathy:Male"]] * Psychopathy * Male,
    predictorValue = Reference,
    response = "Anger",
    predictor = "Machiavellianism",
    sex = as.factor(ifelse(Male==1, "Male", "Female")),
    .keep = "none"
  )

dataAngerPsych <- FSDF %>%
  mutate(
    fittedValue =
      angerCoefs[["Intercept"]] +
      angerCoefs[["Male"]] * Male +
      angerCoefs[["PsychopathyVWLE"]] * PsychopathyFO +
      angerCoefs[["Psychopathy:MaleVWLE"]] * PsychopathyFO * Male,
    responseValue = Anger - 
      angerCoefs[["Narcissism"]] * Narcissism -
      angerCoefs[["Narcissism:Male"]] * Narcissism * Male,
    predictorValue = PsychopathyFO,
    response = "Anger",
    predictor = "Psychopathy",
    sex = as.factor(ifelse(Male==1, "Male", "Female")),
    .keep = "none"
  )

dataAngerNarc <- FSDF %>%
  mutate(
    fittedValue =
      angerCoefs[["Intercept"]] +
      angerCoefs[["Male"]] * Male +
      angerCoefs[["NarcissismVWLE"]] * NarcissismFO +
      angerCoefs[["Narcissism:MaleVWLE"]] * NarcissismFO * Male,
    responseValue = Anger - 
      angerCoefs[["Psychopathy"]] * Psychopathy -
      angerCoefs[["Psychopathy:Male"]] * Psychopathy * Male,
    predictorValue = NarcissismFO,
    response = "Anger",
    predictor = "Narcissism",
    sex = as.factor(ifelse(Male==1, "Male", "Female")),
    .keep = "none"
  )


responseLevels <- c(
  "Physical",
  "Verbal",
  "Hostility",
  "Anger"
)

predictorLevels <- c(
  "Machiavellianism",
  "Psychopathy",
  "Narcissism"
)

dataPlot <- dplyr::bind_rows(
  dataPhysMach,
  dataPhysPsych,
  dataPhysNarc,
  dataVerbMach,
  dataVerbPsych,
  dataVerbNarc,
  dataHostMach,
  dataHostPsych,
  dataHostNarc,
  dataAngerMach,
  dataAngerPsych,
  dataAngerNarc
) %>%
  mutate(
    response = factor(response, levels = responseLevels),
    predictor = factor(predictor, levels = predictorLevels)
  )

exploratoryPlot <- ggplot(dataPlot, aes(x=predictorValue, y=responseValue, color=sex))+
  geom_point(
    alpha = 0.5,
    size = 0.05,
    show.legend = FALSE
  ) +
  geom_line(
    aes(y = fittedValue),
    linewidth = 0.75,
    show.legend = TRUE
  ) +
  scale_color_manual(
    values = c(
      Female = "steelblue",
      Male   = "lightcoral"
    )
  ) +
  facet_grid(
    response ~ predictor, 
    scales = "fixed",
    switch = "y"
  ) + 
  scale_y_continuous(position = "right") +
  labs(
    title = NULL,
    x = NULL,
    y = NULL
  ) +
  theme_minimal(
    base_family = "serif",
    base_size = 9.5
  ) +
  theme(
    strip.text = element_text(
      face = "bold",
      size = 11
    ),
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.text = element_text(size = 8),
    legend.text = element_text(
      face = "bold",
      size = 10
    ),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(
      linewidth = 0.25,
      colour = "grey88"
    )
  ) +
  guides(
    color = guide_legend(
      override.aes = list(
        linewidth = 1.5,
        alpha = 1
      )
    )
  )

if(export) {
  ggsave(
    "../Plots/sexDifferencesPlot.pdf",
    plot = exploratoryPlot,
    device = "pdf",
    width = 7,
    height = 8,
    units = "in",
    useDingbats = FALSE
  )
  
  ggsave(
    "../Plots/sexDifferencesPlot.png",
    plot = exploratoryPlot,
    width = 7,
    height = 8,
    units = "in",
    dpi = 600,
    bg = "white"
  ) 
}
```

## Sensitivity

### Correlated factors

```{r}

set.seed(masterSeed)

correlatedStructuralModel <- gsub(
  "Reference",
  "Machiavellianism",
  parsimoniousModel,
  fixed = TRUE
)

if (parallelSupported) {
  structuralFit <- pbmcapply::pbmclapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = correlatedStructuralModel,
    measurementFit = congenialFirstOrderFit,
    VWLE=FALSE,
    g=NULL,
    s=NULL,
    covariatesVWLE = NULL,
    data = replicationData,
    masterSeed = masterSeed,
    mc.cores = availableCores,
    mc.set.seed = TRUE
  )
} else {
  structuralFit <- lapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = correlatedStructuralModel,
    measurementFit = congenialFirstOrderFit,
    VWLE=FALSE,
    g=NULL,
    s=NULL,
    covariatesVWLE = NULL,
    data = replicationData,
    masterSeed = masterSeed
  )
}

correlatedFactorsFit <- processFunPV(structuralFit)

bootPath <- "../Data/correlatedFactorsBoot.rds"

targetReached <- FALSE
restartLocal <- restartBootstraps

while (runBootstraps && !targetReached) {
  
  if(!restartLocal) {
    storedResults <- readRDS(bootPath)
    lastAttempt <- attr(storedResults, "lastAttempt")
    setStart <- lastAttempt + 1L
    remainingDraws <- B - n_distinct(storedResults$draw)
    setEnd <- setStart + remainingDraws - 1L
  } else {
    setStart <- 1
    setEnd <- B
  }
  
  targetReached <- setStart > setEnd
  
  if (!targetReached) {
  
    if (parallelSupported && setStart < setEnd) {
      structuralFit <- pbmcapply::pbmclapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = correlatedStructuralModel,
        measurementModel = list(responseMeasurement, firstOrderMeasurement),
        fullMeasurement = congenialFirstOrderFit,
        VWLE=FALSE,
        g=NULL,
        s=NULL,
        covariatesVWLE = NULL,
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed,
        mc.cores = availableCores,
        mc.set.seed = TRUE
      )
    } else {
      structuralFit <- lapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = correlatedStructuralModel,
        measurementModel = list(responseMeasurement, firstOrderMeasurement),
        fullMeasurement = congenialFirstOrderFit,
        VWLE=FALSE,
        g=NULL,
        s=NULL,
        covariatesVWLE = NULL,
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed
      )
    }
  
    if(!restartLocal) {
      structuralFit <- dplyr::bind_rows(storedResults, structuralFit)
      rm(storedResults)
    } else {
      structuralFit <- dplyr::bind_rows(structuralFit)
    }
    
    attr(structuralFit, "lastAttempt") <- setEnd
    
    saveRDS(structuralFit, bootPath)
    
    restartLocal <- FALSE
    
    rm(structuralFit)
  }
}


correlatedFactorsBoot <- processFunBoot(correlatedFactorsFit, readRDS("../Data/correlatedFactorsBoot.rds")) %>%
  mutate(
    isReference = ifelse(rhs=="Reference", 1, 0),
    rhs = recode(
      rhs,
      Machiavellianism = "Machiavellianism (FO)",
      Psychopathy = "Psychopathy (FO)",
      Narcissism = "Narcissism (FO)"
    ),
    reference = "Correlated"
  )

correlatedFactorsBoot %>%
  filter(op %in% c("~", "gof") & rhs != "N") %>%
  dplyr::select(lhs, rhs, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootSuccess, bootRate) %>%
  mutate(
    across(c(Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootRate), \(x) round(x, digits = 3))
  )
```

### Machiavellianism reference

```{r}

machiavellianismReferenceBoot <- processFunBoot(parsimoniousFit, readRDS("../Data/parsimoniousBoot.rds")) %>%
  mutate(
    isReference = ifelse(rhs=="Reference", 1, 0),
    rhs = recode(rhs, Reference = "Machiavellianism (FO)"),
    reference = "Machiavellianism"
  )

machiavellianismReferenceBoot %>%
  filter(op %in% c("~", "gof") & rhs != "N") %>%
  dplyr::select(lhs, rhs, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootSuccess, bootRate) %>%
  mutate(
    across(c(Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootRate), \(x) round(x, digits = 3))
  )
```

### Psychopathy reference

```{r}

set.seed(masterSeed)

psychopathyMeasurement <- paste(
  'Reference =~ ', paste(coreItems, collapse = " + "), ' \n ',
  'Machiavellianism =~ ', paste(machiavellianismItems, collapse = " + "), ' \n ',
  'Narcissism =~ ', paste(narcissismItems, collapse = " + "), ' \n ',
  'Machiavellianism ~~ 0*Reference \n ',
  'Narcissism ~~ 0*Reference \n '
)

partialPsychopathyFit <- cfa(
  psychopathyMeasurement,  
  estimator = "ML",
  se = "none",
  test = "none",
  baseline = FALSE,
  meanstructure = TRUE,
  std.lv = TRUE,
  group = "Male",
  group.label = c("0", "1"),
  group.equal = c("loadings", "intercepts"),
  group.partial = paste0(freeSD3, "~ 1"),
  data = replicationData
)

partialPsychopathyFit <- congenialFun(
  measurementFit=list(partialInvarianceFitBPAQ, partialPsychopathyFit), 
  covariates=c(
    "Age"
  ),
  group="Male",
  groupLabels = c("0", "1"),
  data=replicationData
)

psychopathyStructural <- gsub(
  "Psychopathy",
  "Machiavellianism",
  parsimoniousModel,
  fixed = TRUE
)

if (parallelSupported) {
  structuralFit <- pbmcapply::pbmclapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = psychopathyStructural, 
    measurementFit = partialPsychopathyFit,
    VWLE=TRUE,
    g=c("Reference"),
    s=list(c("Machiavellianism", "Narcissism")),
    covariatesVWLE = c("Male"),
    data = replicationData,
    masterSeed = masterSeed,
    mc.cores = availableCores,
    mc.set.seed = TRUE
  )
} else {
  structuralFit <- lapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = psychopathyStructural, 
    measurementFit = partialPsychopathyFit,
    VWLE=TRUE,
    g=c("Reference"),
    s=list(c("Machiavellianism", "Narcissism")),
    covariatesVWLE = c("Male"),
    data = replicationData,
    masterSeed = masterSeed
  )
}

psychopathyReferenceFit <- processFunPV(structuralFit)

bootPath <- "../Data/psychopathyReferenceBoot.rds"

targetReached <- FALSE
restartLocal <- restartBootstraps

while (runBootstraps && !targetReached) {
  
  if(!restartLocal) {
    storedResults <- readRDS(bootPath)
    lastAttempt <- attr(storedResults, "lastAttempt")
    setStart <- lastAttempt + 1L
    remainingDraws <- B - n_distinct(storedResults$draw)
    setEnd <- setStart + remainingDraws - 1L
  } else {
    setStart <- 1
    setEnd <- B
  }
  
  targetReached <- setStart > setEnd
  
  if (!targetReached) {
  
    if (parallelSupported && setStart < setEnd) {
      structuralFit <- pbmcapply::pbmclapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = psychopathyStructural, 
        measurementModel = list(responseMeasurement, psychopathyMeasurement),
        fullMeasurement = partialPsychopathyFit,
        VWLE=TRUE,
        g=c("Reference"),
        s=list(c("Machiavellianism", "Narcissism")),
        covariatesVWLE = c("Male"),
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed,
        mc.cores = availableCores,
        mc.set.seed = TRUE
      )
    } else {
      structuralFit <- lapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = psychopathyStructural, 
        measurementModel = list(responseMeasurement, psychopathyMeasurement),
        fullMeasurement = partialPsychopathyFit,
        VWLE=TRUE,
        g=c("Reference"),
        s=list(c("Machiavellianism", "Narcissism")),
        covariatesVWLE = c("Male"),
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed
      )
    }
    
    if(!restartLocal) {
      structuralFit <- dplyr::bind_rows(storedResults, structuralFit)
      rm(storedResults)
    } else {
      structuralFit <- dplyr::bind_rows(structuralFit)
    }
    
    attr(structuralFit, "lastAttempt") <- setEnd
    
    saveRDS(structuralFit, bootPath)
    
    restartLocal <- FALSE
    
    rm(structuralFit)
  }
}

psychopathyReferenceBoot <- processFunBoot(psychopathyReferenceFit, readRDS("../Data/psychopathyReferenceBoot.rds")) %>%
  mutate(
    isReference = ifelse(rhs=="Reference", 1, 0),
    rhs = recode(rhs, Reference = "Psychopathy (FO)"),
    reference = "Psychopathy"
  )

psychopathyReferenceBoot %>%
  filter(op %in% c("~", "gof") & rhs != "N") %>%
  dplyr::select(lhs, rhs, Eta2, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootSuccess, bootRate) %>%
  mutate(
    across(c(Eta2, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootRate), \(x) round(x, digits = 3))
  )
```

### Narcissism reference

```{r}

set.seed(masterSeed)

narcissismMeasurement <- paste(
  'Reference =~ ', paste(coreItems, collapse = " + "), ' \n ',
  'Machiavellianism =~ ', paste(machiavellianismItems, collapse = " + "), ' \n ',
  'Psychopathy =~ ', paste(psychopathyItems, collapse = " + "), ' \n ',
  'Machiavellianism ~~ 0*Reference \n ',
  'Psychopathy ~~ 0*Reference \n '
)

partialNarcissismFit <- cfa(
  narcissismMeasurement,  
  estimator = "ML",
  se = "none",
  test = "none",
  baseline = FALSE,
  meanstructure = TRUE,
  std.lv = TRUE,
  group = "Male",
  group.label = c("0", "1"),
  group.equal = c("loadings", "intercepts"),
  group.partial = paste0(freeSD3, "~ 1"),
  data = replicationData
)

partialNarcissismFit <- congenialFun(
  measurementFit=list(partialInvarianceFitBPAQ, partialNarcissismFit), 
  covariates=NULL,
  group="Male",
  groupLabels = c("0", "1"),
  data=replicationData
)

narcissismStructural <- gsub(
  "Narcissism",
  "Machiavellianism",
  parsimoniousModel,
  fixed = TRUE
)

if (parallelSupported) {
  structuralFit <- pbmcapply::pbmclapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = narcissismStructural, 
    measurementFit = partialNarcissismFit,
    VWLE=TRUE,
    g=c("Reference"),
    s=list(c("Machiavellianism", "Psychopathy")),
    covariatesVWLE = c("Male"),
    data = replicationData,
    masterSeed = masterSeed,
    mc.cores = availableCores,
    mc.set.seed = TRUE
  )
} else {
  structuralFit <- lapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = narcissismStructural, 
    measurementFit = partialNarcissismFit,
    VWLE=TRUE,
    g=c("Reference"),
    s=list(c("Machiavellianism", "Psychopathy")),
    covariatesVWLE = c("Male"),
    data = replicationData,
    masterSeed = masterSeed
  )
}

narcissismReferenceFit <- processFunPV(structuralFit)

bootPath <- "../Data/narcissismReferenceBoot.rds"

targetReached <- FALSE
restartLocal <- restartBootstraps

while (runBootstraps && !targetReached) {

  if(!restartLocal) {
    storedResults <- readRDS(bootPath)
    lastAttempt <- attr(storedResults, "lastAttempt")
    setStart <- lastAttempt + 1L
    remainingDraws <- B - n_distinct(storedResults$draw)
    setEnd <- setStart + remainingDraws - 1L
  } else {
    setStart <- 1
    setEnd <- B
  }

  targetReached <- setStart > setEnd

  if (!targetReached) {
    
    if (parallelSupported && setStart < setEnd) {
      structuralFit <- pbmcapply::pbmclapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = narcissismStructural, 
        measurementModel = list(responseMeasurement, narcissismMeasurement),
        fullMeasurement = partialNarcissismFit,
        congenialCovariates = NULL,
        VWLE=TRUE,
        g=c("Reference"),
        s=list(c("Machiavellianism", "Psychopathy")),
        covariatesVWLE = c("Male"),
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed,
        mc.cores = availableCores,
        mc.set.seed = TRUE
      )
    } else {
      structuralFit <- lapply(
        X = setStart:setEnd,
        FUN = bootFun,
        mDraws = MB,
        structuralModel = narcissismStructural, 
        measurementModel = list(responseMeasurement, narcissismMeasurement),
        fullMeasurement = partialNarcissismFit,
        congenialCovariates = NULL,
        VWLE=TRUE,
        g=c("Reference"),
        s=list(c("Machiavellianism", "Psychopathy")),
        covariatesVWLE = c("Male"),
        group="Male",
        groupLabels = c("0", "1"),
        invariance = list(c("loadings", "intercepts"), c("loadings", "intercepts")),
        groupFree = list(freeBPAQ, freeSD3),
        data = replicationData,
        masterSeed = masterSeed
      )
    }
    
    if(!restartLocal) {
      structuralFit <- dplyr::bind_rows(storedResults, structuralFit)
      rm(storedResults)
    } else {
      structuralFit <- dplyr::bind_rows(structuralFit)
    }
    
    attr(structuralFit, "lastAttempt") <- setEnd
    
    saveRDS(structuralFit, bootPath)
    
    restartLocal <- FALSE
    
    rm(structuralFit)
  }
}


narcissismReferenceBoot <- processFunBoot(narcissismReferenceFit, readRDS("../Data/narcissismReferenceBoot.rds")) %>%
  mutate(
    isReference = ifelse(rhs=="Reference", 1, 0),
    rhs = recode(rhs, Reference = "Narcissism (FO)"),
    reference = "Narcissism"
  )

narcissismReferenceBoot %>%
  filter(op %in% c("~", "gof") & rhs != "N") %>%
  dplyr::select(lhs, rhs, Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootSuccess, bootRate) %>%
  mutate(
    across(c(Estimate, SE, Z, P, pBoot, meanBoot, biasBoot, bootRate), \(x) round(x, digits = 3))
  )
```

### Sensitivity table

#### HTML

```{r}

outcomeLevels <- c(
  "Physical",
  "Verbal",
  "Hostility",
  "Anger"
)

outcomeLabels <- c(
  "Physical",
  "Verbal",
  "Hostility",
  "Anger"
)

termLevels <- c(
  "Machiavellianism (FO)",
  "Psychopathy (FO)",
  "Narcissism (FO)",
  "Machiavellianism (S)",
  "Psychopathy (S)",
  "Narcissism (S)",
  "Male",
  "",
  "R2"
)

termLabels <- c(
  "Mach (FO)",
  "Psych (FO)",
  "Narc (FO)",
  "Mach (S)",
  "Psych (S)",
  "Narc (S)",
  "Male",
  "Intercept",
  "R²"
)

modelLevels <- c("Machiavellianism", "Psychopathy", "Narcissism", "Correlated")
modelLabels <- c("Machiavellianism", "Psychopathy", "Narcissism", "Correlated")

sensitivityTable <- dplyr::bind_rows(
  machiavellianismReferenceBoot, 
  psychopathyReferenceBoot,
  narcissismReferenceBoot,
  correlatedFactorsBoot
  ) %>%
  dplyr::filter(
    lhs %in% outcomeLevels
  ) %>%
  mutate(
    rhs = recode(
      rhs, 
      Machiavellianism = "Machiavellianism (S)",
      Psychopathy = "Psychopathy (S)",
      Narcissism = "Narcissism (S)"
    ),
    rhs = sub("VWLE$", " (FO)", rhs),
    stars = case_when(
      pBoot <= 0.001 ~ "***",
      pBoot <= 0.01  ~ "**",
      pBoot <= 0.05  ~ "*",
      is.na(pBoot) & P <= 0.001 ~ "***",
      is.na(pBoot) & P <= 0.01  ~ "**",
      is.na(pBoot) & P <= 0.05  ~ "*",
      .default = ""
    ),
    pFormatted = case_when(
      pBoot < 0.001 ~ "&lt;.001",
      pBoot >= 0.001 ~ paste0("=", sub("^0", "", sprintf("%.3f", pBoot))),
      is.na(pBoot) & P < 0.001 ~ "&lt;.001",
      .default = paste0("=", sub("^0", "", sprintf("%.3f", P))),
    ),
    Estimate = case_when(
      isReference == 1 ~ sprintf(
        "<span style='font-weight:bold;'>%.3f%s</span><br>(%.3f)<br>p%s",
        Estimate, stars, SE, pFormatted
#        "<span style='font-weight:bold;'>%.3f</span><br>(%.3f)<br>p%s",
#        Estimate, SE, pFormatted
      ),
      op %in% c("~", "~1") ~ sprintf(
        "%.3f%s<br>(%.3f)<br>p%s",
        Estimate, stars, SE, pFormatted
#        "%.3f<br>(%.3f)<br>p%s",
#        Estimate, SE, pFormatted
      ),
      .default = sprintf("%.3f", Estimate)
    ),
    Outcome = factor(
      lhs,
      levels = outcomeLevels,
      labels = outcomeLabels
    ),
    Model = factor(
      reference,
      levels = modelLevels,
      labels = modelLabels
    ),
    Term = factor(
      rhs, 
      levels = termLevels,
      labels = termLabels
    ),
    Panel = factor(
      case_when(
        endsWith(rhs, "(FO)") ~ "First order",
        op == "gof" ~ "Model information",
        .default = "Specific"
      ),
      levels = c("First order", "Specific", "Model information")
    )
  ) %>%
  dplyr::select(
    Outcome,
    Term,
    Model,
    Estimate,
    Panel
  )

sensitivityTableFull <- sensitivityTable %>%
  filter(
    !is.na(Outcome),
    !is.na(Panel),
    !is.na(Term)
  ) %>%
  tidyr::pivot_wider(
    id_cols = c(Panel, Term),
    names_from = c(Outcome, Model),
    values_from = Estimate,
    names_sep = "_",
    names_expand = TRUE
  ) %>%
  arrange(Panel, Term)

sensitivityTableLean <- sensitivityTable %>%
  filter(
    !is.na(Outcome),
    !is.na(Panel),
    Term %in% c(
      "Mach (FO)",
      "Psych (FO)",
      "Narc (FO)",
      "R²"
    ),
    Outcome %in% c("Physical", "Verbal", "Hostility")
  ) %>%
  mutate(
    Outcome = forcats::fct_drop(Outcome)
  ) %>%
  tidyr::pivot_wider(
    id_cols = c(Panel, Term),
    names_from = c(Outcome, Model),
    values_from = Estimate,
    names_sep = "_",
    names_expand = TRUE
  ) %>%
  arrange(Panel, Term)

sensitivityGT <- sensitivityTableLean %>%
  dplyr::select(-Panel) %>%
  gt::gt(
    rowname_col = "Term"
  ) %>%
  gt::tab_spanner(
    label = "Bifactor (S-1)",
    id = "bifactor_physical",
    level = 1,
    columns = starts_with("Physical_") &
      ends_with(c("Machiavellianism", "Psychopathy", "Narcissism"))
  ) %>%
  gt::tab_spanner(
    label = "Bifactor (S-1)",
    id = "bifactor_verbal",
    level = 1,
    columns = starts_with("Verbal_") &
      ends_with(c("Machiavellianism", "Psychopathy", "Narcissism"))
  ) %>%
  gt::tab_spanner(
    label = "Bifactor (S-1)",
    id = "bifactor_hostility",
    level = 1,
    columns = starts_with("Hostility_") &
      ends_with(c("Machiavellianism", "Psychopathy", "Narcissism"))
  ) %>%
  gt::tab_spanner(
    label = "Physical",
    columns = starts_with("Physical_")
  ) %>%
  gt::tab_spanner(
    label = "Verbal",
    columns = starts_with("Verbal_")
  ) %>%
  gt::tab_spanner(
    label = "Hostility",
    columns = starts_with("Hostility_")
  ) %>%
  gt::cols_label(
    ends_with("Correlated") ~ "C3F",
    ends_with("Machiavellianism") ~ "Mach",
    ends_with("Psychopathy") ~ "Psych",
    ends_with("Narcissism") ~ "Narc"
  ) %>%
  gt::fmt_markdown(
    columns = -Term
  ) %>%
  gt::cols_align(
    align = "center",
    columns = -Term
  ) %>%
  gt::sub_missing(
    columns = -Term,
    missing_text = "—"
  ) %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(
      groups = everything()
    )
  ) %>%
  gt::tab_style(
    style = gt::cell_borders(
      sides = "top",
      color = "#D3D3D3",
      weight = gt::px(2)
    ),
    locations = list(
      gt::cells_stub(
        rows = Term %in% c("Mach (S)", "R²")
      ),
      gt::cells_body(
        rows = Term %in% c("Mach (S)", "R²")
      )
    )
  ) %>%
  gt::tab_options(
    table.font.names = c("Verdana", "Arial", "sans-serif"),
    table.font.size = gt::px(11),
    column_labels.font.weight = "bold",
    column_labels.border.top.width = gt::px(0),
    column_labels.border.bottom.width = gt::px(1),
    table_body.hlines.width = gt::px(0)
  )

sensitivityGT

if(export) {
  sensitivityGT_png <- sensitivityGT %>%
    gt::tab_options(
      table.width = gt::px(624)
    )
  
  gt::gtsave(
    sensitivityGT_png,
    filename = "../Tables/sensitivityTable.png",
    zoom = 3.125,
    expand = 0
  ) 
}
```

#### LaTeX

```{r}

if(export) {
  # Convert one HTML-formatted result cell to LaTeX
  toLatexCell <- function(x) {
    if (is.na(x)) {
      return("\\textemdash{}")
    }
    
    x <- gsub("&lt;", "$<$", x, fixed = TRUE)
    
    # Convert the bold HTML span to LaTeX
    x <- gsub(
      "<span style='font-weight:bold;'>(.*?)</span>",
      "\\\\textbf{\\1}",
      x,
      perl = TRUE
    )
    
    # Replace each complete star sequence exactly once
    x <- gsub(
      "(\\*{1,3})",
      "{\\\\tiny \\1}",
      x,
      perl = TRUE
    )
    
    lines <- strsplit(x, "<br>", fixed = TRUE)[[1]]
    
    paste0(
      "\\makecell{",
      paste(lines, collapse = " \\\\ "),
      "}"
    )
  }
  
  # ------------------------------------ LEAN TABLE ---------------------------------------
  
  sensitivityTableLatex <- sensitivityTableLean %>%
    mutate(
      Panel = as.character(Panel),
      Term = as.character(Term),
      Term = recode(
        Term,
        "R²" = "$\\text{R}^2$"
      )
    ) %>%
    mutate(
      across(
        -c(Panel, Term),
        \(x) vapply(x, toLatexCell, character(1))
      )
    )
  
  
  # Determine panel positions automatically
  panelRuns <- rle(sensitivityTableLatex$Panel)
  
  panelIndex <- stats::setNames(
    panelRuns$lengths,
    panelRuns$values
  )
  
  panelSizes <- table(sensitivityTableLatex$Panel)
  
  nFO <- unname(panelSizes["First order"])
  nS <- unname(panelSizes["Specific"])
  nModelInfo <- unname(panelSizes["Model information"])
  
  sensitivityKable <- sensitivityTableLatex %>%
    dplyr::select(-Panel) %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", rep("c", 12)),
      col.names = c("", rep(c("Mach", "Psych", "Narc", "C3F"), 3))
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(sensitivityTableLatex) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::add_header_above(
      c(
        " " = 1,
        "Bifactor ($\\\\mathbf{S-1}$)" = 3, " " = 1,
        "Bifactor ($\\\\mathbf{S-1}$)" = 3, " " = 1,
        "Bifactor ($\\\\mathbf{S-1}$)" = 3, " " = 1
      ),
      escape = FALSE,
      bold = TRUE
    ) %>%
    kableExtra::add_header_above(
      c(
        " " = 1,
        "Physical" = 4,
        "Verbal" = 4,
        "Hostility" = 4
      ),
      escape = FALSE,
      bold = TRUE
    ) %>%
    kableExtra::row_spec(
      row = setdiff(
        seq_len(nrow(sensitivityTableLatex) - 1),
        nFO
      ),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    # Separator after the first-order estimates
    kableExtra::row_spec(
      row = nFO,
      extra_latex_after = "\\specialrule{0.3pt}{0.65em}{0.35em}"
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(sensitivityKable),
    "../Tables/sensitivityTable.tex"
  )
  
  
  # ------------------------------------ FULL TABLE ---------------------------------------
  
  
  sensitivityFullLatex <- sensitivityTableFull %>%
    mutate(
      Panel = as.character(Panel),
      Term = as.character(Term),
      Term = recode(
        Term,
        "R²" = "$\\text{R}^2$"
      )
    ) %>%
    mutate(
      across(
        -c(Panel, Term),
        \(x) vapply(x, toLatexCell, character(1))
      )
    )
  
  
  # Determine panel positions automatically
  panelRuns <- rle(sensitivityFullLatex$Panel)
  
  panelIndex <- stats::setNames(
    panelRuns$lengths,
    panelRuns$values
  )
  
  panelSizes <- table(sensitivityFullLatex$Panel)
  
  nFO <- unname(panelSizes["First order"])
  nS <- unname(panelSizes["Specific"])
  nModelInfo <- unname(panelSizes["Model information"])
  
  sensitivityFullKable <- sensitivityFullLatex %>%
    dplyr::select(-Panel) %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", rep("c", 16)),
      col.names = c("", rep(c("Mach", "Psych", "Narc", "C3F"), 4))
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(sensitivityFullLatex) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::add_header_above(
      c(
        " " = 1,
        "Bifactor ($\\\\mathbf{S-1}$)" = 3, " " = 1,
        "Bifactor ($\\\\mathbf{S-1}$)" = 3, " " = 1,
        "Bifactor ($\\\\mathbf{S-1}$)" = 3, " " = 1,
        "Bifactor ($\\\\mathbf{S-1}$)" = 3, " " = 1
      ),
      escape = FALSE,
      bold = TRUE
    ) %>%
    kableExtra::add_header_above(
      c(
        " " = 1,
        "Physical" = 4,
        "Verbal" = 4,
        "Hostility" = 4,
        "Anger" = 4
      ),
      escape = FALSE,
      bold = TRUE
    ) %>%
    # Ordinary spacing within panels
    kableExtra::row_spec(
      row = setdiff(
        seq_len(nrow(sensitivityFullLatex) - 1),
        c(nFO, nFO + nS)
      ),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    # Explicit, equal spacing around panel separators
    kableExtra::row_spec(
      row = c(nFO, nFO + nS),
      extra_latex_after = "\\specialrule{0.3pt}{0.65em}{0.35em}"
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(sensitivityFullKable),
    "../Tables/sensitivityTableFull.tex"
  )
}
```

# Supplemental

### Variance-Weighted Latent Effect

The type-2 Variance-Weighted Latent Effect introduced in this project targets the partial effect of a first-order factor while holding all non-overlapping components and covariates fixed, but relaxing the conditional interpretation with respect to overlapping components. Here, we illustrate the equivalent parametrizations that recover the VWLEs reported alongside the VWLE recovery. The reference model in this exercise includes all latent components and their interactions with sex. Each equivalent first-order parametrization expresses the target factor in first-order coordinates while retaining all non-overlapping residual components, covariates, and corresponding interaction terms.

```{r}

set.seed(masterSeed)

DTFS <- lavPredict(congenialPartialFit, method = "Regression", transform = FALSE)
caseIdx <- unlist(lavInspect(congenialPartialFit, "case.idx"), use.names = FALSE)
DTFSmat <- do.call(rbind, DTFS)
FSDF <- cbind(
  replicationData[caseIdx, , drop = FALSE],
  DTFSmat
)

gBase <- c("Reference")

lambdaMatrix <- as.matrix(lavInspect(congenialPartialFit, "est")$`0`$lambda)[lavNames(congenialPartialFit, type="ov.ind"), lavNames(congenialPartialFit, type="lv")]

lambda_x <- lambdaMatrix[, !(colnames(lambdaMatrix) %in% gBase), drop = FALSE]

lambda_x_xi <- lambdaMatrix[, gBase, drop = FALSE]

lambda_xi <- solve(t(lambda_x) %*% lambda_x) %*% t(lambda_x) %*% lambda_x_xi

# ---------------------------------- REFERENCE MODEL -------------------------------------

structuralFit <- sem(
  model=saturatedModel,
  estimator="MLR",
  meanstructure=TRUE,
  data = FSDF
)

response <- c(
  lavNames(structuralFit, type = "ov.y"),
  lavNames(structuralFit, type = "lv.y")
)

g <- c("Reference", "Reference:Male")

s <- list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male", "Narcissism:Male"))

covariates <- c("Male")

coefMatrix <- as.matrix(lavInspect(structuralFit, "est")$beta)[response, ] #Ensure order

order <- colnames(coefMatrix)

covMatrix <- as.matrix(lavInspect(structuralFit, "cov.all"))

covMatrix <- covMatrix[order, order, drop=FALSE]

vwleResult <- vwleFun(
  response=response, 
  g=g, 
  s=s, 
  covariates=covariates, 
  lambdaMatrix=lambdaMatrix,
  covMatrix=covMatrix,
  coefMatrix=coefMatrix
)

vwleList <- lapply(
  seq_len(nrow(vwleResult$lvl)), 
  function(i) {
    out <- lapply(
      seq_len(ncol(vwleResult$lvl)), 
      function(j){
        return(vwleResult$lvl[i,j, drop=FALSE])
      }
    )
    return(out)
  }
)

vwleList <- unlist(vwleList, recursive=FALSE)

vwleRows <- do.call(
  rbind,
  lapply(
    vwleList,
    function(i) {
      left <- rownames(i)
      right <- colnames(i)
      
      target <- coefMatrix[left, right]
      
      if(target == 0) {
        # Do not extract the VWLE if a specific component is absent from the corresponding equation
        return(NULL)
      } else {
        vwleRows <- tibble::tibble(
          lhs = left,
          op = "~",
          rhs = paste0(right, "VWLE"),
          est = as.numeric(i),
          se = NA,
          z = NA,
          pvalue = NA
        )
        return(vwleRows)
      }
    }
  )
)

# ----------------------------- PSYCHOPATHY PARAMETRIZATION ---------------------------------

FSDF$PsychopathyFO <-
  lambda_xi["Psychopathy", "Reference"] * FSDF$Reference +
  FSDF$Psychopathy

structuralModel <- '
  Physical ~ Male + Narcissism + PsychopathyFO + PsychopathyFO:Male + Narcissism:Male
  Verbal ~ Male + Narcissism + PsychopathyFO + PsychopathyFO:Male + Narcissism:Male
  Hostility ~ Male + Narcissism + PsychopathyFO + PsychopathyFO:Male + Narcissism:Male
  Anger ~ Male + Narcissism + PsychopathyFO + PsychopathyFO:Male + Narcissism:Male
  
  Physical ~~ Verbal
  Physical ~~ Hostility
  Physical ~~ Anger
  Verbal ~~ Hostility
  Verbal ~~ Anger
  Hostility ~~ Anger
'

psychopathyFit <- sem(
  model=structuralModel,
  estimator="MLR",
  meanstructure=TRUE,
  data = FSDF
)

psychopathyTable <- parameterEstimates(psychopathyFit) %>%
  filter(op=="~" & grepl("FO", rhs, fixed = TRUE)) %>%
  dplyr::select(-c(ci.lower, ci.upper))

# ----------------------------- NARCISSISM PARAMETRIZATION ---------------------------------

FSDF$NarcissismFO <-
  lambda_xi["Narcissism", "Reference"] * FSDF$Reference +
  FSDF$Narcissism

structuralModel <- '
  Physical ~ Male + NarcissismFO + Psychopathy + Psychopathy:Male + NarcissismFO:Male
  Verbal ~ Male + NarcissismFO + Psychopathy + Psychopathy:Male + NarcissismFO:Male
  Hostility ~ Male + NarcissismFO + Psychopathy + Psychopathy:Male + NarcissismFO:Male
  Anger ~ Male + NarcissismFO + Psychopathy + Psychopathy:Male + NarcissismFO:Male
  
  Physical ~~ Verbal
  Physical ~~ Hostility
  Physical ~~ Anger
  Verbal ~~ Hostility
  Verbal ~~ Anger
  Hostility ~~ Anger
'

narcissismFit <- sem(
  model=structuralModel,
  estimator="MLR",
  meanstructure=TRUE,
  data = FSDF
)

narcissismTable <- parameterEstimates(narcissismFit) %>%
  filter(op=="~" & grepl("FO", rhs, fixed = TRUE)) %>%
  dplyr::select(-c(ci.lower, ci.upper))

# ----------------------------- COMPARISON TABLE -------------------------------------

vwleTable <- bind_rows(
  psychopathyTable,
  narcissismTable
) %>%
  mutate(
    rhs = sub("FO", "", rhs),
  ) %>%
  left_join(
    vwleRows %>%
      transmute(
        lhs,
        op,
        rhs = sub("VWLE$", "", rhs),
        VWLE = est
      ),
    by = c("lhs", "op", "rhs")
  )
    
vwleTable %>%
  dplyr::select(lhs, op, rhs, est, VWLE, se, z, pvalue)
```

#### HTML

```{r}

outcomeLevels <- c(
  "Physical",
  "Verbal",
  "Hostility",
  "Anger"
)

outcomeLabels <- c(
  "Physical",
  "Verbal",
  "Hostility",
  "Anger"
)

termLevels <- c(
  "Machiavellianism",
  "Machiavellianism:Male",
  "Psychopathy",
  "Psychopathy:Male",
  "Narcissism",
  "Narcissism:Male"
)

termLabels <- c(
  "Machiavellianism",
  "Machiavellianism × Male",
  "Psychopathy",
  "Psychopathy × Male",
  "Narcissism",
  "Narcissism × Male"
)

modelLevels <- c("est", "VWLE")
modelLabels <- c("Direct", "VWLE")

comparisonTable <- vwleTable %>%
  pivot_longer(
    cols = c(est, VWLE),
    names_to = "model",
    values_to = "Estimate"
  ) %>%
  mutate(
    Estimate = sprintf("%.3f", Estimate),
    Outcome = factor(
      lhs,
      levels = outcomeLevels,
      labels = outcomeLabels
    ),
    Model = factor(
      model,
      levels = modelLevels,
      labels = modelLabels
    ),
    Term = factor(
      rhs, 
      levels = termLevels,
      labels = termLabels
    )
  ) %>%
  dplyr::select(
    Outcome,
    Term,
    Model,
    Estimate
  )

comparisonTable <- comparisonTable %>%
  tidyr::pivot_wider(
    id_cols = Term,
    names_from = c(Outcome, Model),
    values_from = Estimate,
    names_sep = "_",
    names_expand = TRUE
  ) %>%
  arrange(Term)


comparisonGT <- comparisonTable %>%
  gt::gt(
    rowname_col = "Term"
  ) %>%
  gt::tab_spanner(
    label = "Physical",
    columns = starts_with("Physical_")
  ) %>%
  gt::tab_spanner(
    label = "Verbal",
    columns = starts_with("Verbal_")
  ) %>%
  gt::tab_spanner(
    label = "Hostility",
    columns = starts_with("Hostility_")
  ) %>%
  gt::tab_spanner(
    label = "Anger",
    columns = starts_with("Anger_")
  ) %>%
  gt::cols_label(
    ends_with("Direct") ~ "Direct",
    ends_with("VWLE") ~ "VWLE"
  ) %>%
  gt::fmt_markdown(
    columns = -Term
  ) %>%
  gt::cols_align(
    align = "center",
    columns = -Term
  ) %>%
  gt::sub_missing(
    columns = -Term,
    missing_text = "—"
  ) %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(
      groups = everything()
    )
  ) %>%
  gt::tab_options(
    table.font.names = c("Verdana", "Arial", "sans-serif"),
    table.font.size = gt::px(11),
    column_labels.font.weight = "bold",
    column_labels.border.top.width = gt::px(0),
    column_labels.border.bottom.width = gt::px(1),
    table_body.hlines.width = gt::px(0)
  )

comparisonGT

if(export) {
  comparisonGT_png <- comparisonGT %>%
    gt::tab_options(
      table.width = gt::px(624)
    )
  
  gt::gtsave(
    comparisonGT_png,
    filename = "../Tables/comparisonTable.png",
    zoom = 3.125,
    expand = 0
  )
}
```

#### LaTeX

```{r}

if(export) {
  # Convert one HTML-formatted result cell to LaTeX
  toLatexCell <- function(x) {
    if (is.na(x)) {
      return("\\textemdash{}")
    }
    
    x <- gsub("&lt;", "$<$", x, fixed = TRUE)
    
    # Replace each complete star sequence exactly once
    x <- gsub(
      "(\\*{1,3})",
      "{\\\\tiny \\1}",
      x,
      perl = TRUE
    )
    
    lines <- strsplit(x, "<br>", fixed = TRUE)[[1]]
    
    paste0(
      "\\makecell{",
      paste(lines, collapse = " \\\\ "),
      "}"
    )
  }
  
  comparisonTableLatex <- comparisonTable %>%
    mutate(
      Term = as.character(Term),
      Term = recode(
        Term,
        "Psychopathy × Male" = "Psychopathy $\\times$ Male",
        "Narcissism × Male" = "Narcissism $\\times$ Male"
      )
    ) %>%
    mutate(
      across(
        -c(Term),
        \(x) vapply(x, toLatexCell, character(1))
      )
    )
  
  comparisonKable <- comparisonTableLatex %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", rep("c", 8)),
      col.names = c("", rep(c("Direct", "VWLE"), 4))
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(comparisonTableLatex) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::add_header_above(
      c(
        " " = 1,
        "Physical" = 2,
        "Verbal" = 2,
        "Hostility" = 2,
        "Anger" = 2
      ),
      escape = FALSE,
      bold = TRUE
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(comparisonKable),
    "../Tables/comparisonTable.tex"
  )
}
```

### Invariance sensitivity

#### Metric

```{r}

if (parallelSupported) {
  structuralFit <- pbmcapply::pbmclapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = saturatedModel, 
    measurementFit = congenialMetricFit,
    VWLE=TRUE,
    g=c("Reference", "Reference:Male"),
    s=list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male", "Narcissism:Male")),
    covariatesVWLE = c("Male"),
    data = replicationData,
    masterSeed = masterSeed,
    mc.cores = availableCores,
    mc.set.seed = TRUE
  )
} else {
  structuralFit <- lapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = saturatedModel, 
    measurementFit = congenialMetricFit,
    VWLE=TRUE,
    g=c("Reference", "Reference:Male"),
    s=list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male", "Narcissism:Male")),
    covariatesVWLE = c("Male"),
    data = replicationData,
    masterSeed = masterSeed
  )
}

metricStructuralFit <- processFunPV(structuralFit)

metricStructuralFit %>%
  filter(op %in% c("~", "gof") & !(rhs %in% c("R2","N"))) %>%
  dplyr::select(lhs, rhs, Estimate, SE, Z, P) %>%
  mutate(
    across(c(Estimate, SE, Z, P), \(x) round(x, digits = 4))
  )
```

#### Scalar

```{r}

if (parallelSupported) {
  structuralFit <- pbmcapply::pbmclapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = saturatedModel, 
    measurementFit = congenialScalarFit,
    VWLE=TRUE,
    g=c("Reference", "Reference:Male"),
    s=list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male", "Narcissism:Male")),
    covariatesVWLE = c("Male"),
    data = replicationData,
    masterSeed = masterSeed,
    mc.cores = availableCores,
    mc.set.seed = TRUE
  )
} else {
  structuralFit <- lapply(
    X = 1:M,
    FUN = plausibleFun,
    structuralModel = saturatedModel, 
    measurementFit = congenialScalarFit,
    VWLE=TRUE,
    g=c("Reference", "Reference:Male"),
    s=list(c("Psychopathy", "Narcissism"), c("Psychopathy:Male", "Narcissism:Male")),
    covariatesVWLE = c("Male"),
    data = replicationData,
    masterSeed = masterSeed
  )
}

scalarStructuralFit <- processFunPV(structuralFit)

scalarStructuralFit %>%
  filter(op %in% c("~", "gof") & !(rhs %in% c("R2","N"))) %>%
  dplyr::select(lhs, rhs, Estimate, SE, Z, P) %>%
  mutate(
    across(c(Estimate, SE, Z, P), \(x) round(x, digits = 4))
  )
```

#### Invariance sensititvity table

##### HTML

```{r}

outcomeLevels <- c(
  "Physical",
  "Verbal",
  "Hostility",
  "Anger"
)

outcomeLabels <- c(
  "Physical (Z)",
  "Verbal (Z)",
  "Hostility (Z)",
  "Anger (Z)"
)

termLevels <- c(
  "Male",
  "Reference",
  "Reference:Male",
  "Psychopathy",
  "Psychopathy:Male",
  "Narcissism",
  "Narcissism:Male",
  "",
  "R2",
  "N"
)

termLabels <- c(
  "Male",
  "Reference (Z)",
  "Reference × Male",
  "Psychopathy (Z)",
  "Psychopathy × Male",
  "Narcissism (Z)",
  "Narcissism × Male",
  "Intercept",
  "R²",
  "N"
)

modelLevels <- c("metric", "scalar")
modelLabels <- c("Metric", "Scalar")

metricStructuralFit$model <- "metric"
scalarStructuralFit$model <- "scalar"

invarianceSensitivityTable <- dplyr::bind_rows(metricStructuralFit, scalarStructuralFit) %>%
  filter(op %in% c("~", "gof") | (lhs %in% outcomeLevels & op == "~1")) %>%
  filter(!endsWith(rhs, "VWLE")) %>%
  mutate(
    stars = case_when(
      P <= 0.001 ~ "***",
      P <= 0.01  ~ "**",
      P <= 0.05  ~ "*",
      .default = ""
    ),
    pFormatted = if_else(
      P < 0.001,
      "&lt;.001",
      paste0("=", sub("^0", "", sprintf("%.3f", P)))
    ),
    Estimate = case_when(
      op %in% c("~", "~1") ~ sprintf(
        "%.3f%s<br>(%.3f)<br>p%s",
        Estimate, stars, SE, pFormatted
      ),
      rhs == "N" ~ sprintf("%.0f", Estimate),
      .default = sprintf("%.3f", Estimate)
    ),
    Outcome = factor(
      lhs,
      levels = outcomeLevels,
      labels = outcomeLabels
    ),
    Model = factor(
      model,
      levels = modelLevels,
      labels = modelLabels
    ),
    Panel = factor(
      case_when(
        op %in% c("~", "~1") & !endsWith(rhs, "VWLE") ~ "Structural",
        op == "gof" ~ "Model information",
        .default = ""
      ),
      levels = c("Structural", "Model information")
    ),
    Term = factor(
      rhs, 
      levels = termLevels,
      labels = termLabels
    )
  ) %>%
  dplyr::select(
    Outcome,
    Term,
    Model,
    Estimate,
    Panel
  )

invarianceSensitivityTable <- invarianceSensitivityTable %>%
  tidyr::pivot_wider(
    id_cols = c(Panel, Term),
    names_from = c(Outcome, Model),
    values_from = Estimate,
    names_sep = "_",
    names_expand = TRUE
  ) %>%
  arrange(Panel, Term)

invarianceSensitivityGT <- invarianceSensitivityTable %>%
  gt::gt(
    rowname_col = "Term",
    groupname_col = "Panel"
  ) %>%
  gt::tab_spanner(
    label = "Physical (Z)",
    columns = starts_with("Physical")
  ) %>%
  gt::tab_spanner(
    label = "Verbal (Z)",
    columns = starts_with("Verbal")
  ) %>%
  gt::tab_spanner(
    label = "Hostility (Z)",
    columns = starts_with("Hostility")
  ) %>%
  gt::tab_spanner(
    label = "Anger (Z)",
    columns = starts_with("Anger")
  ) %>%
  gt::cols_label(
    ends_with("Metric") ~ "Metric",
    ends_with("Scalar") ~ "Scalar"
  ) %>%
  gt::fmt_markdown(
    columns = -Term
  ) %>%
  gt::cols_align(
    align = "center",
    columns = -Term
  ) %>%
  gt::sub_missing(
    columns = -Term,
    missing_text = "—"
  ) %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups(
      groups = everything()
    )
  ) %>%
  gt::tab_options(
    table.font.names = c("Verdana", "Arial", "sans-serif"),
    table.font.size = gt::px(11),
    column_labels.font.weight = "bold",
    column_labels.border.top.width = gt::px(0),
    column_labels.border.bottom.width = gt::px(1),
    table_body.hlines.width = gt::px(0)
  )

invarianceSensitivityGT

if(export) {
  invarianceSensitivityGT_png <- invarianceSensitivityGT %>%
    gt::tab_options(
      table.width = gt::px(624)
    )
  
  gt::gtsave(
    invarianceSensitivityGT_png,
    filename = "../Tables/invarianceSensitivityTable.png",
    zoom = 3.125,
    expand = 0
  ) 
}
```

##### LaTeX

```{r}

if(export) {
  
  # Convert one HTML-formatted result cell to LaTeX
  toLatexCell <- function(x) {
    if (is.na(x)) {
      return("\\textemdash{}")
    }
    
    x <- gsub("&lt;", "$<$", x, fixed = TRUE)
    
    # Replace each complete star sequence exactly once
    x <- gsub(
      "(\\*{1,3})",
      "{\\\\tiny \\1}",
      x,
      perl = TRUE
    )
    
    lines <- strsplit(x, "<br>", fixed = TRUE)[[1]]
    
    paste0(
      "\\makecell{",
      paste(lines, collapse = " \\\\ "),
      "}"
    )
  }
  
  invarianceSensitivityLatex <- invarianceSensitivityTable %>%
    mutate(
      Panel = as.character(Panel),
      Term = as.character(Term),
      Term = recode(
        Term,
        "Reference × Male" = "Reference $\\times$ Male",
        "Psychopathy × Male" = "Psychopathy $\\times$ Male",
        "Narcissism × Male" = "Narcissism $\\times$ Male",
        "R²" = "$\\text{R}^2$"
      )
    ) %>%
    mutate(
      across(
        -c(Panel, Term),
        \(x) vapply(x, toLatexCell, character(1))
      )
    )
  
  
  # Determine panel positions automatically
  panelRuns <- rle(invarianceSensitivityLatex$Panel)
  
  panelIndex <- stats::setNames(
    panelRuns$lengths,
    panelRuns$values
  )
  
  panelSizes <- table(invarianceSensitivityLatex$Panel)
  
  nPredictors <- unname(panelSizes["Structural"])
  nModelInfo <- unname(panelSizes["Model information"])
  
  invarianceSensitivityKable <- invarianceSensitivityLatex %>%
    dplyr::select(-Panel) %>%
    knitr::kable(
      format = "latex",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", rep("c", 8)),
      col.names = c("Structural", rep(c("Metric", "Scalar"), 4))
    ) %>%
    kableExtra::row_spec(
      row = seq_len(nrow(invarianceSensitivityLatex) - 1),
      extra_latex_after = "\\addlinespace[0.5em]"
    ) %>%
    kableExtra::add_header_above(
      c(
        " " = 1,
        "Physical (Z)" = 2,
        "Verbal (Z)" = 2,
        "Hostility (Z)" = 2,
        "Anger (Z)" = 2
      ),
      escape = FALSE,
      bold = TRUE
    ) %>%
    kableExtra::pack_rows(
      "Model information",
      start_row = nPredictors + 1,
      end_row = nPredictors + nModelInfo,
      bold = TRUE,
      hline_after = FALSE,
      extra_latex_after = "\\midrule ",
      indent = FALSE,
      escape = FALSE,
      latex_align = "@{}l@{}"
    ) %>%
    kableExtra::row_spec(
      row = 0,
      bold = TRUE
    ) %>%
    kableExtra::kable_styling(
      latex_options = "basic",
      full_width = FALSE,
      position = "left"
    )
  
  writeLines(
    stretchLatexTable(invarianceSensitivityKable),
    "../Tables/invarianceSensitivityTable.tex"
  )
}
```
